### 2017-10-14 proposal/mprop.tex
Included basic info

\documentclass{mprop}
\usepackage{graphicx}

% alternative font if you prefer
%\usepackage{times}

% for alternative page numbering use the following package
% and see documentation for commands
%\usepackage{fancyheadings}

% other potentially useful packages
%\uspackage{amssymb,amsmath}
%\usepackage{url}
%\usepackage{fancyvrb}
%\usepackage[final]{pdfpages}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Software Ticket Quality}
\author{Andrei-Mihai Nicolae}
\date{December 18th 2017}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tableofcontents
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{intro}

briefly explain the context of the project problem

\subsection{A subsection}
Please note your proposal need not follow the included section headings - this is only a suggested structure. Also add subsections etc as required

example references: \cite{BK08}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Statement of Problem}

clearly state the problem to be addressed in your forthcoming project. Explain why it would be worthwhile to solve this problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background Survey}

present an overview of relevant previous work including articles, books, and existing software products. Critically evaluate the strengths and weaknesses of the previous work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Approach}

state how you propose to solve the software development problem. Show that your proposed approach is feasible, but identify any risks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Plan}

show how you plan to organize your work, identifying intermediate deliverables and dates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{mprop}
\end{document}

### 2017-10-14 proposal/mprop.tex
Added structure to the literature review subsection of the proposal

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background Survey}
+\section{Background Survey - I believe this is Lit Review?}
 
-present an overview of relevant previous work including articles, books, and existing software products. Critically evaluate the strengths and weaknesses of the previous work.
+\subsection{Introduction}
+
+\subsection{What was covered and why}
+
+\subsection{How papers were found - what terms were searched for + snowballing}
+
+\subsection{Data Quality Metrics}
+
+\subsection{Issue Quality}
+
+\subsection{Measuring Cost and Waste in Software Projects}
+
+\subsection{Sentiment Analysis}
+
+\subsection{Conclusion}
 

### 2017-10-14 paper/example.tex
Added skeleton for the paper as well

%% example.tex
%% Jeremy Singer
%% 16 Oct 12

\documentclass{mpaper}

\begin{document}

\title{An Example Paper for MSci Submission}
\author{Jeremy Singer}
\matricnum{12345678}

\maketitle

\begin{abstract}
According to Simon Peyton Jones, an abstract should address
four key questions. First, what is the problem that this
paper tackles? Second, why is this an interesting problem?
Third, what is the solution this paper proposes?
Finally, why is the proposed solution a good one?
\end{abstract}

\section{Introduction}

This paper outlines the standard template for an MSci submission.
In earlier years, MSci students at the School of Computing
Science\footnote{\url{http://www.dcs.gla.ac.uk}},
University of Glasgow, were expected to produce a full-length
dissertation. Now, the requirement is for MSci students to
write a paper of up to 14 pages in length, using the supplied
\texttt{mpaper} \LaTeX style file.

The precise structure of an MSci paper is not mandated, but it should
probably cover in detail the following aspects of the project.
\begin{enumerate}
\item General description of the problem, motivation, relevance
\item Background information, possibly including a literature survey
\item Description of approach taken to solve the problem, including
  high-level design and lower-level implementation details as appropriate
\item Evaluation, qualitative or quantitative as appropriate
\item Conclusion, including scope for future work
\end{enumerate}

\section{Background}

This \LaTeX template is based on the ACM \texttt{sig-alternate} class.
The layout is two-column text. Generally figures and tables only
extend to one column width, e.g.\ Table \ref{tab-eg},
but it is possible to make them
stretch over both columns using the \texttt{figure*} and
\texttt{table*} environments. For an example, see Figure \ref{fig-eg}.

\begin{table}
\begin{tabular}{l||c||p{2cm}}
\emph{Operating System} & \emph{Version} & \emph{Verdict} \\ \hline \hline
Ubuntu & 12.04 & Everyone's favourite Linux, unless you grew up with
RedHat \\ \hline
Slackware & xxx & Pseudo-hacker's Linux, how often do you recompile
your kernel? \\ \hline
Mac OS & 10.7 & For people with more money than sense \\ \hline
\end{tabular}
\caption{\label{tab-eg}Single column table of figures}
\end{table}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.3]{images/alice.pdf}
\end{center}
\caption{\label{fig-eg}An example figure stretching over two columns}
\end{figure*}

\section{The WizWoz System}

Again, Simon Peyton Jones has a lovely description of how to write a
paper on his
website\footnote{\url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}}.
Personally, I put URLs in footnotes and \emph{bona fide} references
in the bibliography. For instance, Turing \cite{turing37computable}
and Knuth \cite{knuth68art} would not be out of place in list of
references.
How many references? Hard to say. Five is not enough, 50 is pushing
it.

\subsection{User Interface}

Blah blah blah
Blah blah blah
Blah blah blah
Blah blah blah

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Foo}

Blah blah blah
Blah blah blah
Blah blah blah

\subsubsection{Bar}
\textsf{Blah} \textit{blah} \textbf{blah}

\section{Evaluation}

Graphs are always good. I recommend getting to grips with Matlab, R or
gnuplot rather than exporting horribly Excel bitmapped graphs.

\begin{quotation}
 The Assyrian came down like the wolf on the fold,
 And his cohorts were gleaming in purple and gold;
 And the sheen of their spears was like stars on the sea,
 When the blue wave rolls nightly on deep Galilee.

 Like the leaves of the forest when Summer is green,
 That host with their banners at sunset were seen:
 Like the leaves of the forest when Autumn hath blown,
 That host on the morrow lay withered and strown.
\end{quotation}

\section{Conclusions}

The standard Lorem Ipsum passage, used since the 1500s

``Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.''
\vskip8pt \noindent
{\bf Acknowledgments.}
This is optional; it is a location for you to thank people

\bibliographystyle{abbrv}
\bibliography{example}

\end{document}

### 2017-10-15 proposal/mprop.tex
Added one of the papers to the reference section
Started work on Secret Life of Bugs paper
Populated fields for first paper

@@
 \subsection{A subsection}
-Please note your proposal need not follow the included section headings - this is only a suggested structure. Also add subsections etc as required
-
-example references: \cite{BK08}
+Please note your proposal need not follow the included section headings; this is only a suggested structure. Also add subsections etc as required
 
@@
 
-clearly state the problem to be addressed in your forthcoming project. Explain why it would be worthwhile to solve this problem.
+Clearly state the problem to be addressed in your forthcoming project.
+Explain why it would be worthwhile to solve this problem.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background Survey - I believe this is Lit Review?}
+\section{Background Survey}
 
@@
 
-\subsection{How papers were found - what terms were searched for + snowballing}
+\subsection{How papers were found; what terms were searched for + snowballing}
 
@@
 \subsection{Issue Quality}
+
+Secret Life of Bugs (\citep{aranda2009secret}):
+\begin{itemize}
+\item What were the goals?
+  The paper tries to understand and analyze common bug fixing coordination
+  activities. Another goal of the paper was to analyze the reliability of
+  repositories in terms of software projects coordination and propose
+  different directions on how to implement proper tools.
+\item What was the method?
+  They executed a field study which was split into two parts:
+  \begin{itemize}
+  \item firstly, they did an exploratory case study of bug repos histories;
+  \item secondly, they conducted a survey with professionals (i.e.\ testers,
+    developers).
+  \end{itemize}
+  All data and interviews were conducted using Microsoft bug repositories and
+  employees.
+\item What did they learn?
+  They learned that there are multiple factors which influence the coordination
+  activities that revolve around bug fixing, such as organizational, social and
+  technical knowledge, thus one cannot infer any conclusions only by automatic
+  analysis of the bug repositories. Also, through surverying the professionals,
+  they reached the conclusion that there are 8 main goals which can be used for
+  better tools and practices:
+  \begin{itemize}
+  \item probing for ownership;
+  \item summit;
+  \item probing for expertise;
+  \item code review;
+  \item triaging;
+  \item rapid-fire emailing;
+  \item infrequent, direct email;
+  \item shotgun emails.
+  \end{itemize}
+
+\item Link to other work
+  \begin{itemize}
+    \item @inproceedings{anvik2006should,
+  title={Who should fix this bug?},
+  author={Anvik, John and Hiew, Lyndon and Murphy, Gail C},
+  booktitle={Proceedings of the 28th international conference on Software engineering},
+  pages={361--370},
+  year={2006},
+  organization={ACM}
+    }
+      \item @inproceedings{bettenburg2008makes,
+  title={What makes a good bug report?},
+  author={Bettenburg, Nicolas and Just, Sascha and Schr{\"o}ter, Adrian and Weiss, Cathrin and Premraj, Rahul and Zimmermann, Thomas},
+  booktitle={Proceedings of the 16th ACM SIGSOFT International Symposium on Foundations of software engineering},
+  pages={308--318},
+  year={2008},
+  organization={ACM}
+      }
+        \item @inproceedings{ko2007information,
+  title={Information needs in collocated software development teams},
+  author={Ko, Andrew J and DeLine, Robert and Venolia, Gina},
+  booktitle={Software Engineering, 2007. ICSE 2007. 29th International Conference on},
+  pages={344--353},
+  year={2007},
+  organization={IEEE}
+        }
+  \end{itemize}
+\item Relevance to our work: this paper is one of the key papers for our
+  research paper.
+\end{itemize}
+
+\citep{Korkala2014WasteIdentification}
+\begin{itemize}
+\item What were the goals?
+
+\item What was the method?
+\item What did they learn?
+\item Link to other work
+\item Relevance to our work
+\end{itemize}
+
+\citep{aranda2009secret}
+\begin{itemize}
+\item What were the goals?
+\item What was the method?
+\item What did they learn?
+\item Link to other work
+\item Relevance to our work
+\end{itemize}
+
+\citep{aranda2009secret}
+\begin{itemize}
+\item What were the goals?
+\item What was the method?
+\item What did they learn?
+\item Link to other work
+\item Relevance to our work
+\end{itemize}
+
+\citep{aranda2009secret}
+\begin{itemize}
+\item What were the goals?
+\item What was the method?
+\item What did they learn?
+\item Link to other work
+\item Relevance to our work
+\end{itemize}
 

### 2017-10-15 proposal/mprop.tex
Added the second paper

@@
   \end{itemize}
-
-\item Link to other work
-  \begin{itemize}
-    \item @inproceedings{anvik2006should,
-  title={Who should fix this bug?},
-  author={Anvik, John and Hiew, Lyndon and Murphy, Gail C},
-  booktitle={Proceedings of the 28th international conference on Software engineering},
-  pages={361--370},
-  year={2006},
-  organization={ACM}
-    }
-      \item @inproceedings{bettenburg2008makes,
-  title={What makes a good bug report?},
-  author={Bettenburg, Nicolas and Just, Sascha and Schr{\"o}ter, Adrian and Weiss, Cathrin and Premraj, Rahul and Zimmermann, Thomas},
-  booktitle={Proceedings of the 16th ACM SIGSOFT International Symposium on Foundations of software engineering},
-  pages={308--318},
-  year={2008},
-  organization={ACM}
-      }
-        \item @inproceedings{ko2007information,
-  title={Information needs in collocated software development teams},
-  author={Ko, Andrew J and DeLine, Robert and Venolia, Gina},
-  booktitle={Software Engineering, 2007. ICSE 2007. 29th International Conference on},
-  pages={344--353},
-  year={2007},
-  organization={IEEE}
-        }
-  \end{itemize}
 \item Relevance to our work: this paper is one of the key papers for our
@@
 
-\citep{Korkala2014WasteIdentification}
+\citep{bettenburg2008makes}
 \begin{itemize}
 \item What were the goals?
-
+  The main goal of the paper was to investigate the \textbf{quality of bug reports} from a developer's
+  point of view, based on the typical information found in such a report (e.g. stack traces, screenshots).
 \item What was the method?
+  The authors conducted a massive survey with over 450 respondents. The survey was online and it targeted
+  developers from Mozilla, Apache and Eclipse.
 \item What did they learn?
-\item Link to other work
-\item Relevance to our work
+  The main conclusion of this research paper was that well written bug reports will more likely get the 
+  attention of the developers. Thus, including steps to reproduce the bugs or stack traces proved to increase
+  the quality of the bug report. Also, an important achievement reached by the authors was the development of
+  a prototype tool called Cuezilla that could estimate, with an accuracy rate of 31\-48\%, the quality of a bug
+  report.
+\item Relevance to our work: it is relevant to our research in that it provides valuable insight into 
+  what makes for a good bug report based on actual professionals' opinions.
 \end{itemize}

### 2017-10-16 proposal/mprop.tex
Added third and fourth papers

@@
 
-Secret Life of Bugs (\citep{aranda2009secret}):
+Secret Life of Bugs\cite{aranda2009secret}:
 \begin{itemize}
@@
 
-\citep{bettenburg2008makes}
+What makes a good bug report\cite{bettenburg2008makes}:
 \begin{itemize}
-\item What were the goals?
+  \item \textbf{What were the goals?}
   The main goal of the paper was to investigate the \textbf{quality of bug reports} from a developer's
   point of view, based on the typical information found in such a report (e.g. stack traces, screenshots).
-\item What was the method?
+\item \textbf{What was the method?}
   The authors conducted a massive survey with over 450 respondents. The survey was online and it targeted
   developers from Mozilla, Apache and Eclipse.
-\item What did they learn?
+\item \textbf{What did they learn?}
   The main conclusion of this research paper was that well written bug reports will more likely get the 
@@
   report.
-\item Relevance to our work: it is relevant to our research in that it provides valuable insight into 
+\item \textbf{Relevance to our work}: it is relevant to our research in that it provides valuable insight into 
   what makes for a good bug report based on actual professionals' opinions.
+\end{itemize}
+
+Who should fix this bug\cite{anvik2006should}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The authors aimed to create a tool that could automatically assign the 
+    bug report to a specific developer based on his/her suitability for that
+    specific task.
+  \item \textbf{What was the method?}
+    They applied a supervised machine learning algorithm on the 
+    repositories to learn which developers were best suited for specific tasks,
+    thus when a new bug report would come in, a small set of people 
+    would be selected. In order to train the algorithm, they looked at
+    Bugzilla repositories and selected the free text form of tickets, trying
+    to label similar ones based on textual similarities. Once the tickets were 
+    labeled and grouped for specific developers, the algorithm would then be
+    able to present the triager the set of developers suitable to fix the bug.
+  \item \textbf{What did they learn?}
+    The most important lesson learned was that collecting data from bug reports 
+    and CVS logs was quite challenging. One of the major reasons why they 
+    found this aspect hard was that not all CVS comments referenced the 
+    specific bug report id.
+  \item \textbf{Relevance to our work}
+    The paper taught us that bug triaging is hard and that there is almost no 
+    automated tool that can choose the perfect developers to work on the task.
+    Moreover, the method applied by the authors could prove useful as a 
+    learning aid when working with the open source repositories 
+    chosen as data sets.
 \end{itemize}
@@
 \begin{itemize}
-\item What were the goals?
-\item What was the method?
-\item What did they learn?
-\item Link to other work
-\item Relevance to our work
-\end{itemize}
-
-\citep{aranda2009secret}
-\begin{itemize}
-\item What were the goals?
-\item What was the method?
-\item What did they learn?
-\item Link to other work
-\item Relevance to our work
+  \item \textbf{What were the goals?}
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Link to other work}
+  \item \textbf{Relevance to our work}
 \end{itemize}
@@
 \subsection{Measuring Cost and Waste in Software Projects}
+
+Waste Identification\cite{Korkala2014WasteIdentification}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The paper had two main goals: 
+    \begin{itemize}
+      \item a means to identify communication waste in agile software projects 
+        environments;
+      \item types of communication waste in agile projects.
+  \item \textbf{What was the method?}
+    The authors collaborated with a medium-sized American software company
+    and conducted a series of observations, informal discussions, documents 
+    provided by the organization, as well as semi-structured interviews. Moreover,
+    the data collection for waste identification was split into 2 parts:
+      \begin{itemize}
+        \item \textbf{pre-development}: occured before the actual implementation
+          begun (e.g. backlog creation);
+        \item \textbf{development}: happened throughout the implementation
+          process (e.g. throughout sprints, retrospectives, sprint reviews,
+          communication media).
+      \end{itemize}
+  \item \textbf{What did they learn?}
+    They realized the communication waste can be divided into 5 main categories:
+      \begin{itemize}
+        \item lack of involvement;
+        \item lack of shared understanding;
+        \item outdated information;
+        \item restricted access to information;
+        \item scattered information.
+      \end{itemize}
+    Also, they learned that their way of identifying these types of waste was
+    quite efficient and they even recommend it to companies if they'd like
+    to conduct such processes internally.
+  \item \textbf{Relevance to our work}
+\end{itemize}
 

### 2017-10-16 proposal/mprop.tex
Completed the fourth paper with relevance

@@
 
-\citep{aranda2009secret}
-\begin{itemize}
-\item What were the goals?
-\item What was the method?
-\item What did they learn?
-\item Link to other work
-\item Relevance to our work
-\end{itemize}
-
 \subsection{Measuring Cost and Waste in Software Projects}
@@
       \item types of communication waste in agile projects.
+    \end{itemize}
   \item \textbf{What was the method?}
@@
         \item \textbf{pre-development}: occured before the actual implementation
-          begun (e.g. backlog creation);
+          begun (e.g.\ backlog creation);
         \item \textbf{development}: happened throughout the implementation
-          process (e.g. throughout sprints, retrospectives, sprint reviews,
+          process (e.g.\ throughout sprints, retrospectives, sprint reviews,
           communication media).
@@
     to conduct such processes internally.
-  \item \textbf{Relevance to our work}
+  \item \textbf{Relevance to our work}: the waste identification process can
+    be applied to our work so that we can identify possible causes to poor 
+    quality tickets.
 \end{itemize}

### 2017-10-16 proposal/mprop.tex
Added in the fifth paper

@@
 
-Secret Life of Bugs\cite{aranda2009secret}:
+\textbf{Secret Life of Bugs}\cite{aranda2009secret}:
 \begin{itemize}
@@
 
-What makes a good bug report\cite{bettenburg2008makes}:
+\textbf{What makes a good bug report}\cite{bettenburg2008makes}:
 \begin{itemize}
@@
 
-Who should fix this bug\cite{anvik2006should}:
+\textbf{Who should fix this bug?}\cite{anvik2006should}:
 \begin{itemize}
@@
 
-\citep{aranda2009secret}
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  \item \textbf{What was the method?}
-  \item \textbf{What did they learn?}
-  \item \textbf{Link to other work}
-  \item \textbf{Relevance to our work}
-\end{itemize}
-
 \subsection{Measuring Cost and Waste in Software Projects}
 
-Waste Identification\cite{Korkala2014WasteIdentification}:
+\textbf{Waste Identification}\cite{Korkala2014WasteIdentification}:
 \begin{itemize}
@@
 
+\textbf{Software Development Waste}\cite{sedano2017software}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the paper was to identify main types of waste in software
+    development projects.
+  \item \textbf{What was the method?}
+    They conducted a participant-observation study over a long period of time
+    at Pivotal, a consultancy software development company. They also interviewed
+    multiple engineers and balanced theoretical sampling with analysis to achieve
+    the conclusions.
+  \item \textbf{What did they learn?}
+    They found out there are nine main types of waste in software projects:
+    \begin{itemize}
+      \item building the wrong feature or product;
+      \item mismanaging backlog;
+      \item extraneous cognitive load;
+      \item rework;
+      \item ineffective communication;
+      \item waiting/multitasking;
+      \item solutions too complex;
+      \item psychological distress.
+  \item \textbf{Relevance to our work}: this paper complements the previous 
+    one on waste identification\cite{Korkala2014WasteIdentification}.
+\end{itemize}
+
 \subsection{Sentiment Analysis}

### 2017-10-16 proposal/mprop.tex
Added new paper to references; formatting

@@
   The main goal of the paper was to investigate the \textbf{quality of bug reports} from a developer's
-  point of view, based on the typical information found in such a report (e.g. stack traces, screenshots).
+  point of view, based on the typical information found in such a report (e.g.\ stack traces, screenshots).
 \item \textbf{What was the method?}
@@
     \end{itemize}
+\end{itemize}
 

### 2017-10-16 proposal/mprop.tex
Added another paper

@@
 
+\textbf{Analysis of Software Cost Estimation}\cite{grimstad2006framework}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The authors are trying to show that poor estimation analysis techniques 
+    in software projects will lead to wrong conclusions regarding cost 
+    estimation accuracy. Moreover, they also propose a framework for 
+    better analysis of software cost estimation error.
+  \item \textbf{What was the method?}
+    They approached a real-world company where they conducted analysis on
+    their cost estimation techniques.
+  \item \textbf{What did they learn?}
+    They learned that regular, straight-forward types of cost estimation analysis
+    techniques error lead them to wrong conclusions. 
+  \item \textbf{Relevance to our work}: it showed us that we need to be careful
+    when selecting techniques for cost estimation in our own research.
+\end{itemize}
+
 \textbf{Waste Identification}\cite{Korkala2014WasteIdentification}:
@@
 
+\textbf{Recognizing Contextual Polarity}\cite{wilson2005recognizing}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The paper's main goal is to experiment with automatically distinguishing
+    between contextual and prior polarity.
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
+
 \subsection{Conclusion}

### 2017-10-16 proposal/mprop.tex
Completed the contextual polarity paper summary

@@
   \item \textbf{What were the goals?}
-    The paper's main goal is to experiment with automatically distinguishing
-    between contextual and prior polarity.
+    The paper's main goal is to find efficient ways to distinguish between 
+    contextual and prior polarity.
   \item \textbf{What was the method?}
+    They used a two step method that used machine learning and a variety of
+    features. The first step classified each phrase which had a clue as either
+    neutral or polar, followed by taking all phrases marked in the previous step
+    and giving them a contextual polarity (e.g.\ positive, negative, both, neutral).
   \item \textbf{What did they learn?}
-  \item \textbf{Relevance to our work}:
+    Through the method the authors employed, they managed to automatically identify
+    the contextual polarity. As most papers were only looking at the sentiment  
+    extracted from the overall document, they managed to get valuable results
+    from looking at specific words and phrases.
+  \item \textbf{Relevance to our work}: when analyzing the description and
+    comments of the ticket, we can use their method for accurately 
+    infering the sentiment transmitted.
 \end{itemize}

### 2017-10-16 proposal/mprop.tex
Added 8th paper

@@
 
+\textbf{Thumbs Up or Thumbs Down}\cite{turney2002thumbs}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
+
+\textbf{Thumbs Up or Thumbs Down}\cite{turney2002thumbs}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the paper is to detect the overall sentiment transmitted
+    through reviews of various types.
+  \item \textbf{What was the method?}
+    The author created an unsupervised machine learning algorithm that was 
+    evaluated on more than 400 reviews on Epinions on various kinds of markets 
+    (e.g.\ automobiles, movie). The algorithm implementation was divided 
+    into three steps:
+      \begin{itemize}
+        \item extract phrases containing adjectives or adverbs;
+        \item estimate the semantic orientation of the phrases;
+        \item classify the review as recommended or not recommended based on
+          the semantic orientation calculated at previous step.
+      \end{itemize}
+  \item \textbf{What did they learn?}
+    One thing the author learned that different categories will yield different 
+    results. For example, the automobile section on Epinions ranked much higher, 
+    84\%, compared to movie reviews, which had an accuracy of 65.83\%. Moreover, 
+    most pitfalls of the algorithm could be attributed to multiple factors, such 
+    as not using a supervised learning system or limitations of PMI-IR.
+  \item \textbf{Relevance to our work}: the method can be applied for extracting
+    sentiments from the tickets (description and comments) we will use 
+    in our own research.
+\end{itemize}
+
 \textbf{Recognizing Contextual Polarity}\cite{wilson2005recognizing}:
@@
     neutral or polar, followed by taking all phrases marked in the previous step
-    and giving them a contextual polarity (e.g.\ positive, negative, both, neutral).
+    and giving them a contextual polarity (e.g.\ positive, negative, 
+    both, neutral).
   \item \textbf{What did they learn?}
-    Through the method the authors employed, they managed to automatically identify
-    the contextual polarity. As most papers were only looking at the sentiment  
-    extracted from the overall document, they managed to get valuable results
-    from looking at specific words and phrases.
+    Through the method the authors employed, they managed to automatically 
+    identify the contextual polarity. As most papers were only looking at the 
+    sentiment extracted from the overall document, they managed to get valuable 
+    results from looking at specific words and phrases.
   \item \textbf{Relevance to our work}: when analyzing the description and
-    comments of the ticket, we can use their method for accurately 
-    infering the sentiment transmitted.
+    comments of the ticket, we can use their method for infering the sentiment 
+    transmitted probably more accurately than the technique used in 
+    Turney's paper\cite{turney2002thumbs}.
 \end{itemize}

### 2017-10-17 proposal/mprop.tex
Added the 9th paper

@@
 
+\textbf{Software Quality \- The Elusive Target}\cite{kitchenham1996software}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the paper is to determine what makes for a good quality
+    software project, as well as who are the people in charge of this aspect
+    and how should they approach achieving it.
+  \item \textbf{What was the method?}
+    They tried to define quality in software projects and analyze techniques that 
+    measure such quality by looking at other models proposed in different other  
+    papers (e.g.\ McCall's quality model, ISO 9126).
+  \item \textbf{What did they learn?}
+    They learned that quality is very hard to define and there are various 
+    factors which need to be taken into consideration, such as the business
+    model of the company, the type of the software project (e.g.\ safety
+    critical, financial) or the actors which are involved and how they
+    coordinate the software activities.
+  \item \textbf{Relevance to our work}: this paper is a key paper on software  
+    quality and it can prove beneficial in our research by
+    giving valuable insights into how software quality can be modeled, thus
+    helping us in selecting good quality open source repositories to work with 
+    (i.e.\ ticket selection and analysis).
+\end{itemize}
+
 \subsection{Sentiment Analysis}
 
-\textbf{Thumbs Up or Thumbs Down}\cite{turney2002thumbs}:
+\textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
 \begin{itemize}

### 2017-10-17 proposal/mprop.tex
Added paper on software quality in OSS

@@
 
+\textbf{Code Quality Analysis in OSS}\cite{stamelos2002code}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The article tries to discuss and examine the quality of the source code
+    delivered by open source projects.
+  \item \textbf{What was the method?}
+    They used a set of tools that could automatically inspect various aspects
+    of source code. The authors analyzed the 6th release of the OpenSUSE project
+    and examined only the components, which are defined by C functions in the
+    programs.
+  \item \textbf{What did they learn?}
+    The research's results show that Linux applications have high quality 
+    code standards that one might expect in an open source repository, but 
+    the quality is lower than the one implied by the standard. More than half
+    of the components were in a high state of quality, but on the other hand, 
+    most lower quality components cannot be improved only by applying some
+    corrective actions. Thus, even though not all the source code was in 
+    an industrial standards shape, there is definitely room for further 
+    improvement and open source repositories proved to be of good quality.
+  \item \textbf{Relevance to our work}: this work completes the previous paper
+    on software quality in general by looking specifically at quality in
+    open source projects, which will be our main points for data collection.
+\end{itemize}
+
 \subsection{Sentiment Analysis}

### 2017-10-18 proposal/mprop.tex
Commented out skeleton for further papers
Added paper on Kanban software projects waste

@@
 
-\subsection{Measuring Cost and Waste in Software Projects}
+\textbf{Software Quality \- The Elusive Target}\cite{kitchenham1996software}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the paper is to determine what makes for a good quality
+    software project, as well as who are the people in charge of this aspect
+    and how should they approach achieving it.
+  \item \textbf{What was the method?}
+    They tried to define quality in software projects and analyze techniques that 
+    measure such quality by looking at other models proposed in different other  
+    papers (e.g.\ McCall's quality model, ISO 9126).
+  \item \textbf{What did they learn?}
+    They learned that quality is very hard to define and there are various 
+    factors which need to be taken into consideration, such as the business
+    model of the company, the type of the software project (e.g.\ safety
+    critical, financial) or the actors which are involved and how they
+    coordinate the software activities.
+  \item \textbf{Relevance to our work}: this paper is a key paper on software  
+    quality and it can prove beneficial in our research by
+    giving valuable insights into how software quality can be modeled, thus
+    helping us in selecting good quality open source repositories to work with 
+    (i.e.\ ticket selection and analysis).
+\end{itemize}
+
+\textbf{Code Quality Analysis in OSS}\cite{stamelos2002code}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The article tries to discuss and examine the quality of the source code
+    delivered by open source projects.
+  \item \textbf{What was the method?}
+    They used a set of tools that could automatically inspect various aspects
+    of source code. The authors analyzed the 6th release of the OpenSUSE project
+    and examined only the components, which are defined by C functions in the
+    programs.
+  \item \textbf{What did they learn?}
+    The research's results show that Linux applications have high quality 
+    code standards that one might expect in an open source repository, but 
+    the quality is lower than the one implied by the standard. More than half
+    of the components were in a high state of quality, but on the other hand, 
+    most lower quality components cannot be improved only by applying some
+    corrective actions. Thus, even though not all the source code was in 
+    an industrial standards shape, there is definitely room for further 
+    improvement and open source repositories proved to be of good quality.
+  \item \textbf{Relevance to our work}: this work completes the previous paper
+    on software quality in general by looking specifically at quality in
+    open source projects, which will be our main points for data collection.
+\end{itemize}
 
@@
 \end{itemize}
+
+\subsection{Measuring Cost and Waste in Software Projects}
 
@@
 
-\textbf{Software Quality \- The Elusive Target}\cite{kitchenham1996software}:
+\textbf{Waste in Kanban Projects}\cite{ikonen2010exploring}:
 \begin{itemize}
   \item \textbf{What were the goals?}
-    The main goal of the paper is to determine what makes for a good quality
-    software project, as well as who are the people in charge of this aspect
-    and how should they approach achieving it.
+    The authors are trying to find the main sources of waste in Kanban software
+    development projects and categorize/rank them based on severity.
   \item \textbf{What was the method?}
-    They tried to define quality in software projects and analyze techniques that 
-    measure such quality by looking at other models proposed in different other  
-    papers (e.g.\ McCall's quality model, ISO 9126).
+    A controlled case study research was employed in a company called Software
+    Factory. They conducted semi-structured interviews with 5 of the team
+    members both in the beginning in order to collect data as well as at the end 
+    of the whole process to categorize the seven types of waste found. Moreover,
+    they also measured the overall success of the project based on Shenar's
+    techniques (first-second-third-fourth; project efficiency-imapct on the
+    customer-business success-preparing for the future).
   \item \textbf{What did they learn?}
-    They learned that quality is very hard to define and there are various 
-    factors which need to be taken into consideration, such as the business
-    model of the company, the type of the software project (e.g.\ safety
-    critical, financial) or the actors which are involved and how they
-    coordinate the software activities.
-  \item \textbf{Relevance to our work}: this paper is a key paper on software  
-    quality and it can prove beneficial in our research by
-    giving valuable insights into how software quality can be modeled, thus
-    helping us in selecting good quality open source repositories to work with 
-    (i.e.\ ticket selection and analysis).
+    They reached two main findings:
+      \begin{itemize}
+        \item they found 7 types of waste throughout the project at various
+          development stages:
+            \begin{itemize}
+              \item partially done work;
+              \item extra processes;
+              \item extra features;
+              \item task switching;
+              \item waiting;
+              \item motion;
+              \item defects.
             \end{itemize}
-
-\textbf{Code Quality Analysis in OSS}\cite{stamelos2002code}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The article tries to discuss and examine the quality of the source code
-    delivered by open source projects.
-  \item \textbf{What was the method?}
-    They used a set of tools that could automatically inspect various aspects
-    of source code. The authors analyzed the 6th release of the OpenSUSE project
-    and examined only the components, which are defined by C functions in the
-    programs.
-  \item \textbf{What did they learn?}
-    The research's results show that Linux applications have high quality 
-    code standards that one might expect in an open source repository, but 
-    the quality is lower than the one implied by the standard. More than half
-    of the components were in a high state of quality, but on the other hand, 
-    most lower quality components cannot be improved only by applying some
-    corrective actions. Thus, even though not all the source code was in 
-    an industrial standards shape, there is definitely room for further 
-    improvement and open source repositories proved to be of good quality.
-  \item \textbf{Relevance to our work}: this work completes the previous paper
-    on software quality in general by looking specifically at quality in
-    open source projects, which will be our main points for data collection.
+        \item they reached the conclusion that they couldn't explain the success
+          of the project even though waste was found.
+      \end{itemize}
+  \item \textbf{Relevance to our work}: this work completes the findings 
+    from the previous work presented as most of the projects we will work with
+    will be Agile, thus Kanban-based in terms of issue management.
 \end{itemize}
@@
 
-\textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  \item \textbf{What was the method?}
-  \item \textbf{What did they learn?}
-  \item \textbf{Relevance to our work}:
-\end{itemize}
+% \textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
+% \begin{itemize}
+%   \item \textbf{What were the goals?}
+%   \item \textbf{What was the method?}
+%   \item \textbf{What did they learn?}
+%   \item \textbf{Relevance to our work}:
+% \end{itemize}
 

### 2017-10-19 proposal/mprop.tex
Added paper on automatic bug report assigning

@@
 \subsection{Issue Quality}
+
+\textbf{Bug Report Assignee Recommendation using 
+Activity Profiles}\cite{Naguib2013BugReportAssignee}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the paper is to automatically detect who should be
+    the developers who are most suitable to solve a specific issue.
+  \item \textbf{What was the method?}
+    They employed an algorithm using activity profiles (i.e.\ assign, review,
+    resolve activity of the developer) such that, after detecting the prior
+    experience, developer's role, and involvement in the project, it could
+    recommend who should fix a specific bug. The average accuracy was around
+    88\%, much higher than the LDA-SVM technique.
+  \item \textbf{What did they learn?}
+    They found out that their approach was more accurate than previous work
+    done on assignee recommendation, but they think that it might even be
+    improved further by combining their technique with the classic LDA-SVM one.
+  \item \textbf{Relevance to our work}: this work complements the research
+    presented in Anvik et al. \cite{anvik2006should} and it will provide us
+    with valuable insight into how automatic triaging should be performed.
+\end{itemize}
 

### 2017-10-28 proposal/mprop.tex
Added paper reference and layout for modeling bug report quality
Started working on a new paper
Add modeling bug report quality paper

@@
     with valuable insight into how automatic triaging should be performed.
+\end{itemize}
+
+\textbf{Modeling Bug Report Quality}\cite{hooimeijer2007modeling}
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The authors' goal is to present a model that would determine if a bug
+    report will be triaged in a given amount of time. Moreover, they are 
+    trying to propose features that could help composing a good quality
+    bug report.
+  \item \textbf{What was the method?}
+    They run an analysis on over 27000 bug reports from the Mozilla Firefox
+    project, selecting a couple of surface features that could be applied:
+      \begin{itemize}
+        \item self-reported severity;
+        \item readability;
+        \item daily load (i.e.\ total number of bug reports that need to be
+          dealt with at that point in time);
+        \item submitter reputation;
+        \item changes over time.
+      \end{itemize}
+    Afterwards, they ran 4 experiments (i.e.\ validate the assumptions, find
+    how much post-submission data is necessary, find the optimal resolved by
+    cutoff, evaluate the hypothetical benefit) and analyzed the results to
+    see if their model would be beneficial.
+  \item \textbf{What did they learn?}
+    They found out that linear model, even a simple one, can have 
+    better-than-chance predictive power. Also, they came to the conclusion that 
+    attachment and comment counts are really valuable for triaging the bug faster,
+    compared to, for example, patch count. Moreover, the readability of a bug is
+    important as it proved to influence the duration of the triaging process. 
+  \item \textbf{Relevance to our work}: the authors' goal was quite similar to ours
+    as they are trying to find out which features make for a good quality bug 
+    report. Moreover, they are also using programmatic analysis instead of
+    interviews with developers to produce the results, which is the same approach
+    we are aiming for in our research.
 \end{itemize}

### 2017-10-28 proposal/mprop.tex
Add measuring data quality paper in bib
Add metrics for measuring data quality paper

@@
 \subsection{Data Quality Metrics}
+
+\textbf{Metrics for Measuring Data Quality}\cite{Heinrich2007MetricsDataQuality}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The authors of the paper aimed to answer the two main research questions:
+      \begin{itemize}
+        \item how can data quality be measured as metrics?
+        \item what can be done in regards to data quality and what economic
+          consequences would it bring?
+      \end{itemize}
+  \item \textbf{What was the method?}
+    They applied the metric for timeliness at a major German mobile services
+    provider. Due to some Data Quality issues the company was having, they had
+    lower mailing campaign success rates, but after applying the metrics, the 
+    company was able to establish a direct connection between the results of
+    measuring data quality and the success rates of campaigns.
+  \item \textbf{What did they learn?}
+    For some practical problems, the metrics that they applied in regards to
+    data quality proved to be quite appropriate. As they designed the metrics
+    to revolve around interpretability and cardinality, they could quantify
+    data quality, thus they could analyse the economical impact.
+  \item \textbf{Relevance to our work}: this paper could possibly help us in
+    measuring data quality. This is an important step in our research as we 
+    specifically need to measure quality in software tickets.
+\end{itemize}
 

### 2017-10-29 proposal/mprop.tex
Add paper on impact related to poor data quality
Finish paper on poor data quality in enterprise

@@
 \subsection{Data Quality Metrics}
+
+\textbf{Impact of Poor Data Quality}\cite{redman1998impact}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main purpose of the article is to provide some insights into how
+    data quality can have a major economical impact on a company, as well
+    as to raise awareness about this issue.
+  \item \textbf{What was the method?}
+    The author has analysed various large enterprises and their available data 
+    to infer conclusions about the impact data quality has.
+  \item \textbf{What did they learn?}
+    There are three main issues across most enterprises:
+      \begin{itemize}
+        \item inaccurate data;
+        \item inconsistencies across databases;
+        \item unavailable data necessary for certain operations.
+      \end{itemize}
+    Moreover, the paper also presents a list of impacts poor data quality brings, among 
+    which we can find:
+      \begin{itemize}
+        \item lowered customer satisfaction;
+        \item increased cost;
+        \item lowered employee satisfaction;
+        \item it becomes more difficult to set strategy;
+        \item poorer decision making.
+      \end{itemize}
+  \item \textbf{Relevance to our work}: this is a key paper on data quality in
+    an enterprise setting and what impact it can have. It is valuable to our research 
+    because we can relate the findings with what negative impacts poor tickets
+    can bring to software projects.
+\end{itemize}
 

### 2017-10-30 proposal/mprop.tex
Add organizational impact of information quality paper

@@
 \subsection{Data Quality Metrics}
+
+\textbf{Organizational Impact of 
+        Information Quality}\cite{gorla2010organizational}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The authors had two main research questions they wanted to address:
+      \begin{itemize}
+        \item what individual/combined influences system quality, service quality,
+          information quality have on organizational impact?
+        \item what effect does system quality have on information quality?
+      \end{itemize}
+  \item \textbf{What was the method?}
+    They conducted a construct measurement for the IS quality dimensions and 
+    collected data through empirical testing.
+  \item \textbf{What did they learn?}
+    Firstly, they learned that service quality has the greatest impact 
+    of all three quality constructs. Moreover, they found out that there is a 
+    linkage between system and information quality, fact that previous research
+    did not reveal. Lastly, their results indicate that the above-mentioned 
+    quality dimensions have a significant positive influence on organizational
+    impact either directly or indirectly.
+  \item \textbf{Relevance to our work}: the paper can provide us insights into
+    how valuable information quality is and what an impact it can have.
+\end{itemize}
 

### 2017-10-30 proposal/mprop.tex
Add paper on evaluating IT quality in e-gov

@@
 
+% \textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
+% \begin{itemize}
+%   \item \textbf{What were the goals?}
+%   \item \textbf{What was the method?}
+%   \item \textbf{What did they learn?}
+%   \item \textbf{Relevance to our work}:
+% \end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Data Quality Metrics}
+
+\textbf{Evaluating IT Quality in E-Government 
+        Environment}\cite{prybutok2008evaluating}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the paper is to identify if leadership and IT quality
+    can lead to positive outcomes in an e-government environment.
+  \item \textbf{What was the method?}
+    They conducted a web survey to gather data and test their hypotheses. They
+    assessed the City of Denton's e-government initiatives, including current 
+    plans and implementations.
+  \item \textbf{What did they learn?}
+    They learned that the MBNQA leadership triad (leadership, strategic
+    planning and customer/market focus) had a positive impact on the IT quality
+    triad (information, system and service quality). Moreover, they found out
+    that both leadership and IT quality improved the benefits.
+  \item \textbf{Relevance to our work}: even though the environment presented
+    in the paper was an e-government, it is useful to see how the organization 
+    around a project as well as IT quality can lead to a better functioning of the 
+    system. Thus, in our research, it can prove helpful in choosing the right 
+    open source project to gather and analyse the data from.
+\end{itemize}
 
@@
 
-% \textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
-% \begin{itemize}
-%   \item \textbf{What were the goals?}
-%   \item \textbf{What was the method?}
-%   \item \textbf{What did they learn?}
-%   \item \textbf{Relevance to our work}:
-% \end{itemize}
-
 \textbf{Thumbs Up or Thumbs Down}\cite{turney2002thumbs}:

### 2017-10-30 proposal/mprop.tex
Clean up bib file
Add paper on information quality

@@
 \subsection{Data Quality Metrics}
+
+ \textbf{AIMQ}\cite{lee2002aimq}:
+ \begin{itemize}
+   \item \textbf{What were the goals?}
+     The main challenge set by the authors was to develop an overall model
+     with an accompanying assessment instrument for quantifying information
+     quality.
+   \item \textbf{What was the method?}
+     They developed a methodology called AIM quality (hence the name AIMQ) which
+     they applied at 5 different organizations. It has 3 main components:
+      \begin{itemize}
+        \item 2 $\times$ 2 model of what information quality means to managers;
+        \item questionnaire for measuring information quality along the dimensions
+          found in first step;
+        \item two analysis techniques for interpreting the assessments captured 
+          by the questionnaire.
+      \end{itemize} 
+   \item \textbf{What did they learn?}
+      They conclude that the AIMQ methodology proved to be a practical information
+      quality tool to organizations.
+   \item \textbf{Relevance to our work}: the paper gave us valuable insight into 
+     how to assess information quality.
+\end{itemize}
 

### 2017-10-30 proposal/mprop.tex
Add paper on information and system quality

@@
 \section{Introduction}\label{intro}
+briefly explain the context of the project problem
 
-briefly explain the context of the project problem
+% \textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
+% \begin{itemize}
+%   \item \textbf{What were the goals?}
+%   \item \textbf{What was the method?}
+%   \item \textbf{What did they learn?}
+%   \item \textbf{Relevance to our work}:
+% \end{itemize}
 
@@
 \subsection{Data Quality Metrics}
+
+\textbf{Antecedents of Information and System Quality}
+\cite{nelson2005antecedents}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The authors had 2 main research objectives they wanted to aim for in this
+    paper:
+      \begin{itemize}
+        \item identify a set of antecedents that both drive information and
+          system quality, as well as define the nature of the IT artifact;
+        \item explore data warehousing in general, especially analytical tools,
+          predefined reports and ad hoc queries.
+        \end{itemize}
+  \item \textbf{What was the method?}
+    They conducted a cross-functional survey to test the model the authors 
+    proposed. They focused on user experience with a data warehouse. They sent
+    email invites to the Data Warehouse Institute which distributed it further
+    to organizations, among which 7 agreed to participate, yielding a total of
+    465 completed surveys. 
+  \item \textbf{What did they learn?}
+    They learned that their selected features were indeed a good indicator of
+    overall information and system quality. They also found out that accuracy is
+    the dominant determinant across all three data warehouse technologies, 
+    followed by completeness and format. Also, the results showed that more 
+    attention needs to be given to differences across varying technologies. 
+  \item \textbf{Relevance to our work}: this paper presents important findings
+    regarding information and system quality in an IT environment. We can use it
+    when analysing the quality of the tickets we will mine.
+\end{itemize}
 

### 2017-10-30 proposal/mprop.tex
Add paper on data quality

@@
 
-% \textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
+% \textbf{}\cite{}:
 % \begin{itemize}
@@
 \subsection{Data Quality Metrics}
+
+\textbf{Knowing-Why about Data Processes and Data Quality}\cite{lee2003knowing}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    They tried to investigate whether knowing-why affects work performance and
+    whether knowledge held by people in different roles affect the overall work
+    performance. 
+  \item \textbf{What was the method?}
+    They had 6 companies that served as data collection points. In all of them,
+    the research focused on the quality of their customer activity data, tuned
+    for the specific domain the company was activating in. They held 2 sessions
+    at each company: in the first session, the participants were presented with
+    an overview of the research and a questionnaire, while during the second 
+    session provided summary feedback on the questionnaire results and gave the
+    participants the chance to provide comments and explanations.
+  \item \textbf{What did they learn?}
+    The major finding of the study was that there is vast complexity of knowledge
+    at work in data production process. 
+  \item \textbf{Relevance to our work}: an important research on how knowledge in
+    different roles in a company can lead to decreased data quality overall. It
+    will help us to analyse the software tickets we will mine better.
+\end{itemize}
 

### 2017-10-31 proposal/mprop.tex
Work on paper on data quality in context

@@
 \subsection{Data Quality Metrics}
+
+\textbf{Data Quality in Context}\cite{strong1997data}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+
+  \item \textbf{What was the method?}
+    They performed a qualitative analysis, examining 42 data quality probjects 
+    from 3 organizations. They collected data via inteviews of data procedures,
+    custodians, customers and managers. The authors analysed each project using
+    the data quality dimensions as content analysis codes. 
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
 

### 2017-10-31 proposal/mprop.tex
Finish paper on data quality in context

--- 2017-10-30 proposal/mprop.tex
@@
 \subsection{Data Quality Metrics}
+
+\textbf{Data Quality in Context}\cite{strong1997data}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the authors was to analyze data quality in different 
+    organizations, observe data quality problem patterns as well as see 
+    its implications.
+  \item \textbf{What was the method?}
+    They performed a qualitative analysis, examining 42 data quality projects 
+    from 3 organizations. They collected data via interviews of data procedures,
+    custodians, customers and managers. The authors analysed each project using
+    the data quality dimensions as content analysis codes. 
+  \item \textbf{What did they learn?}
+    One thing that the authors learned is that representational data quality 
+    dimensions are underlying causes of accessibility data quality problem 
+    patterns. Also, they observed three underlying causes for users' complaints
+    regarding data not supporting their tasks:
+      \begin{itemize}
+        \item incomplete data;
+        \item inadequately defined or measured data;
+        \item data that could not be appropriately aggregated.
+      \end{itemize}
+  \item \textbf{Relevance to our work}: this paper brings valuable insight into
+    major data quality issues and patterns, information which we can apply in 
+    our own research.
+\end{itemize}
 

### 2017-10-31 proposal/mprop.tex
Add bib entries for two data quality assessment papers
Finish paper on data quality assessment

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
-% \begin{itemize}
-%   \item \textbf{What were the goals?}
-%   \item \textbf{What was the method?}
-%   \item \textbf{What did they learn?}
-%   \item \textbf{Relevance to our work}:
-% \end{itemize}
 
@@
     our own research.
+\end{itemize}
+
+\textbf{Data Quality Assessment}\cite{pipino2002data}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the authors is to present ways of developing usable data
+    quality metrics that organizations can implement in their own internal 
+    processes.
+  \item \textbf{What was the method?}
+    They have researched previous methods of assessing data quality in information
+    systems and they formulated general advice that can be directly implemented
+    by organizations in their processes.
+  \item \textbf{What did they learn?}
+    They learned that there is no universal approach to assessing data quality
+    as it heavily depends on the context where it is analysed.
+  \item \textbf{Relevance to our work}: it shows how one can effectively measure
+    data quality in information systems, thus we can apply it on the quality of
+    the tickets we are analysing.
+\end{itemize}
+
+\textbf{Product perspective on total 
+        Data Quality Assessment}\cite{wang1998product}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
 \end{itemize}

### 2017-11-15 proposal/mprop.tex
Add another paper on data quality assessment
Add paper on automatic bug report assignment

@@
   \item \textbf{What was the method?}
+    They created the TDQM methodology which is based on accumulated research 
+    and extended 
   \item \textbf{What did they learn?}
@@
 \subsection{Issue Quality}
+
+\textbf{Automatic Bug Report Assignment}\cite{anvik2006automating}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The author’s main goal was to determine a way through which bug triaging can be made 
+    easier using automatization approaches. 
+  \item \textbf{What was the method?}
+    The research’s output was an algorithm that can automatically assign bugs to developers based on various types of information fed.
+The author looked exclusively at ML approaches, examining 8 main types of information (textual description of bug, bug component, OS, hardware, software version, developer who owns the code, current workload of developers, list of devs actively contributing).
+Moreover, the author considers launching a Firefox extension to test the app even further through human evaluation as well.
+  \item \textbf{What did they learn?}
+  The research brings 3 main contributions: methodology for creating semi-automated bug triaging algorithms, a characterization of performance of different approaches, as well as an actual implementation for such a semi-automated big triaget.
+The author discovered that with further improvements and tweaking, we can reach an even further bug triager.
+  \item \textbf{Relevance to our work}:
+  Another project that we can use to learn about bug triaging; also we can contact maybe the author and receive either an executable or the source code for the application. 
+\end{itemize}
 

### 2017-11-15 proposal/mprop.tex
Add multiple papers on issue quality

@@
   Another project that we can use to learn about bug triaging; also we can contact maybe the author and receive either an executable or the source code for the application. 
+\end{itemize}
+
+\textbf{Reducing the effort of bug report triage}\cite{anvik2011reducing}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  The authors had one main goal, and that was to find out if costs related to bug triaging can be reduced if ML algorithms were to be introduced.
+This hypothesis was backed by 2 research questions, which were if the approach would create recommenders that make accurate recommendations and if the humans can make use of the information provided by the approach.
+  \item \textbf{What was the method?}
+  They created a bug triager which can present a list of developers from which someone can choose who is the most suitable to fix that specific issue.
+Also, they improved a previous research the same authors worked on, thus increasing the precision and recall of the algorithm.
+They employed machine learning techniques to create the algorithm.
+Then, in order to test it, they implemented a proxy to the actual web service that’s providing the issue repository, thus visualizing results helped conduct the evaluation process.
+  \item \textbf{What did they learn?}
+  The authors learned that their approach could actually be used in software projects as its accuracy is reasonable.
+They also learned that the impact of poor software project management, including bug triaging, on software projects can be  quite high.
+  \item \textbf{Relevance to our work}:
+  The research presented can help us in understanding better if statistical expetiments are helpful in analyzing tickets, as well as give an insight into how important ticket quality and proper triaging are for any software projct.
+\end{itemize}
+
+\textbf{Effects of process maturity on quality, cycle time and effort in software product development}\cite{harter2000effects}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  The research tries to investigate the relationship between process maturity, quality, cycle time and effort in software projects.
+The authors are mainly trying to prove/reject a couple of hypotheses: higher levels of process maturity lead to higher product quality in software projects, higher levels of process maturity are associated with increased cycle time in software products, higher product quality is associated with lower cycle time, higher levels of process maturity lead to increased development efforts in the project and higher product quality is associated with lower development effort.
+  \item \textbf{What was the method?}
+  In order to test their hypotheses, the authors examined data coming from 30 projects belonging to the systems integration division from a large IT company.
+The process improvement data was collected via external divisions and by government agencies to provide independent assessments of the firm’s software development processes.
+Then, they analyzed a couple of key variables and see how they interact: process maturity, product quality, cycle time, development effort, product size, domain/data/decision complexity and requirements ambiguity.
+  \item \textbf{What did they learn?}
+  They learned that the main features they inspected are additively separable and linear.
+Moreover, they found out that higher levels of process maturity are associated with significantly higher quality, but also with increased cycle times and development efforts.
+On the other hand, the reductions in cycle time and effort resulting from improved quality outweigh the marginal increases from achieving more process maturity.
+  \item \textbf{Relevance to our work}:
+  It can aid our research through better understanding of how various factors can influence the software development processes, thus giving more value to our own research (i.e.
+being able to automatically determine issue quality could improve better issue writing guidelines/better rules to be enforced, thus reduced triaging and development costs).
+\end{itemize}
+
+\textbf{Where should the bugs be fixed?-more accurate information retrieval-based bug localization based on bug reports}\cite{zhou2012should}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  The main goal of the paper was to implement a tool that, based on a bug report, could accurately select a number of files where the developer needs to make the necessary changes to fix the issue.
+They tried to answer 4 main research questions: how many bugs can be successfully lovated by BugLocator, does the revised VSM improve bug localization accuracy, does considering similar bugs improve localization accuracy, can bugLocator outperform other similar methods.
+  \item \textbf{What was the method?}
+  The tool firstly performed a textual analysis, looking for similarities between the bug report description and the source code files.
+Then, it analyzed previous bugs in the repository to find the most similar ones, thus being able to find which files ought to be changed.
+Lastly, it assigned scores to similar files, the ones with bigger sizes obtaining higher scores as they are more likely to contain bugs.
+They collected the necessary data from Bugzilla projects and then performed the evaluation.
+  \item \textbf{What did they learn?}
+  The buglocator can locate a large percentage of bugs analysing just a small set of source code files.
+Secondly, the revised VSM outperforms the standard VSM.
+Moreover, similar bugs can improve the localization accuracy only to a certain extent, while the locator outperformed every other competitor on a multitude of projects.
+  \item \textbf{Relevance to our work}:
+  We can try to use BugLocator and even include it in our research as it gives a direct correlation between bug reports and development effort (thus reduced costs).
+Thus, we can infer even more possible hypotheses regarding our issues’ quality.
+\end{itemize}
+
+\textbf{}\cite{}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
+
+\textbf{}\cite{}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
+
+\textbf{}\cite{}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
+
+\textbf{}\cite{}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
+
+\textbf{}\cite{}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
+
+\textbf{}\cite{}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
 \end{itemize}

### 2017-11-15 proposal/mprop.tex
Add paper on duplicate bug reports

@@
 
-\textbf{}\cite{}:
+\textbf{Analyzing and Relating Bug Report Data for Feature Tracking}\cite{fischer2003analyzing}:
 \begin{itemize}
   \item \textbf{What were the goals?}
+  The main goal of the paper was to analyze the proximity of software features based on modification and problem report data.
   \item \textbf{What was the method?}
+  They employed a method to track features by analyzing and relating bug report data filtered from a release history database.
+Features are instrumented and tracked, relationships of modification and problem reports to these features are established, and tracked features are visualized to illustrate their otherwise hidden dependencies.
   \item \textbf{What did they learn?}
+  The authors’ approach suggest first to instrument and track features, then establish the relationships of modification and problem reports to these features and lastly visualize the tracked features for illustrating their non apparent dependencies.
   \item \textbf{Relevance to our work}:
+  This paper can give us insight into how bug reports can influence feature implementation throughout the lifetime of the ticket. 
 \end{itemize}
 
-\textbf{}\cite{}:
+\textbf{Duplicate Bug Reports Considered Harmful... Really?}\cite{bettenburg2008duplicate}:
 \begin{itemize}
   \item \textbf{What were the goals?}
+  The authors wanted to test two main hypotheses, and these were: duplicate bug reports provide developers with information that was not present in the original report and the information in bug duplicates can improve automated triaging techniques.
   \item \textbf{What was the method?}
+  They collected big amounts of data from the Eclipse open source project in XML form.
+Then, they ran different kinds of textual and statistical analysis on the data to find answers to their research questions.
   \item \textbf{What did they learn?}
+  They reached the conclusion that bug duplicates contain information that is not present in the master reports.
+This additional data can be helpful for developers and it can also aid automated triaging techniques (e.g.
+decide who to assign a bug to).
   \item \textbf{Relevance to our work}:
+  The findings presented in this paper could potentially make us consider duplicate tickets in a different way (i.e.
+do not treat it as disposable but analyze it and see if it maybe adds more information to the original/master report).
 \end{itemize}

### 2017-11-15 proposal/mprop.tex
Add paper on bug tossing graphs

@@
 
-\textbf{}\cite{}:
+\textbf{Summarizing Software Artifacts: A Case Study of Bug Reports}\cite{rastkar2010summarizing}:
 \begin{itemize}
   \item \textbf{What were the goals?}
+  The main goal of the research was to determine if software artifacts could be summarized effectively and automatically so that developers would need only to analyze summaries instead of full software artifacts (i.e.
+in our case, bug reports).
   \item \textbf{What was the method?}
+  Firstly, they collected data to analyze from 4 different open source projects (Eclipse, Mozilla, Gnome, KDE).
+Then, they asked the volunteers (i.e.
+university students) to annotate the bug reports - write a summary of maximum 250 words in their own sentences.
+These human-produced annotations were then used by algorithms to learn how to effectively summarize a bug report.
+Afterwards, the authors asked the end users of these bug reports, the software developers, to rate the summaries against the original bug reports.
   \item \textbf{What did they learn?}
+  They learned that existing conversation-based extractive summary generators trained on bug reports produce the best results. 
   \item \textbf{Relevance to our work}:
+  As the paper revolves around conversations that are attached to a bug (i.e.
+comments) instead of the actual description of the bug, we can apply the technique described here maybe to generate summaries and analyze them as well in the overall context of ticket quality (maybe together with some sentiment analysis).
 \end{itemize}
 
-\textbf{}\cite{}:
+\textbf{Improving Bug Triage with Bug Tossing Graphs}\cite{jeong2009improving}:
 \begin{itemize}
   \item \textbf{What were the goals?}
+  The two main goals of the authors, through their bug tossing graph idea (based on the Markov property), were to discover developer networks and team structures, as well as help to better assign developers to bug reports.
   \item \textbf{What was the method?}
+  They analyzed 145.000 bug reports from Eclipse and 300.000 from Mozilla.
+Then, using statistical analysis on the bug reports in order to find evolution histories and changes throughout the lifetime of the reports, they created the bug tossing graph.
   \item \textbf{What did they learn?}
+  They learned that it takes a long time to assign and toss bugs.
+Additionally, they learned that their model reduces tossing steps by up to 72\% and improved the automatic bug assignment by up to 23\%.
   \item \textbf{Relevance to our work}:
+  First paper on importance of tossing and its impact on the software development process.
+It might prove useful as we shall also inspect tossing and bug assignment in our own research in order to determine ticket quality (i.e.
+maybe tossing actually reduces the quality of the ticket?).
 \end{itemize}

### 2017-11-15 proposal/mprop.tex
Add paper on bug tracking systems

@@
 
-\textbf{}\cite{}:
+\textbf{Towards the Next Generation of Bug Tracking Systems}\cite{just2008towards}:
 \begin{itemize}
   \item \textbf{What were the goals?}
+  The authors wanted to determine what makes for good bug reports and, more specifically, how the reporting environment can be changed to best suit the developers’ needs (and everyone else involved in the software project).
   \item \textbf{What was the method?}
+  They first launched a survey to developers from Eclipse, Mozilla and Apache open source projects from which they received 175 comments back.
+Then, they applied a card sort in order to organize the comments into hierarchies to deduce a higher level of abstraction and identify common patterns.
   \item \textbf{What did they learn?}
+  They found 7 main topics of improvement for bug tracking systems: provide tool support for users to collect and prepare information that developers need, find volunteers to translate bug reports filed in foreign languages, provide different user interfaces for each user level and give cues to inexperienced reporters on what to report and best practices, reward reporters when they do a good job, integrate reputation into user profiles to mark experienced reporters, provide powerful and easy to use tools to search bug reports, encourage users to submit additional details (provide tools for merging bugs).
   \item \textbf{Relevance to our work}:
+  This is an important paper to our research as it presents, from open source developers’ perspective, how bug reporting and bug tracking systems should behave.
+This research gives us various topics to concentrate on when analyzing the quality of tickets.
 \end{itemize}

### 2017-11-15 proposal/mprop.tex
Add paper on bug report quality in Eclipse

@@
 
-\textbf{}\cite{}:
+\textbf{Quality of Bug Reports in Eclipse}\cite{bettenburg2007quality}:
 \begin{itemize}
   \item \textbf{What were the goals?}
+  The authors were looking to find the most important factors that determine the quality of a bug report. 
   \item \textbf{What was the method?}
+  They conducted a survey with Eclipse developers on what they find most important and helpful in a bug report.
+Another goal was to develop a tool that could  automatically measure the quality in bug reports based on the best practices for writing such reports (Eclipse guidelines).
   \item \textbf{What did they learn?}
+  They learned that well written bug reports will most likely get more attention from developers.
+Moreover, the most important factors which influence  ticket quality are stack traces and steps to reproduce.
+On the other hand, the most harmful information in bug reports are errors in steps to reproduce, incomplete information and wrong observed behavior.
+Regarding quzilla, they measured that the tool achieved an accuracy of 42\% which indicates that it could, on the long term, ensure some standard quality when reporting and creating new tickets.
   \item \textbf{Relevance to our work}:
+  It is mostly the same topic as our research, but we want to use statistical analysis instead of interviews/questionnaires as well as investigate tickets from multiple open source repositories, not just one.
+However, the findings presented here could serve as clues on where to search for factors that influence ticket quality.
 \end{itemize}

### 2017-11-15 proposal/mprop.tex
Add paper on software process data quality and characteristics

@@
 \subsection{Data Quality Metrics}
+
+\textbf{Software Process Data Quality and Characteristics}\cite{bachmann2009software}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The authors are trying to investigate different software process data
+    (e.g. bug tracking databases, version control systems logs) in order to
+    infer quality and characteristics. Then, they want to compute measures
+    and discuss the issues that arise from these observations.
+  \item \textbf{What was the method?}
+    They examined 6 software projects, 5 of which were open source, by extracting
+    the SVN and CSV logs, as well as the content of the bug tracker databases. Then,
+    they tried to link the logs with the contents of the bug tracker databases as they
+    are not integrated by default. 
+  \item \textbf{What did they learn?}
+    Firstly, the closed source project the authors examined showed much more data
+    quality as the open source counterparts, among which better average attachments 
+    per bug report, better average status changes per bug report or average commits
+    per bug report/developer. Moreover, the authors found that there is little linkage
+    between bug reports and version control logs, thus reducing the overall traceability.
+    Also, there is reduced quality in change logs as, for example, the Eclipse project
+    has more than 20\% empty commit messages. In conclusion, closed source projects will
+    probably exhibit improved data quality than open source ones, but data quality in general
+    differs from project to project.
+  \item \textbf{Relevance to our work}:
+    The analysis on data quality in open/closed source projects presented in this 
+    research is valuable to us as it presents various statistics on commits, bug report
+    structure and quality, as well as linkage between the two. We might apply the techniques
+    in our own research on ticket quality.
+\end{itemize}
 

### 2017-11-15 proposal/mprop.tex
Add paper on extracting info from bug reports

@@
 
+% TODO: complete this paper
 \textbf{Product perspective on total 
@@
 \subsection{Issue Quality}
+
+\textbf{Extracting Structural Information from Bug Reports}\cite{bettenburg2008extracting}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The authors try to present a tool called infoZilla that can accurately
+    extract different types of information (e.g. stack traces, source code
+    fragments) from bug reports.
+  \item \textbf{What was the method?}
+    They selected a few categories of information that both infoZilla could
+    successfully extract from bug reports and that are of most interest to developers. Thus,
+    the categories selected are:
+      \begin{itemize}
+        \item patches;
+        \item stack traces;
+        \item source code;
+        \item enumerations.
+      \end{itemize}
+    Then, they ran the tool on tickets and evaluated the overall accuracy.
+  \item \textbf{What did they learn?}
+    After developing the tool to inspect such elements and retrieve them, 
+    they evaluated it on over 160000 Eclipse bug reports. For all categories, infoZilla
+    achieved over 97\% accuracy. 
+  \item \textbf{Relevance to our work}:
+    If we could manage to get this tool and use it in our own research, it would be
+    beneficial as we could extract efficiently different types of information we are
+    interested in testing ticket quality (e.g. stack traces).
+\end{itemize}
 

### 2017-11-15 proposal/mprop.tex
Add paper on stack traces in bug reports

@@
     They examined 6 software projects, 5 of which were open source, by extracting
-    the SVN and CSV logs, as well as the content of the bug tracker databases. Then,
+    the SVN and CVS logs, as well as the content of the bug tracker databases. Then,
     they tried to link the logs with the contents of the bug tracker databases as they
@@
 \subsection{Issue Quality}
+
+\textbf{Do Stack Traces Help Developers Fix Bugs?}\cite{schroter2010stack}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the paper was to identify if including a stack trace in a 
+    bug report would help the developers fix the issue quicker. They divided their
+    investigations in order to follow 4 research questions:
+      \begin{itemize}
+        \item are bugs fixed in methods in stack traces;
+        \item how far down the stack to trace;
+        \item are two or more stack traces better than one;
+        \item do stack traces help speed up debugging.
+  \item \textbf{What was the method?}
+    They conducted their investigation on the Eclipse project which is developed in
+    Java. Then, they extracted stack traces from bug reports using the infoZilla tool.
+    Afterwards, they linked the stack traces (and thus the corresponding bug report)
+    to changes in the source code (change logs) by mining the version repository of the
+    Eclipse project.
+  \item \textbf{What did they learn?}
+    They found answers to all their research questions, and are as follows:
+      \begin{itemize}
+        \item around 60\% of the bugs that contained stack traces were fixed in 
+        one of the methods in the frames;
+        \item around 40\% were fixed in the first stack frame, around 80\% were fixed
+        within the top 6 frames, while close to 90\% of the bugs were fixed within top 10 stack frames;
+        \item having more than one stack trace usually helped more than only a single one;
+        \item bug reports containing stack traces usually have a shorter lifetime, thus
+        speeding up the debugging process.
+      \end{itemize}
+  \item \textbf{Relevance to our work}:
+    Stack traces are one of the types of information we are investigating in our research
+    and it is very useful to have such a study back up the statement that stack traces are
+    valuable for developers so that they speed up the issue fixing process.
+\end{itemize}
 

### 2017-11-15 proposal/mprop.tex
Fix bug in rendering tex file
Finish paper on data quality assessment

@@
 
-% TODO: complete this paper
-\textbf{Product perspective on total 
-        Data Quality Assessment}\cite{wang1998product}:
+\textbf{Product perspective on total Data Quality Assessment}\cite{wang1998product}:
 \begin{itemize}
   \item \textbf{What were the goals?}
-
+    The author wanted to create a Total Data Quality Management methodology so that
+    high quality information products could be delivered to information consumers.
   \item \textbf{What was the method?}
-    They created the TDQM methodology which is based on accumulated research 
-    and extended 
+    The research presents us, firstly, with a couple of definitions for the methodology:
+      \begin{itemize}
+        \item TDQM cycle - define, measure, analyze and improve information quality continuously;
+        \item information product - information output from an information manufacturing system
+          that has value to the information consumer;
+        \item information quality - fitness for use by information consumers.
+      \end{itemize}
+    Then, the author presents the four steps in order to successfully implement the TDQM methodology:
+      \begin{itemize}
+        \item clearly articulate the information product;
+        \item establish several roles that would be in charge of the information product management;
+        \item teach information quality assessment and management skills to all IP constituencies;
+        \item institutionalize continuous information product improvement.
+      \end{itemize}
   \item \textbf{What did they learn?}
-  \item \textbf{Relevance to our work}:
+    The author learned that this methodology is filling a gap in the information quality
+    world and that it could help organizations better manage the information quality of their
+    information products.
+  \item \textbf{Relevance to our work}
+    This article could prove helpful to our own research as the methodology presented could help
+    us in detecting if there is data quality in the projects we will be analyzing.
 \end{itemize}
@@
         \item do stack traces help speed up debugging.
+      \end{itemize}
   \item \textbf{What was the method?}

### 2017-11-15 proposal/mprop.tex
Add where should we fix this bug paper

@@
 \subsection{Issue Quality}
+
+\textbf{Where should we fix this bug?}\cite{kim2013should}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the paper was to aid developers in easily finding where to
+    apply the necessary changes in order to fix a bug. The authors wanted to bridge
+    this gap by creating a two-phase recommendation model that would locate the locations
+    where the fixes need to be applied based on the corresponding bug reports.
+  \item \textbf{What was the method?}
+    They divided the work into multiple stages:
+      \begin{itemize}
+        \item firstly, they did a feature extraction on the bug reports (e.g. extract
+        description, metadata, summary);
+        \item in order to predict the locations of the necessary fixes, the one-phase
+        recommendation model was put into place - this model would be trained on collected
+        bug reports and then, when given a new bug report, it would try to localize the 
+        files that need to be changed automatically;
+        \item last step was to implement the two-phase recommendation model which basically
+        has two classification phases - binary and multiclass:
+          \begin{itemize}
+            \item binary phase filters out uninformative bug reports before predicting the
+            files to fix;
+            \item multiclass phase where the previously filtered bug reports are used as
+            training data and only after that new bug reports can be analyzed and files to be
+            changed recommended.
+          \end{itemize}
+      \end{itemize}
+  \item \textbf{What did they learn?}
+    Evaluating the model yielded a 70\% accuracy in pointing to the correct files
+    to be fixed, as long as the algorithm actually recommended any locations. However, the authors
+    acknowledge that the approach needs extra work, especially in fine-grained defect 
+    localization, performance improvement and bug triaging.
+  \item \textbf{Relevance to our work}:
+    The research shows interesting points regarding time-to-fix-bug and bug report
+    contents, thus it can give us an insight into how ticket quality can affect that 
+    time to fix the bug (in the case of this paper it would mean to successfully pass the first
+    phase of the recommendation model so that fix locations could be proposed).
+\end{itemize}
 

### 2017-11-20 proposal/mprop.tex
Add skeleton for paper and bib entry to fuzzy code search to link code fragments in discussions to source code paper

@@
 \subsection{Issue Quality}
+
+\textbf{Using fuzzy code search to link code fragments in discussions to source code}\cite{bettenburg2012using}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the paper is to find an approach that improves on
+    previous methods to link source code fragments in discussions to source code.
+    These previous methods were mainly based on information retrieval or 
+    change log analysis.
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
+
+% \textbf{}\cite{}:
+% \begin{itemize}
+%   \item \textbf{What were the goals?}
+%   \item \textbf{What was the method?}
+%   \item \textbf{What did they learn?}
+%   \item \textbf{Relevance to our work}:
+% \end{itemize}
+
+% \textbf{}\cite{}:
+% \begin{itemize}
+%   \item \textbf{What were the goals?}
+%   \item \textbf{What was the method?}
+%   \item \textbf{What did they learn?}
+%   \item \textbf{Relevance to our work}:
+% \end{itemize}
 

### 2017-11-20 proposal/mprop.tex
Finish paper on fuzzy code linkage paper

@@
     These previous methods were mainly based on information retrieval or 
-    change log analysis.
-  \item \textbf{What was the method?}
-  \item \textbf{What did they learn?}
-  \item \textbf{Relevance to our work}:
+    change log analysis. The main reason behind the authors' goal was
+    that a successful tool which could accomplish the goal would drastically
+    improve traceability in a project.
+  \item \textbf{What was the method?}
+    They created a tool based on fuzzy code search that could parse bug reports
+    discussions and, then, match the locations in the source code where those
+    code fragments belong to. The authors conducted the evaluation on the Eclipse
+    open source project after developing the 2 stages of the algorithm:
+      \begin{itemize}
+        \item they first use infoZilla, presented in \cite{bettenburg2008extracting},
+        to extract source code from documents belonging to a document archive;
+        \item then they perform a fuzzy textual search using a token-based clone
+        detection tool;
+        \item finally, they analyze all clone groups that associate clone pairs with
+        extracted code fragments to source code files; then, a traceability link is created,
+        which is basically a tuple containing a clone group ID and file paths corresponding
+        to the corresponding source code files.
+      \end{itemize}
+  \item \textbf{What did they learn?}
+    First of all, as many software projects have large code bases, creating such 
+    traceability links is no trivial task. Moreover, they noticed an increase of 20.01\%
+    in total traceability links between issue reports and source code compared to state of the art
+    technique (which is also most used one), change log analysis. Thus, there is room for
+    improvement in this area.
+  \item \textbf{Relevance to our work}:
+    If we'd decide to use this approach, we can find out even more information about
+    quality in issue reports/tickets as we can also analyze the source code files necessary
+    to fix that specific issue. This, combined with infoZilla, could prove valuable for our
+    mining and extraction processes.
 \end{itemize}

### 2017-11-20 proposal/mprop.tex
Add paper on bug report severity analysis

@@
 
-% \textbf{}\cite{}:
-% \begin{itemize}
-%   \item \textbf{What were the goals?}
-%   \item \textbf{What was the method?}
-%   \item \textbf{What did they learn?}
-%   \item \textbf{Relevance to our work}:
-% \end{itemize}
+\textbf{Predicting the severity of a reported bug}\cite{lamkanfi2010predicting}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The main goal of the research was to determine if, using textual analysis, one can
+    predict the severity of a bug. This main research question was further divided into
+    4 RQs:
+      \begin{itemize}
+        \item which terms in the textual description could serve as good indicators for
+        the bug severity;
+        \item what types of textual fields (e.g. summary, description) serve indicate the
+        bug severity best;
+        \item how many sample does one need to train an accurate predictor;
+        \item is it better to have a specialized predictor for each component or combine
+        bug reports over multiple components.
+      \end{itemize}
+  \item \textbf{What was the method?}
+    The authors conducted their research on the Mozilla, Eclipse and GNOME project. The 
+    approach can be divided into 5 steps:
+      \begin{itemize}
+        \item extract and organize bug reports;
+        \item preprocess bug reports (i.e. tokenization, stop word removal and stemming);
+        \item train the classifier on multiple datasets of bug reports (they used a ratio of
+        70\% - training, 30\% - evaluation);
+        \item apply the trained classifier on the evaluation set.
+      \end{itemize}
+        Then, they used precision and recall to evaluate their results.
+  \item \textbf{What did they learn?}
+    The authors managed to answer all their 4 research questions:
+      \begin{itemize}
+        \item terms such as deadlock, hand, crash, memory or segfault usually indicate a severe bug;
+        however, there are other terms that can indicate the opposite (i.e. non-severe bugs),
+        such as typo;
+        \item they switched from analysing only the one-line summary to analysing the whole
+        textual description as it contains more detailed information, thus the model can be
+        trained better; however, when they analysed the results and noticed that they had a large
+        number of false positives, which made them switch back to one-line summaries;
+        \item the classifier needs a large number of datasets in order to predict better on the
+        evaluation set;
+        \item it mainly depends on the type of project and how it is structured; thus, in Mozilla
+        and GNOME, which share problem-specific characteristics over different components, using a 
+        predictor across components sees improvements; however, the dataset needs to be even larger,
+        otherwise the performance starts to decrease.
+      \end{itemize}
+  \item \textbf{Relevance to our work}:
+    The authors' findings could help us in better understanding textual description analysis and how
+    it can indicate various aspects about a ticket, such as severity. Thus, we can apply the technique
+    described in order to differentiate between severe and non-severe bug reports so that we can 
+    focus on a specific category in our own research, if we want that.
+\end{itemize}
 

### 2017-11-20 proposal/mprop.tex
Add bib entry and skeleton for information needs in bug reports paper
Added some comments and structure suggestions.

@@
 \usepackage{graphicx}
+
+\usepackage{natbib}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}\label{intro}
-briefly explain the context of the project problem
+
+% 2 - 3 pages tops
+
+\begin{itemize}
+\item Background briefly explain the context of the project problem
+\item Problem statement and justification. Clearly state the problem to be addressed in your forthcoming project.
+  Explain why it would be worthwhile to solve this problem.
+
+\item Research questions and contributions
+\item Structure of the rest of the document
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Background Survey}
+
+% 10 - 12 pages
 
@@
 
-\subsection{A subsection}
-Please note your proposal need not follow the included section headings; this is only a suggested structure. Also add subsections etc as required
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Statement of Problem}
-
-Clearly state the problem to be addressed in your forthcoming project.
-Explain why it would be worthwhile to solve this problem.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background Survey}
-
-\subsection{Introduction}
-
-\subsection{What was covered and why}
-
-\subsection{How papers were found; what terms were searched for + snowballing}
+\subsection{Study Design}
+
+What was covered and why; How papers were found; what terms were searched for + snowballing.
 
 \subsection{Data Quality Metrics}
+
+2nd and 3rd papers both investigate what quality means.
+
+Several authors have investigated the \emph{meaning} of quality.   \cite{sucansuch2018} said ..
+
+Several authors have investigated the application quality metrics to ticket data.
+
+\citet{bachmann2009software} attempted to compute quality metrics for a range of project data sources, including bug tracking databases, version control logs.
+They attempted to link bug tracking and change logs and showed that the closed source project investigated reported higher quality metrics.
+
+\citet{}
 
@@
 
-% \textbf{}\cite{}:
-% \begin{itemize}
-%   \item \textbf{What were the goals?}
-%   \item \textbf{What was the method?}
-%   \item \textbf{What did they learn?}
-%   \item \textbf{Relevance to our work}:
-% \end{itemize}
+\textbf{Information needs in bug reports: improving cooperation between developers and users}\cite{breu2010information}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+
+  \item \textbf{What was the method?}
+  \item \textbf{What did they learn?}
+  \item \textbf{Relevance to our work}:
+\end{itemize}
 
@@
 
+% 3- 4 pages
+
+What are we actually going to do?
+
+Research questions, outline experimental design, independent variables, dependent variables.
+
 state how you propose to solve the software development problem. Show that your proposed approach is feasible, but identify any risks.
@@
 
+% 1 - 2 pages  structure as work packages (don't bother with a chart).
+
 show how you plan to organize your work, identifying intermediate deliverables and dates.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{plain}
+\bibliographystyle{plainnat}
 \bibliography{mprop}

### 2017-11-25 proposal/mprop.tex
Work on study design

@@
 
-% \textbf{}\cite{}:
-% \begin{itemize}
-%   \item \textbf{What were the goals?}
-%   \item \textbf{What was the method?}
-%   \item \textbf{What did they learn?}
-%   \item \textbf{Relevance to our work}:
-% \end{itemize}
-
 \subsection{Study Design}
+
+In order to conduct a thorough background survey, several topics needed to be 
+explored, among which the most important were:
+  \begin{itemize}
+    \item data quality and metrics;
+    \item issue/ticket quality;
+    \item waste in software projects;
+    \item sentiment analysis.
+  \end{itemize}
+
+The main sources of information when searching for papers were Google Scholar, 
+ACM digital library and IEEE Xplore digital library. The first step in the 
+literature review process was finding relevant papers that could aid us in
+our research and splitting them into the categories mentioned above. There were
+a couple of key search phrases that I started with (along with slight 
+variations):
+  \begin{itemize}
+    \item software data quality;
+    \item software data quality metrics;
+    \item data quality in software projects;
+    \item issue quality in software projects;
+    \item ticket quality software;
+    \item sentiment analysis;
+    \item software project communication waste.
+  \end{itemize}
+
+Then, after reading the papers retrieved when searching for the above-mentioned
+phrases, I also applied the snowballing research technique as per Dr. Storer's 
+advice. This extra step was helpful and allowed me to easily find linked 
+papers and correlate them in this literature review.
+
+Moreover, when reading papers, one key aspect for selecting and including it
+in the literature review was citation count. Thus, after finding the most 
+cited papers, I then checked to see the journal where it was published so that
+we would only have material from the most important journals.
+
+Even though the literature review contains around 40 papers, there were
+around 80 papers that were reviewed but roughly half of them were excluded 
+because they eventually proved to not be so relevant to our research.
+
+Firstly, we will deal with a large volume of tickets and information extracted 
+from software projects and the tools that revolve around them, such as issue 
+trackers and version control systems. Thus, \emph{data quality} is an important 
+topic that needed to be explored in order to infer appropriate conclusions.
+
+As the main objective of our research is to determine what makes for a good 
+quality ticket, we needed to explore what was previously done in
 

### 2017-11-26 proposal/mprop.tex
Add more information to study design

@@
   \end{itemize}
+
+Firsly, we will deal with a large volume of tickets and information extracted 
+from software projects and the tools that revolve around them, such as issue 
+trackers and version control systems. Thus, \emph{data quality} is an important 
+topic that needed to be explored in order to infer appropriate conclusions.
+
+As the main objective of our research is to determine what makes for a good 
+quality ticket, we needed to explore what was previously done in
 
@@
 because they eventually proved to not be so relevant to our research.
-
-Firstly, we will deal with a large volume of tickets and information extracted 
-from software projects and the tools that revolve around them, such as issue 
-trackers and version control systems. Thus, \emph{data quality} is an important 
-topic that needed to be explored in order to infer appropriate conclusions.
-
-As the main objective of our research is to determine what makes for a good 
-quality ticket, we needed to explore what was previously done in
 

### 2017-11-26 proposal/mprop.tex
Work on study design

--- 2017-11-25 proposal/mprop.tex
@@
 \section{Background Survey}
-
 % 10 - 12 pages
@@
   \end{itemize}
+
+Firstly, we will deal with a large volume of tickets and information extracted 
+from software projects and the tools that revolve around them, such as issue 
+trackers and version control systems. Thus, \emph{data quality} is an important 
+topic that needed to be explored in order to infer appropriate conclusions.
+
+We analyzed data quality mainly in software organizations and looked at what metrics
+are most useful when trying to perform measurements. We also tried to find different
+methodologies that either measure data quality or calculate the impact of poor data
+quality on the software project.
+
+Secondly, probably the topic of most interest to our research is \emph{issue quality}.
+This field is mainly concerned with software tickets and their characteristics: how
+important
 
@@
 
-Firstly, we will deal with a large volume of tickets and information extracted 
-from software projects and the tools that revolve around them, such as issue 
-trackers and version control systems. Thus, \emph{data quality} is an important 
-topic that needed to be explored in order to infer appropriate conclusions.
-
-As the main objective of our research is to determine what makes for a good 
-quality ticket, we needed to explore what was previously done in
-
-What was covered and why; How papers were found; what terms were searched for + snowballing.
+What was covered and why; How papers were found; what terms were searched 
+for + snowballing.
 

### 2017-11-26 proposal/mprop.tex
Work on study design

@@
 This field is mainly concerned with software tickets and their characteristics: how
-important
+important are issue trackers to a software project, what makes for a good bug report,
+what impact does bad triaging have etc. While reading multipe
 

### 2017-11-26 proposal/mprop.tex
Finish discussion on why topics of interest were selected

@@
 important are issue trackers to a software project, what makes for a good bug report,
-what impact does bad triaging have etc. While reading multipe
+what impact does bad triaging have etc. As we are interested in finding out what
+features are most important in improving the quality of a ticket, the issue quality
+literature I have reviewed proved to be beneficial and provided valuable insight into
+how other researchers tried to approach this problem.
+
+The third topic was waste in software projects and how it impacts them. We needed to
+look into various communication and tool-related waste in software projects because
+having a project with a considerable amount of waste might affect our results and
+compromise the evaluation process. We investigated researches that looked into what
+are the main types of waste in software projects and how it can be avoided so that
+we could apply the findings into selecting the projects.
+
+Last but not least, we did a literature review on sentiment analysis as well because
+we will inspect, among other components of a ticket, comments - we want to analyze
+the textual representation of comments and see if the overall sentiment might influence
+the time it takes to close a ticket (i.e. maybe a negative conversation in comments 
+might increase the time it takes to solve the issue).
 
@@
 our research and splitting them into the categories mentioned above. There were
-a couple of key search phrases that I started with (along with slight 
-variations):
+a couple of key search phrases that I started with (along with slight variations):
   \begin{itemize}

### 2017-11-26 proposal/mprop.tex
Complete study design

@@
 we will inspect, among other components of a ticket, comments - we want to analyze
-the textual representation of comments and see if the overall sentiment might influence
+the textual representation of comments and see if the overall sentiment influences
 the time it takes to close a ticket (i.e. maybe a negative conversation in comments 
@@
 because they eventually proved to not be so relevant to our research.
-
-What was covered and why; How papers were found; what terms were searched 
-for + snowballing.
 

### 2017-11-26 proposal/mprop.tex
Combine first two papers in data quality

@@
 
-Last but not least, we did a literature review on sentiment analysis as well because
-we will inspect, among other components of a ticket, comments - we want to analyze
-the textual representation of comments and see if the overall sentiment influences
-the time it takes to close a ticket (i.e. maybe a negative conversation in comments 
-might increase the time it takes to solve the issue).
+Last but not least, we did a literature review on sentiment analysis as well 
+because we will inspect, among other components of a ticket, comments - we want 
+to analyze the textual representation of comments and see if the overall 
+sentiment influences the time it takes to close a ticket (i.e. maybe a negative 
+conversation in comments might increase the time it takes to solve the issue).
 
@@
 
-2nd and 3rd papers both investigate what quality means.
-
-Several authors have investigated the \emph{meaning} of quality.   \cite{sucansuch2018} said ..
-
-Several authors have investigated the application quality metrics to ticket data.
-
-\citet{bachmann2009software} attempted to compute quality metrics for a range of project data sources, including bug tracking databases, version control logs.
-They attempted to link bug tracking and change logs and showed that the closed source project investigated reported higher quality metrics.
-
-\citet{}
-
-\textbf{Software Process Data Quality and Characteristics}\cite{bachmann2009software}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors are trying to investigate different software process data
-    (e.g. bug tracking databases, version control systems logs) in order to
-    infer quality and characteristics. Then, they want to compute measures
-    and discuss the issues that arise from these observations.
-  \item \textbf{What was the method?}
-    They examined 6 software projects, 5 of which were open source, by extracting
-    the SVN and CVS logs, as well as the content of the bug tracker databases. Then,
-    they tried to link the logs with the contents of the bug tracker databases as they
-    are not integrated by default. 
-  \item \textbf{What did they learn?}
-    Firstly, the closed source project the authors examined showed much more data
-    quality as the open source counterparts, among which better average attachments 
-    per bug report, better average status changes per bug report or average commits
-    per bug report/developer. Moreover, the authors found that there is little linkage
-    between bug reports and version control logs, thus reducing the overall traceability.
-    Also, there is reduced quality in change logs as, for example, the Eclipse project
-    has more than 20\% empty commit messages. In conclusion, closed source projects will
-    probably exhibit improved data quality than open source ones, but data quality in general
-    differs from project to project.
-  \item \textbf{Relevance to our work}:
-    The analysis on data quality in open/closed source projects presented in this 
-    research is valuable to us as it presents various statistics on commits, bug report
-    structure and quality, as well as linkage between the two. We might apply the techniques
-    in our own research on ticket quality.
-\end{itemize}
+Several authors have investigated the \emph{meaning} of data quality, how to 
+\emph{measure} it and what \emph{impact} poor data quality has on software 
+projects.
+
+\citet{bachmann2009software} conducted a thorough investigation of several
+software projects, both open source (5 projects) as well as closed source (1 
+project), in order to infer what determines if it has quality. They selected 
+various sources of information, among which bug tracking 
+databases and version control systems logs, and examined SVN logs, CVS logs
+and the content of the bug tracker databases, in the end trying to link 
+the logs with the bug tracker contents as they are not integrated by default. 
+On the other hand, \citet{strong1997data} conducted a qualitative analysis
+instead of quantitative by collecting data from 42 data quality projects by 
+interviewing custodians, customers and managers. They analyzed each project
+using the data quality dimensions as content analysis codes.
+
+The first study came to several conclusions, among which:
+  \begin{itemize}
+    \item closed source software projects usually exhibit better data quality 
+    (i.e. better average number of attachments, better average status changes, 
+    better average number of commits per bug report);
+    \item reduced traceability between bug reports and version control logs
+    due to scarce linkage between the two;
+    \item open source projects exhibit reduced quality in change logs as,
+    for example, the Eclipse project has over 20\% empty commit messages.
+  \end{itemize}
+However, the second study reached the conclusion that representational data 
+quality dimensions are underlying causes of accessibility data quality problem
+patterns. The authors also found out that three underlying causes for users'
+complaints regarding data not supporting their tasks are incomplete data, 
+inadequately defined or measured data and data that could not be appropriately
+aggregated.
+
+Several authors have investigated the application quality metrics to ticket 
+data.
 
@@
 
-\textbf{Organizational Impact of 
-        Information Quality}\cite{gorla2010organizational}:
+\textbf{Organizational Impact of Information Quality}
+\cite{gorla2010organizational}:
 \begin{itemize}

### 2017-11-26 proposal/mprop.tex
Combine papers on measuring data quality

@@
 
-Several authors have investigated the \emph{meaning} of data quality, how to 
-\emph{measure} it and what \emph{impact} poor data quality has on software 
-projects.
+Several authors have investigated the \emph{meaning} of data quality and
+what characteristics define it.
 
@@
   \end{itemize}
+
 However, the second study reached the conclusion that representational data 
@@
 
-Several authors have investigated the application quality metrics to ticket 
-data.
-
-\textbf{Data Quality in Context}\cite{strong1997data}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the authors was to analyze data quality in different 
-    organizations, observe data quality problem patterns as well as see 
-    its implications.
-  \item \textbf{What was the method?}
-    They performed a qualitative analysis, examining 42 data quality projects 
-    from 3 organizations. They collected data via interviews of data procedures,
-    custodians, customers and managers. The authors analysed each project using
-    the data quality dimensions as content analysis codes. 
-  \item \textbf{What did they learn?}
-    One thing that the authors learned is that representational data quality 
-    dimensions are underlying causes of accessibility data quality problem 
-    patterns. Also, they observed three underlying causes for users' complaints
-    regarding data not supporting their tasks:
-      \begin{itemize}
-        \item incomplete data;
-        \item inadequately defined or measured data;
-        \item data that could not be appropriately aggregated.
-      \end{itemize}
-  \item \textbf{Relevance to our work}: this paper brings valuable insight into
-    major data quality issues and patterns, information which we can apply in 
-    our own research.
-\end{itemize}
-
-\textbf{Data Quality Assessment}\cite{pipino2002data}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the authors is to present ways of developing usable data
-    quality metrics that organizations can implement in their own internal 
-    processes.
-  \item \textbf{What was the method?}
-    They have researched previous methods of assessing data quality in information
-    systems and they formulated general advice that can be directly implemented
-    by organizations in their processes.
-  \item \textbf{What did they learn?}
-    They learned that there is no universal approach to assessing data quality
-    as it heavily depends on the context where it is analysed.
-  \item \textbf{Relevance to our work}: it shows how one can effectively measure
-    data quality in information systems, thus we can apply it on the quality of
-    the tickets we are analysing.
-\end{itemize}
-
-\textbf{Product perspective on total Data Quality Assessment}\cite{wang1998product}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The author wanted to create a Total Data Quality Management methodology so that
-    high quality information products could be delivered to information consumers.
-  \item \textbf{What was the method?}
-    The research presents us, firstly, with a couple of definitions for the methodology:
-      \begin{itemize}
-        \item TDQM cycle - define, measure, analyze and improve information quality continuously;
-        \item information product - information output from an information manufacturing system
-          that has value to the information consumer;
-        \item information quality - fitness for use by information consumers.
-      \end{itemize}
-    Then, the author presents the four steps in order to successfully implement the TDQM methodology:
-      \begin{itemize}
-        \item clearly articulate the information product;
-        \item establish several roles that would be in charge of the information product management;
-        \item teach information quality assessment and management skills to all IP constituencies;
-        \item institutionalize continuous information product improvement.
-      \end{itemize}
-  \item \textbf{What did they learn?}
-    The author learned that this methodology is filling a gap in the information quality
-    world and that it could help organizations better manage the information quality of their
-    information products.
-  \item \textbf{Relevance to our work}
-    This article could prove helpful to our own research as the methodology presented could help
-    us in detecting if there is data quality in the projects we will be analyzing.
-\end{itemize}
+After defining what data quality is and what are its characteristics, the next 
+step would be how to measure data or information quality in a project.
+
+There are several research papers that try to find the answer, among which the 
+work of \citet{lee2002aimq}. The authors tried to define an overall model along 
+with an accompanying assessment instrument for quantifying information quality 
+in an organization. The methodology has 3 main steps that need to be followed 
+in order to apply it successfully:
+  \begin{itemize}
+    \item 2 $\times$ 2 model of what information quality means to managers;
+    \item questionnaire for measuring information quality along the dimensions
+    found in first step;
+    \item two analysis techniques for interpreting the assessments captured 
+    by the questionnaire.
+  \end{itemize} 
+After developing the technique, they applied it at 5 different organizations and
+found that the tool proved to be practical.
+
+Compared to the methodology proposed by \citet{lee2002aimq}, the solution found
+by \citet{Heinrich2007MetricsDataQuality} is quite different. Even though the 
+main goals were the same, the authors used a single metric, and that is 
+the metric for timeliness (i.e. whether the values of attributes still 
+correspond to the current state of their real world counterparts and whether 
+they are out of date). Thus, they applied the metric at a major German mobile 
+services provider. Due to some Data Quality issues the company was having, they 
+had lower mailing campaign success rates, but after applying the metrics, the 
+company was able to establish a direct connection between the results of
+measuring data quality and the success rates of campaigns.
+
+Another important area of data quality is what methodologies can be applied by
+organizations in order to improve it. There are several studies that tried to
+propose such methodologies. A general overview of such techniques was presented 
+by \citet{pipino2002data} - they wanted to present ways of developing usable 
+data quality methods that organizations can implement in their own internal 
+processes. After reviewing various techniques of assessing data quality in
+information systems, they reached the conclusion that there is no universal 
+approach to assess data quality as it heavily depends on the context where it is
+analysed.
+
+One such methodology examined by \citet{pipino2002data} is the technique 
+proposed by \citet{wang1998product} called Total Data Quality Management
+(abbreviated TDQM). Through this method, the authors wanted to help 
+organizations deliver high quality information products to information
+consumers by following the TDQM cycle - define, measure, analyse and improve
+information quality continuously. In order to do that, the research proposes
+4 steps: clearly articulate the information product, establish several roles
+that would be in charge of the information product management, teach information
+quality assessment and management skills to all information products 
+constituencies and, finally, institutionalize continuous information product 
+improvement. After developing the methodology, the authors conclude on a 
+confident note that their technique can fill a gap in the information quality
+environment.
 
@@
     when analysing the quality of the tickets we will mine.
-\end{itemize}
-
- \textbf{AIMQ}\cite{lee2002aimq}:
- \begin{itemize}
-   \item \textbf{What were the goals?}
-     The main challenge set by the authors was to develop an overall model
-     with an accompanying assessment instrument for quantifying information
-     quality.
-   \item \textbf{What was the method?}
-     They developed a methodology called AIM quality (hence the name AIMQ) which
-     they applied at 5 different organizations. It has 3 main components:
-      \begin{itemize}
-        \item 2 $\times$ 2 model of what information quality means to managers;
-        \item questionnaire for measuring information quality along the dimensions
-          found in first step;
-        \item two analysis techniques for interpreting the assessments captured 
-          by the questionnaire.
-      \end{itemize} 
-   \item \textbf{What did they learn?}
-      They conclude that the AIMQ methodology proved to be a practical information
-      quality tool to organizations.
-   \item \textbf{Relevance to our work}: the paper gave us valuable insight into 
-     how to assess information quality.
 \end{itemize}

### 2017-11-26 proposal/mprop.tex
Work further in combining DQ papers

@@
 
-\subsection{Data Quality Metrics}
+\subsection{Data Quality and Metrics}
 
@@
 
-Another important area of data quality is what methodologies can be applied by
-organizations in order to improve it. There are several studies that tried to
-propose such methodologies. A general overview of such techniques was presented 
-by \citet{pipino2002data} - they wanted to present ways of developing usable 
-data quality methods that organizations can implement in their own internal 
-processes. After reviewing various techniques of assessing data quality in
-information systems, they reached the conclusion that there is no universal 
-approach to assess data quality as it heavily depends on the context where it is
-analysed.
+Another important area of data quality is what methodologies or techniques can 
+be applied by organizations in order to improve DQ. There are several studies 
+that tried to propose such methodologies. A general overview of such techniques 
+was presented by \citet{pipino2002data} - they wanted to present ways of 
+developing usable  data quality methods that organizations can implement in 
+their own internal processes. After reviewing various techniques of assessing 
+data quality in information systems, they reached the conclusion that there is 
+no universal approach to assess data quality as it heavily depends on the 
+context where it is analysed.
 
@@
 
+However, there are other aspects that can be investigated when trying to measure
+data quality. For example, \citet{prybutok2008evaluating} tried to find if 
+leadership and information quality can lead to positive outcomes in an 
+e-government's data quality. They conducted a web survey to gather data and test 
+their hypotheses. Afterwards, they assessed the City of Denton's e-government 
+initiatives, including current plans and implementations. They learned that the 
+MBNQA leadership triad (leadership, strategic planning and customer/market focus) 
+had a positive impact on the IT quality triad (information, system and service 
+quality). Moreover, they found out that both leadership and IT quality improved 
+the benefits.
+
 \textbf{Knowing-Why about Data Processes and Data Quality}\cite{lee2003knowing}:
@@
   \item \textbf{What did they learn?}
-    The major finding of the study was that there is vast complexity of knowledge
-    at work in data production process. 
+    The major finding of the study was that there is vast complexity of knowledge at work in data production process. 
   \item \textbf{Relevance to our work}: an important research on how knowledge in
@@
 
-\textbf{Evaluating IT Quality in E-Government 
-        Environment}\cite{prybutok2008evaluating}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the paper is to identify if leadership and IT quality
-    can lead to positive outcomes in an e-government environment.
-  \item \textbf{What was the method?}
-    They conducted a web survey to gather data and test their hypotheses. They
-    assessed the City of Denton's e-government initiatives, including current 
-    plans and implementations.
-  \item \textbf{What did they learn?}
-    They learned that the MBNQA leadership triad (leadership, strategic
-    planning and customer/market focus) had a positive impact on the IT quality
-    triad (information, system and service quality). Moreover, they found out
-    that both leadership and IT quality improved the benefits.
-  \item \textbf{Relevance to our work}: even though the environment presented
-    in the paper was an e-government, it is useful to see how the organization 
-    around a project as well as IT quality can lead to a better functioning of the 
-    system. Thus, in our research, it can prove helpful in choosing the right 
-    open source project to gather and analyse the data from.
-\end{itemize}
-
 \textbf{Organizational Impact of Information Quality}
@@
       \begin{itemize}
-        \item what individual/combined influences system quality, service quality,
-          information quality have on organizational impact?
+        \item what individual/combined influences system quality, service 
+          quality, information quality have on organizational impact?
         \item what effect does system quality have on information quality?
@@
     can bring to software projects.
-\end{itemize}
-
-\textbf{Metrics for Measuring Data Quality}\cite{Heinrich2007MetricsDataQuality}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors of the paper aimed to answer the two main research questions:
-      \begin{itemize}
-        \item how can data quality be measured as metrics?
-        \item what can be done in regards to data quality and what economic
-          consequences would it bring?
-      \end{itemize}
-  \item \textbf{What was the method?}
-    They applied the metric for timeliness at a major German mobile services
-    provider. Due to some Data Quality issues the company was having, they had
-    lower mailing campaign success rates, but after applying the metrics, the 
-    company was able to establish a direct connection between the results of
-    measuring data quality and the success rates of campaigns.
-  \item \textbf{What did they learn?}
-    For some practical problems, the metrics that they applied in regards to
-    data quality proved to be quite appropriate. As they designed the metrics
-    to revolve around interpretability and cardinality, they could quantify
-    data quality, thus they could analyse the economical impact.
-  \item \textbf{Relevance to our work}: this paper could possibly help us in
-    measuring data quality. This is an important step in our research as we 
-    specifically need to measure quality in software tickets.
 \end{itemize}

### 2017-11-26 proposal/mprop.tex
Finish data quality section

@@
 
+\citet{nelson2005antecedents} proposed another technique for measuring data 
+quality in an organization by, firstly, setting 2 main research questions:
+  \begin{itemize}
+    \item identify a set of antecedents that both drive information and
+      system quality, as well as define the nature of the IT artifact;
+    \item explore data warehousing in general, especially analytical tools,
+      predefined reports and ad hoc queries.
+  \end{itemize}
+
+Then, the authors set up a model to define a tree-structured representation
+of system quality and data quality, as follows:
+  \begin{itemize}
+    \item data quality - defined by completeness, accuracy, format and currency;
+    \item system quality - defined by reliability, flexibility, integration,
+    response time and accessibility;
+    \item then, data and systems available are evaluated to infer 
+    data satisfaction and system satisfaction (coming from customers), which
+    in turn will compute the final satisfaction score of the product.
+  \end{itemize}
+
+After conducting a cross-functional survey to test the model, they learned that
+the features they selected were a good indicator of overall information/data and
+system quality. They also found that accuracy is the dominant determinant across
+all three data warehouse technologies, followed by completeness and format. Last
+but not least, another discovery was that more attention needs to be given to
+differences across varying technologies.
+
 Another important area of data quality is what methodologies or techniques can 
-be applied by organizations in order to improve DQ. There are several studies 
-that tried to propose such methodologies. A general overview of such techniques 
-was presented by \citet{pipino2002data} - they wanted to present ways of 
-developing usable  data quality methods that organizations can implement in 
-their own internal processes. After reviewing various techniques of assessing 
-data quality in information systems, they reached the conclusion that there is 
-no universal approach to assess data quality as it heavily depends on the 
-context where it is analysed.
+be applied by organizations in order to improve data quality. 
+There are several studies that tried to propose such methodologies. A general 
+overview of such techniques  was presented by \citet{pipino2002data} - they 
+wanted to present ways of developing usable  data quality methods that 
+organizations can implement in their own internal processes. After reviewing 
+various techniques of assessing data quality in information systems, they reached 
+the conclusion that there is no universal approach to assess data quality as it  
+heavily depends on the context where it is analysed.
 
@@
 
-However, there are other aspects that can be investigated when trying to measure
+However, there are other aspects that can be investigated when trying to improve
 data quality. For example, \citet{prybutok2008evaluating} tried to find if 
@@
 
-\textbf{Knowing-Why about Data Processes and Data Quality}\cite{lee2003knowing}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    They tried to investigate whether knowing-why affects work performance and
-    whether knowledge held by people in different roles affect the overall work
-    performance. 
-  \item \textbf{What was the method?}
-    They had 6 companies that served as data collection points. In all of them,
-    the research focused on the quality of their customer activity data, tuned
-    for the specific domain the company was activating in. They held 2 sessions
-    at each company: in the first session, the participants were presented with
-    an overview of the research and a questionnaire, while during the second 
-    session provided summary feedback on the questionnaire results and gave the
-    participants the chance to provide comments and explanations.
-  \item \textbf{What did they learn?}
-    The major finding of the study was that there is vast complexity of knowledge at work in data production process. 
-  \item \textbf{Relevance to our work}: an important research on how knowledge in
-    different roles in a company can lead to decreased data quality overall. It
-    will help us to analyse the software tickets we will mine better.
-\end{itemize}
-
-\textbf{Antecedents of Information and System Quality}
-\cite{nelson2005antecedents}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors had 2 main research objectives they wanted to aim for in this
-    paper:
-      \begin{itemize}
-        \item identify a set of antecedents that both drive information and
-          system quality, as well as define the nature of the IT artifact;
-        \item explore data warehousing in general, especially analytical tools,
-          predefined reports and ad hoc queries.
-        \end{itemize}
-  \item \textbf{What was the method?}
-    They conducted a cross-functional survey to test the model the authors 
-    proposed. They focused on user experience with a data warehouse. They sent
-    email invites to the Data Warehouse Institute which distributed it further
-    to organizations, among which 7 agreed to participate, yielding a total of
-    465 completed surveys. 
-  \item \textbf{What did they learn?}
-    They learned that their selected features were indeed a good indicator of
-    overall information and system quality. They also found out that accuracy is
-    the dominant determinant across all three data warehouse technologies, 
-    followed by completeness and format. Also, the results showed that more 
-    attention needs to be given to differences across varying technologies. 
-  \item \textbf{Relevance to our work}: this paper presents important findings
-    regarding information and system quality in an IT environment. We can use it
-    when analysing the quality of the tickets we will mine.
-\end{itemize}
-
-\textbf{Organizational Impact of Information Quality}
-\cite{gorla2010organizational}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors had two main research questions they wanted to address:
-      \begin{itemize}
-        \item what individual/combined influences system quality, service 
-          quality, information quality have on organizational impact?
-        \item what effect does system quality have on information quality?
-      \end{itemize}
-  \item \textbf{What was the method?}
-    They conducted a construct measurement for the IS quality dimensions and 
-    collected data through empirical testing.
-  \item \textbf{What did they learn?}
-    Firstly, they learned that service quality has the greatest impact 
-    of all three quality constructs. Moreover, they found out that there is a 
-    linkage between system and information quality, fact that previous research
-    did not reveal. Lastly, their results indicate that the above-mentioned 
-    quality dimensions have a significant positive influence on organizational
-    impact either directly or indirectly.
-  \item \textbf{Relevance to our work}: the paper can provide us insights into
-    how valuable information quality is and what an impact it can have.
-\end{itemize}
-
-\textbf{Impact of Poor Data Quality}\cite{redman1998impact}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main purpose of the article is to provide some insights into how
-    data quality can have a major economical impact on a company, as well
-    as to raise awareness about this issue.
-  \item \textbf{What was the method?}
-    The author has analysed various large enterprises and their available data 
-    to infer conclusions about the impact data quality has.
-  \item \textbf{What did they learn?}
-    There are three main issues across most enterprises:
-      \begin{itemize}
-        \item inaccurate data;
-        \item inconsistencies across databases;
-        \item unavailable data necessary for certain operations.
-      \end{itemize}
-    Moreover, the paper also presents a list of impacts poor data quality brings, among 
-    which we can find:
-      \begin{itemize}
-        \item lowered customer satisfaction;
-        \item increased cost;
-        \item lowered employee satisfaction;
-        \item it becomes more difficult to set strategy;
-        \item poorer decision making.
-      \end{itemize}
-  \item \textbf{Relevance to our work}: this is a key paper on data quality in
-    an enterprise setting and what impact it can have. It is valuable to our research 
-    because we can relate the findings with what negative impacts poor tickets
-    can bring to software projects.
-\end{itemize}
+Finally, after defining, measuring and improving data quality, we also need
+to be able to assess the impact poor DQ has on a company. In this area, there
+are several authors that investigated various implications of low indices
+of data quality.
+
+One such research is the one done by \citet{gorla2010organizational}. They wanted
+to examine what influences do system quality, service quality and data quality
+have on an organization, as well as what effect does system quality have on
+data quality. After conducting a construct measurement for the information
+systems quality dimensions \citep{swanson1997maintaining} and collecting data
+through empirical testing, they learned that service quality has the greatest
+impact of all three quality constructs. Moreover, they found out that there is 
+a linkage between system and information quality, fact that previous research
+did not reveal. Last but not least, their results indicate that the 
+above-mentioned quality dimensions have a significant positive influence on 
+organizational impact either directly or indirectly.
+
+On the other hand, \citet{redman1998impact} had different findings. Even though
+they did not analyze multiple types of quality, but only data quality, they 
+learned that there are three main issues across most enterprises: inaccurate
+data, inconsistencies across databases and unavailable data necessary for 
+certain operations. Furthermore, they presented a number of impacts that
+poor data quality has on enterprises: lowered customer satisfaction, increased
+cost, lowered employee satisfaction, it becomes more difficult to set strategy,
+as well as worse decision making.
+
+Another research, the one of \citet{lee2003knowing}, investigated another 
+aspect: whether knowing-why affects work performance and whether knowledge held
+by people in different roles affect the overall work performance. After
+conducting various surveys with 6 companies that served as data collection 
+points, they reached the conclusion that there is vast complexity of 
+knowledge at work in the data production process and if these gaps are not 
+bridged it might lead to decrased data quality.
 

### 2017-11-26 proposal/mprop.tex
Add structured papers in the issue quality section

@@
 
+Issue quality is the main topic of this literature review as it revolves around
+software tickets and what are the characteristics of a well-written and 
+informative bug report, how efficient are bug tracking systems, what defines
+an efficient bug triaging process etc.
+
+The first and most important sub-topic of issue quality, which is the one
+we will address in our own research as well, is the quality of bug reports.
+There are several authors that have tried to defined what makes for a good bug
+report and what components actually improve the overall quality.
+
+\citet{bettenburg2008makes} have tried, through their work, to analyze what 
+makes for a good bug report through qualitative analysis. They interviewed over
+450 developers and asked them what are the most important features for them in
+a bug report that help them solve the issue quicker. They reached the conclusion 
+that stack traces and steps to reproduce increased the quality of a bug report 
+the most, followed by well-written, grammar error free summaries and 
+descriptions. Last but not least, they also created a tool called CueZilla that 
+could with an accuracy rate between 31 and 48\% predict the quality of a bug 
+report.
+
+Strengthening the argument that readability matters considerably in bug report 
+quality is the work of \citet{hooimeijer2007modeling}. They ran an analysis over
+27000 bug reports from the Mozilla Firefox project, looking at self-reported 
+severity, readability, daily load, submitter reputation and changes over time. 
+After running the evaluation, they not only found out about the importance of
+readability in bug reports, but also that attachment and comment counts are 
+valuable for faster triaging and that patch count, for example, does not
+contribute in the same manner as the previous two.
+
 \textbf{Using fuzzy code search to link code fragments in discussions to source code}\cite{bettenburg2012using}:
@@
 
-\textbf{Modeling Bug Report Quality}\cite{hooimeijer2007modeling}
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors' goal is to present a model that would determine if a bug
-    report will be triaged in a given amount of time. Moreover, they are 
-    trying to propose features that could help composing a good quality
-    bug report.
-  \item \textbf{What was the method?}
-    They run an analysis on over 27000 bug reports from the Mozilla Firefox
-    project, selecting a couple of surface features that could be applied:
-      \begin{itemize}
-        \item self-reported severity;
-        \item readability;
-        \item daily load (i.e.\ total number of bug reports that need to be
-          dealt with at that point in time);
-        \item submitter reputation;
-        \item changes over time.
-      \end{itemize}
-    Afterwards, they ran 4 experiments (i.e.\ validate the assumptions, find
-    how much post-submission data is necessary, find the optimal resolved by
-    cutoff, evaluate the hypothetical benefit) and analyzed the results to
-    see if their model would be beneficial.
-  \item \textbf{What did they learn?}
-    They found out that linear model, even a simple one, can have 
-    better-than-chance predictive power. Also, they came to the conclusion that 
-    attachment and comment counts are really valuable for triaging the bug faster,
-    compared to, for example, patch count. Moreover, the readability of a bug is
-    important as it proved to influence the duration of the triaging process. 
-  \item \textbf{Relevance to our work}: the authors' goal was quite similar to ours
-    as they are trying to find out which features make for a good quality bug 
-    report. Moreover, they are also using programmatic analysis instead of
-    interviews with developers to produce the results, which is the same approach
-    we are aiming for in our research.
-\end{itemize}
-
 \textbf{Secret Life of Bugs}\cite{aranda2009secret}:
@@
   research paper.
-\end{itemize}
-
-\textbf{What makes a good bug report}\cite{bettenburg2008makes}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The main goal of the paper was to investigate the \textbf{quality of bug reports} from a developer's
-  point of view, based on the typical information found in such a report (e.g.\ stack traces, screenshots).
-\item \textbf{What was the method?}
-  The authors conducted a massive survey with over 450 respondents. The survey was online and it targeted
-  developers from Mozilla, Apache and Eclipse.
-\item \textbf{What did they learn?}
-  The main conclusion of this research paper was that well written bug reports will more likely get the 
-  attention of the developers. Thus, including steps to reproduce the bugs or stack traces proved to increase
-  the quality of the bug report. Also, an important achievement reached by the authors was the development of
-  a prototype tool called Cuezilla that could estimate, with an accuracy rate of 31\-48\%, the quality of a bug
-  report.
-\item \textbf{Relevance to our work}: it is relevant to our research in that it provides valuable insight into 
-  what makes for a good bug report based on actual professionals' opinions.
 \end{itemize}

### 2017-11-26 proposal/mprop.tex
Refactor and merge papers on information extraction from bug reports

@@
 
-\textbf{Using fuzzy code search to link code fragments in discussions to source code}\cite{bettenburg2012using}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the paper is to find an approach that improves on
-    previous methods to link source code fragments in discussions to source code.
-    These previous methods were mainly based on information retrieval or 
-    change log analysis. The main reason behind the authors' goal was
-    that a successful tool which could accomplish the goal would drastically
-    improve traceability in a project.
-  \item \textbf{What was the method?}
-    They created a tool based on fuzzy code search that could parse bug reports
-    discussions and, then, match the locations in the source code where those
-    code fragments belong to. The authors conducted the evaluation on the Eclipse
-    open source project after developing the 2 stages of the algorithm:
-      \begin{itemize}
-        \item they first use infoZilla, presented in \cite{bettenburg2008extracting},
-        to extract source code from documents belonging to a document archive;
-        \item then they perform a fuzzy textual search using a token-based clone
-        detection tool;
-        \item finally, they analyze all clone groups that associate clone pairs with
-        extracted code fragments to source code files; then, a traceability link is created,
-        which is basically a tuple containing a clone group ID and file paths corresponding
-        to the corresponding source code files.
-      \end{itemize}
-  \item \textbf{What did they learn?}
-    First of all, as many software projects have large code bases, creating such 
-    traceability links is no trivial task. Moreover, they noticed an increase of 20.01\%
-    in total traceability links between issue reports and source code compared to state of the art
-    technique (which is also most used one), change log analysis. Thus, there is room for
-    improvement in this area.
-  \item \textbf{Relevance to our work}:
-    If we'd decide to use this approach, we can find out even more information about
-    quality in issue reports/tickets as we can also analyze the source code files necessary
-    to fix that specific issue. This, combined with infoZilla, could prove valuable for our
-    mining and extraction processes.
-\end{itemize}
+Another research that agrees that stack traces are helpful in solving bug
+reports faster is the one performed by \citet{schroter2010stack}. They conducted
+the whole experiment on the Eclipse project. They first extracted the stack
+traces using the infoZilla tool(\citep{bettenburg2008extracting}), followed by
+linking the stack traces to changes in the source code (change logs) by mining
+the version repository of the Eclipse project. The results were that 
+around 60\% of the bugs that contained stack traces in their reports were fixed
+in one of the methods in the frame, with 40\% being fixed in exactly the first
+stack frame.
+
+Following on the conclusions of \citet{bettenburg2008makes} we have found out
+that the investigations undertaken by \citet{bettenburg2007quality} reveal 
+very similar results. They performed the same type of evaluation method (i.e. 
+interviews with developers) and confirmed that steps to reproduce and stack traces
+are the most important features in a bug report that help developers solve the
+issue quicker.
+
+However, in order to model the quality of a bug report, one needs to be able to
+successfully extract various types of information from such a report and, if 
+possible, link them to the source code of the project (i.e. source code fragments
+in bug report discussions should be linked to the corresponding sections in the 
+actual code) or other software artifacts. There are several researches that tried 
+to analyze such techniques and one of them is the work of 
+\citet{bettenburg2012using}. The authors created a tool that could parse a bug 
+report (using fuzzy code search) and extract source code that could then be
+matched with exact locations in the source code, in the end producing a 
+traceability link (i.e. tuple containing a clone group ID and file paths 
+corresponding to the source code files). Evaluation showed an increase of
+roughly 20\% in total traceability links between issue reports and source code 
+when compared to the current state-of-the-art technique, change log analysis.
+
+\citet{bettenburg2012using} also made use of a tool developed by 
+\citet{bettenburg2008extracting} called infoZilla. This application can
+parse bug reports and correctly extract patches, stack traces, source code and
+enumerations. When evaluating it on over 160.000 Eclipse bug reports, it proved to 
+have a very high rate of over 97\% accuracy.
 
@@
 
-\textbf{Information needs in bug reports: improving cooperation between developers and users}\cite{breu2010information}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-
-  \item \textbf{What was the method?}
-  \item \textbf{What did they learn?}
-  \item \textbf{Relevance to our work}:
-\end{itemize}
-
 \textbf{Where should we fix this bug?}\cite{kim2013should}:
@@
     phase of the recommendation model so that fix locations could be proposed).
-\end{itemize}
-
-\textbf{Do Stack Traces Help Developers Fix Bugs?}\cite{schroter2010stack}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the paper was to identify if including a stack trace in a 
-    bug report would help the developers fix the issue quicker. They divided their
-    investigations in order to follow 4 research questions:
-      \begin{itemize}
-        \item are bugs fixed in methods in stack traces;
-        \item how far down the stack to trace;
-        \item are two or more stack traces better than one;
-        \item do stack traces help speed up debugging.
-      \end{itemize}
-  \item \textbf{What was the method?}
-    They conducted their investigation on the Eclipse project which is developed in
-    Java. Then, they extracted stack traces from bug reports using the infoZilla tool.
-    Afterwards, they linked the stack traces (and thus the corresponding bug report)
-    to changes in the source code (change logs) by mining the version repository of the
-    Eclipse project.
-  \item \textbf{What did they learn?}
-    They found answers to all their research questions, and are as follows:
-      \begin{itemize}
-        \item around 60\% of the bugs that contained stack traces were fixed in 
-        one of the methods in the frames;
-        \item around 40\% were fixed in the first stack frame, around 80\% were fixed
-        within the top 6 frames, while close to 90\% of the bugs were fixed within top 10 stack frames;
-        \item having more than one stack trace usually helped more than only a single one;
-        \item bug reports containing stack traces usually have a shorter lifetime, thus
-        speeding up the debugging process.
-      \end{itemize}
-  \item \textbf{Relevance to our work}:
-    Stack traces are one of the types of information we are investigating in our research
-    and it is very useful to have such a study back up the statement that stack traces are
-    valuable for developers so that they speed up the issue fixing process.
-\end{itemize}
-
-\textbf{Extracting Structural Information from Bug Reports}\cite{bettenburg2008extracting}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors try to present a tool called infoZilla that can accurately
-    extract different types of information (e.g. stack traces, source code
-    fragments) from bug reports.
-  \item \textbf{What was the method?}
-    They selected a few categories of information that both infoZilla could
-    successfully extract from bug reports and that are of most interest to developers. Thus,
-    the categories selected are:
-      \begin{itemize}
-        \item patches;
-        \item stack traces;
-        \item source code;
-        \item enumerations.
-      \end{itemize}
-    Then, they ran the tool on tickets and evaluated the overall accuracy.
-  \item \textbf{What did they learn?}
-    After developing the tool to inspect such elements and retrieve them, 
-    they evaluated it on over 160000 Eclipse bug reports. For all categories, infoZilla
-    achieved over 97\% accuracy. 
-  \item \textbf{Relevance to our work}:
-    If we could manage to get this tool and use it in our own research, it would be
-    beneficial as we could extract efficiently different types of information we are
-    interested in testing ticket quality (e.g. stack traces).
 \end{itemize}
@@
 This research gives us various topics to concentrate on when analyzing the quality of tickets.
-\end{itemize}
-
-\textbf{Quality of Bug Reports in Eclipse}\cite{bettenburg2007quality}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The authors were looking to find the most important factors that determine the quality of a bug report. 
-  \item \textbf{What was the method?}
-  They conducted a survey with Eclipse developers on what they find most important and helpful in a bug report.
-Another goal was to develop a tool that could  automatically measure the quality in bug reports based on the best practices for writing such reports (Eclipse guidelines).
-  \item \textbf{What did they learn?}
-  They learned that well written bug reports will most likely get more attention from developers.
-Moreover, the most important factors which influence  ticket quality are stack traces and steps to reproduce.
-On the other hand, the most harmful information in bug reports are errors in steps to reproduce, incomplete information and wrong observed behavior.
-Regarding quzilla, they measured that the tool achieved an accuracy of 42\% which indicates that it could, on the long term, ensure some standard quality when reporting and creating new tickets.
-  \item \textbf{Relevance to our work}:
-  It is mostly the same topic as our research, but we want to use statistical analysis instead of interviews/questionnaires as well as investigate tickets from multiple open source repositories, not just one.
-However, the findings presented here could serve as clues on where to search for factors that influence ticket quality.
 \end{itemize}

### 2017-11-26 proposal/mprop.tex
Work on and merge papers

@@
 
+However, \citet{kim2013should} propose a rather different technique than the one
+exposed in \citet{bettenburg2012using}. The authors have employed a two-phase
+recommendation model that would locate the necessary fixes based on information
+in bug reports. Firstly, they did a feature extraction on the bug reports (e.g. 
+extract description, summary, metadata). Then, in order to successfully predict
+locations, this model was trained on collected bug reports and then, when given
+a new bug report, it would try to localize the files that need to be changed 
+automatically. Finally, the actual implementation was put into place, and that
+is the two phase recommendation model, composed of binary (filters out 
+uninformative bug reports before predicting the files to fix) and multiclass (
+previously filtered bug reports are used as training data and only after that
+new bug reports can be analyzed and files to be changed recommended). The 
+overall accuracy was above the one achieved by \citet{bettenburg2012using}, 
+being able to rank over 70\%, but only as long as it recommended \emph{any} 
+locations.
+
+Even though we have discussed about quality in bug reports and how it can be
+identified, we must also investigate if the platform where these bug reports 
+reside (i.e. bug trackers) are properly fitting the software environment. 
+The work of \citet{just2008towards} tries to find the answer to this question.
+The authors launched a survey to developers from Eclipse, Mozilla and Apache
+open source projects from which they received 175 comments back. Then, they
+applied a card sort in order to organize the comments into hierarchies to 
+deduce a higher level of abstraction and identify common patterns. In the end,
+they ranked the top suggestions as follows:
+  \begin{itemize}
+    \item provide tool support for users to collect and prepare information that 
+      developers need;
+    \item find volunteers to translate bug reports filed in foreign languages;
+    \item provide different user interfaces for each user level and give cues to 
+      inexperienced reporters on what to report and best practices;
+    \item reward reporters when they do a good job;
+    \item integrate reputation into user profiles to mark experienced reporters;
+    \item provide powerful and easy to use tools to search bug reports;
+    \item encourage users to submit additional details (provide tools for merging 
+      bugs).
+  \end{itemize}
+
+One other important aspect when analyzing the quality of a bug report is the
+time it takes to triage it. Triaging is the process of analyzing issues and 
+based on the information available, assign it to
+
 \textbf{Predicting the severity of a reported bug}\cite{lamkanfi2010predicting}:
@@
 
-\textbf{Where should we fix this bug?}\cite{kim2013should}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the paper was to aid developers in easily finding where to
-    apply the necessary changes in order to fix a bug. The authors wanted to bridge
-    this gap by creating a two-phase recommendation model that would locate the locations
-    where the fixes need to be applied based on the corresponding bug reports.
-  \item \textbf{What was the method?}
-    They divided the work into multiple stages:
-      \begin{itemize}
-        \item firstly, they did a feature extraction on the bug reports (e.g. extract
-        description, metadata, summary);
-        \item in order to predict the locations of the necessary fixes, the one-phase
-        recommendation model was put into place - this model would be trained on collected
-        bug reports and then, when given a new bug report, it would try to localize the 
-        files that need to be changed automatically;
-        \item last step was to implement the two-phase recommendation model which basically
-        has two classification phases - binary and multiclass:
-          \begin{itemize}
-            \item binary phase filters out uninformative bug reports before predicting the
-            files to fix;
-            \item multiclass phase where the previously filtered bug reports are used as
-            training data and only after that new bug reports can be analyzed and files to be
-            changed recommended.
-          \end{itemize}
-      \end{itemize}
-  \item \textbf{What did they learn?}
-    Evaluating the model yielded a 70\% accuracy in pointing to the correct files
-    to be fixed, as long as the algorithm actually recommended any locations. However, the authors
-    acknowledge that the approach needs extra work, especially in fine-grained defect 
-    localization, performance improvement and bug triaging.
-  \item \textbf{Relevance to our work}:
-    The research shows interesting points regarding time-to-fix-bug and bug report
-    contents, thus it can give us an insight into how ticket quality can affect that 
-    time to fix the bug (in the case of this paper it would mean to successfully pass the first
-    phase of the recommendation model so that fix locations could be proposed).
-\end{itemize}
-
 \textbf{Automatic Bug Report Assignment}\cite{anvik2006automating}:
@@
   The research presented can help us in understanding better if statistical expetiments are helpful in analyzing tickets, as well as give an insight into how important ticket quality and proper triaging are for any software projct.
-\end{itemize}
-
-\textbf{Effects of process maturity on quality, cycle time and effort in software product development}\cite{harter2000effects}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The research tries to investigate the relationship between process maturity, quality, cycle time and effort in software projects.
-The authors are mainly trying to prove/reject a couple of hypotheses: higher levels of process maturity lead to higher product quality in software projects, higher levels of process maturity are associated with increased cycle time in software products, higher product quality is associated with lower cycle time, higher levels of process maturity lead to increased development efforts in the project and higher product quality is associated with lower development effort.
-  \item \textbf{What was the method?}
-  In order to test their hypotheses, the authors examined data coming from 30 projects belonging to the systems integration division from a large IT company.
-The process improvement data was collected via external divisions and by government agencies to provide independent assessments of the firm’s software development processes.
-Then, they analyzed a couple of key variables and see how they interact: process maturity, product quality, cycle time, development effort, product size, domain/data/decision complexity and requirements ambiguity.
-  \item \textbf{What did they learn?}
-  They learned that the main features they inspected are additively separable and linear.
-Moreover, they found out that higher levels of process maturity are associated with significantly higher quality, but also with increased cycle times and development efforts.
-On the other hand, the reductions in cycle time and effort resulting from improved quality outweigh the marginal increases from achieving more process maturity.
-  \item \textbf{Relevance to our work}:
-  It can aid our research through better understanding of how various factors can influence the software development processes, thus giving more value to our own research (i.e.
-being able to automatically determine issue quality could improve better issue writing guidelines/better rules to be enforced, thus reduced triaging and development costs).
 \end{itemize}
@@
 
-\textbf{Towards the Next Generation of Bug Tracking Systems}\cite{just2008towards}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The authors wanted to determine what makes for good bug reports and, more specifically, how the reporting environment can be changed to best suit the developers’ needs (and everyone else involved in the software project).
-  \item \textbf{What was the method?}
-  They first launched a survey to developers from Eclipse, Mozilla and Apache open source projects from which they received 175 comments back.
-Then, they applied a card sort in order to organize the comments into hierarchies to deduce a higher level of abstraction and identify common patterns.
-  \item \textbf{What did they learn?}
-  They found 7 main topics of improvement for bug tracking systems: provide tool support for users to collect and prepare information that developers need, find volunteers to translate bug reports filed in foreign languages, provide different user interfaces for each user level and give cues to inexperienced reporters on what to report and best practices, reward reporters when they do a good job, integrate reputation into user profiles to mark experienced reporters, provide powerful and easy to use tools to search bug reports, encourage users to submit additional details (provide tools for merging bugs).
-  \item \textbf{Relevance to our work}:
-  This is an important paper to our research as it presents, from open source developers’ perspective, how bug reporting and bug tracking systems should behave.
-This research gives us various topics to concentrate on when analyzing the quality of tickets.
-\end{itemize}
-
 \textbf{Bug Report Assignee Recommendation using 
@@
     with valuable insight into how automatic triaging should be performed.
-\end{itemize}
-
-\textbf{Secret Life of Bugs}\cite{aranda2009secret}:
-\begin{itemize}
-\item What were the goals?
-  The paper tries to understand and analyze common bug fixing coordination
-  activities. Another goal of the paper was to analyze the reliability of
-  repositories in terms of software projects coordination and propose
-  different directions on how to implement proper tools.
-\item What was the method?
-  They executed a field study which was split into two parts:
-  \begin{itemize}
-  \item firstly, they did an exploratory case study of bug repos histories;
-  \item secondly, they conducted a survey with professionals (i.e.\ testers,
-    developers).
-  \end{itemize}
-  All data and interviews were conducted using Microsoft bug repositories and
-  employees.
-\item What did they learn?
-  They learned that there are multiple factors which influence the coordination
-  activities that revolve around bug fixing, such as organizational, social and
-  technical knowledge, thus one cannot infer any conclusions only by automatic
-  analysis of the bug repositories. Also, through surverying the professionals,
-  they reached the conclusion that there are 8 main goals which can be used for
-  better tools and practices:
-  \begin{itemize}
-  \item probing for ownership;
-  \item summit;
-  \item probing for expertise;
-  \item code review;
-  \item triaging;
-  \item rapid-fire emailing;
-  \item infrequent, direct email;
-  \item shotgun emails.
-  \end{itemize}
-\item Relevance to our work: this paper is one of the key papers for our
-  research paper.
 \end{itemize}
@@
 \subsection{Measuring Cost and Waste in Software Projects}
+
+\textbf{Secret Life of Bugs}\cite{aranda2009secret}:
+\begin{itemize}
+\item What were the goals?
+  The paper tries to understand and analyze common bug fixing coordination
+  activities. Another goal of the paper was to analyze the reliability of
+  repositories in terms of software projects coordination and propose
+  different directions on how to implement proper tools.
+\item What was the method?
+  They executed a field study which was split into two parts:
+  \begin{itemize}
+  \item firstly, they did an exploratory case study of bug repos histories;
+  \item secondly, they conducted a survey with professionals (i.e.\ testers,
+    developers).
+  \end{itemize}
+  All data and interviews were conducted using Microsoft bug repositories and
+  employees.
+\item What did they learn?
+  They learned that there are multiple factors which influence the coordination
+  activities that revolve around bug fixing, such as organizational, social and
+  technical knowledge, thus one cannot infer any conclusions only by automatic
+  analysis of the bug repositories. Also, through surverying the professionals,
+  they reached the conclusion that there are 8 main goals which can be used for
+  better tools and practices:
+  \begin{itemize}
+  \item probing for ownership;
+  \item summit;
+  \item probing for expertise;
+  \item code review;
+  \item triaging;
+  \item rapid-fire emailing;
+  \item infrequent, direct email;
+  \item shotgun emails.
+  \end{itemize}
+\item Relevance to our work: this paper is one of the key papers for our
+  research paper.
+\end{itemize}
+
+\textbf{Effects of process maturity on quality, cycle time and effort in software product development}\cite{harter2000effects}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+  The research tries to investigate the relationship between process maturity, quality, cycle time and effort in software projects.
+The authors are mainly trying to prove/reject a couple of hypotheses: higher levels of process maturity lead to higher product quality in software projects, higher levels of process maturity are associated with increased cycle time in software products, higher product quality is associated with lower cycle time, higher levels of process maturity lead to increased development efforts in the project and higher product quality is associated with lower development effort.
+  \item \textbf{What was the method?}
+  In order to test their hypotheses, the authors examined data coming from 30 projects belonging to the systems integration division from a large IT company.
+The process improvement data was collected via external divisions and by government agencies to provide independent assessments of the firm’s software development processes.
+Then, they analyzed a couple of key variables and see how they interact: process maturity, product quality, cycle time, development effort, product size, domain/data/decision complexity and requirements ambiguity.
+  \item \textbf{What did they learn?}
+  They learned that the main features they inspected are additively separable and linear.
+Moreover, they found out that higher levels of process maturity are associated with significantly higher quality, but also with increased cycle times and development efforts.
+On the other hand, the reductions in cycle time and effort resulting from improved quality outweigh the marginal increases from achieving more process maturity.
+  \item \textbf{Relevance to our work}:
+  It can aid our research through better understanding of how various factors can influence the software development processes, thus giving more value to our own research (i.e.
+being able to automatically determine issue quality could improve better issue writing guidelines/better rules to be enforced, thus reduced triaging and development costs).
+\end{itemize}
 

### 2017-11-26 proposal/mprop.tex
Refactor and merge further

@@
 
+A third technique for linking source code files from the textual description of a 
+bug report is the one proposed by \citet{zhou2012should}. The authors
+firstly performed a textual analysis, looking for similarities between the bug 
+report description and the source code files. Then, it analyzed previous bugs in 
+the repository to find the most similar ones, thus being able to find which files 
+ought to be changed. Lastly, it assigned scores to similar files, the ones with 
+bigger sizes obtaining higher scores as they are more likely to contain bugs. They 
+collected the necessary data from Bugzilla projects and then performed the 
+evaluation. The results of the evaluation phase were positive: the bug locator
+can locate a large percentage of bugs analyzing just a small set of source code
+files. Moreover, similar bugs can improve the localization accuracy only to a 
+certain extent, while the locator outperformed every other competitor on a 
+multitude of projects.
+
 Even though we have discussed about quality in bug reports and how it can be
@@
 time it takes to triage it. Triaging is the process of analyzing issues and 
-based on the information available, assign it to
+based on the information available, determine their severity and assign them to the
+most qualified available developer to fix them. If the ticket would be valuable
+and have an increased index of quality, the triaging process would be quicker and,
+thus, reduce the cost for the organization. There are several researches that 
+are concerned with this field and how gaps can be bridged.
+
+One such example is the work of \citet{anvik2006automating}. The authors tried
+to automate the process of bug report assignment by employing a machine learning 
+algorithm which, after receiving as input various types of information (e.g. 
+textual description of bug, bug component, OS, hardware, software version, 
+developer who owns the code, current workload of developers, list of developers 
+actively contributing), would recommend the best developers to work on the ticket. 
+After the tool was evaluated, it was found that it could actually be deployed
+in the software industry so that it could be used by organizations.
+
+Working on the previous tool, the same authors proposed a new solution to automatic
+bug report assignment through the work presented in \citet{anvik2011reducing}.
+They increased the precision and recall of the algorithm and then, in order to 
+test it, they implemented a proxy to the actual web service that's providing the
+issue repository. Eventually, they also found out that the impact of poor
+software project management, including bug triaging, on software projects can
+reach alarming levels.
+
+A similar research, but which looks at the free form of the ticket only, is
+the technique presented in \citet{anvik2006should}. The authors applied a 
+supervised machine learning algorithm on the repositories to learn which 
+developers were best suited for specific tasks, thus when a new bug report would 
+come in, a small set of people would be selected. In order to train the algorithm,
+they looked at Bugzilla repositories and selected the free text form of tickets, 
+trying to label similar ones based on textual similarities. Once the tickets were
+labeled and grouped for specific developers, the algorithm would then be able
+to present the triager the set of developers suitable to fix the bug. Even though
+this approach, compared to \citet{anvik2006automating} or 
+\citet{anvik2011reducing}, does not reach the same levels of accuracy, it is much
+simpler to implement and evaluate.
+
+However, a completely different approach is the one presented by 
+\citet{jeong2009improving} that looks at both bug report assignment as well as bug 
+tossing (i.e. re-assign tickets from one developer to another). They wanted, 
+through their tossing graph approach based on the Markov property, to both 
+discover developer networks and team structures, as well as help to better assign 
+developers to bug reports. They analyzed 145.000 bug reports from Eclipse and 
+300000 from Mozilla and then, using statistical analysis on the bug reports in 
+order to find evolution histories and changes throughout the lifetime of the 
+reports, they created the bug tossing graph. The research shows that it takes a 
+long time to assign and toss bugs and, additionally, they learned that their model 
+reduces tossing steps by up to 72\% and improved the automatic bug assignment by 
+up to 23\%.
+
+Another approach to bug report assignee recommendation is the one based on
+activity profiles, proposed by \citet{Naguib2013BugReportAssignee}. The authors 
+employed an algorithm using activity profiles (i.e. assign, review, resolve 
+activity of the developer) such that, after detecting the prior
+experience, developer's role, and involvement in the project, it could
+recommend who should fix a specific bug. The average accuracy was around
+88\%, much higher than other techniques, including the ones mentioned previously.
 
@@
 
-\textbf{Automatic Bug Report Assignment}\cite{anvik2006automating}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The author’s main goal was to determine a way through which bug triaging can be made 
-    easier using automatization approaches. 
-  \item \textbf{What was the method?}
-    The research’s output was an algorithm that can automatically assign bugs to developers based on various types of information fed.
-The author looked exclusively at ML approaches, examining 8 main types of information (textual description of bug, bug component, OS, hardware, software version, developer who owns the code, current workload of developers, list of devs actively contributing).
-Moreover, the author considers launching a Firefox extension to test the app even further through human evaluation as well.
-  \item \textbf{What did they learn?}
-  The research brings 3 main contributions: methodology for creating semi-automated bug triaging algorithms, a characterization of performance of different approaches, as well as an actual implementation for such a semi-automated big triaget.
-The author discovered that with further improvements and tweaking, we can reach an even further bug triager.
-  \item \textbf{Relevance to our work}:
-  Another project that we can use to learn about bug triaging; also we can contact maybe the author and receive either an executable or the source code for the application. 
-\end{itemize}
-
-\textbf{Reducing the effort of bug report triage}\cite{anvik2011reducing}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The authors had one main goal, and that was to find out if costs related to bug triaging can be reduced if ML algorithms were to be introduced.
-This hypothesis was backed by 2 research questions, which were if the approach would create recommenders that make accurate recommendations and if the humans can make use of the information provided by the approach.
-  \item \textbf{What was the method?}
-  They created a bug triager which can present a list of developers from which someone can choose who is the most suitable to fix that specific issue.
-Also, they improved a previous research the same authors worked on, thus increasing the precision and recall of the algorithm.
-They employed machine learning techniques to create the algorithm.
-Then, in order to test it, they implemented a proxy to the actual web service that’s providing the issue repository, thus visualizing results helped conduct the evaluation process.
-  \item \textbf{What did they learn?}
-  The authors learned that their approach could actually be used in software projects as its accuracy is reasonable.
-They also learned that the impact of poor software project management, including bug triaging, on software projects can be  quite high.
-  \item \textbf{Relevance to our work}:
-  The research presented can help us in understanding better if statistical expetiments are helpful in analyzing tickets, as well as give an insight into how important ticket quality and proper triaging are for any software projct.
-\end{itemize}
-
-\textbf{Where should the bugs be fixed?-more accurate information retrieval-based bug localization based on bug reports}\cite{zhou2012should}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The main goal of the paper was to implement a tool that, based on a bug report, could accurately select a number of files where the developer needs to make the necessary changes to fix the issue.
-They tried to answer 4 main research questions: how many bugs can be successfully lovated by BugLocator, does the revised VSM improve bug localization accuracy, does considering similar bugs improve localization accuracy, can bugLocator outperform other similar methods.
-  \item \textbf{What was the method?}
-  The tool firstly performed a textual analysis, looking for similarities between the bug report description and the source code files.
-Then, it analyzed previous bugs in the repository to find the most similar ones, thus being able to find which files ought to be changed.
-Lastly, it assigned scores to similar files, the ones with bigger sizes obtaining higher scores as they are more likely to contain bugs.
-They collected the necessary data from Bugzilla projects and then performed the evaluation.
-  \item \textbf{What did they learn?}
-  The buglocator can locate a large percentage of bugs analysing just a small set of source code files.
-Secondly, the revised VSM outperforms the standard VSM.
-Moreover, similar bugs can improve the localization accuracy only to a certain extent, while the locator outperformed every other competitor on a multitude of projects.
-  \item \textbf{Relevance to our work}:
-  We can try to use BugLocator and even include it in our research as it gives a direct correlation between bug reports and development effort (thus reduced costs).
-Thus, we can infer even more possible hypotheses regarding our issues’ quality.
-\end{itemize}
-
 \textbf{Analyzing and Relating Bug Report Data for Feature Tracking}\cite{fischer2003analyzing}:
@@
 
-\textbf{Duplicate Bug Reports Considered Harmful... Really?}\cite{bettenburg2008duplicate}:
+\textbf{Duplicate Bug Reports Considered Harmful... 
+Really}\cite{bettenburg2008duplicate}:
 \begin{itemize}
@@
 comments) instead of the actual description of the bug, we can apply the technique described here maybe to generate summaries and analyze them as well in the overall context of ticket quality (maybe together with some sentiment analysis).
-\end{itemize}
-
-\textbf{Improving Bug Triage with Bug Tossing Graphs}\cite{jeong2009improving}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The two main goals of the authors, through their bug tossing graph idea (based on the Markov property), were to discover developer networks and team structures, as well as help to better assign developers to bug reports.
-  \item \textbf{What was the method?}
-  They analyzed 145.000 bug reports from Eclipse and 300.000 from Mozilla.
-Then, using statistical analysis on the bug reports in order to find evolution histories and changes throughout the lifetime of the reports, they created the bug tossing graph.
-  \item \textbf{What did they learn?}
-  They learned that it takes a long time to assign and toss bugs.
-Additionally, they learned that their model reduces tossing steps by up to 72\% and improved the automatic bug assignment by up to 23\%.
-  \item \textbf{Relevance to our work}:
-  First paper on importance of tossing and its impact on the software development process.
-It might prove useful as we shall also inspect tossing and bug assignment in our own research in order to determine ticket quality (i.e.
-maybe tossing actually reduces the quality of the ticket?).
-\end{itemize}
-
-\textbf{Bug Report Assignee Recommendation using 
-Activity Profiles}\cite{Naguib2013BugReportAssignee}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the paper is to automatically detect who should be
-    the developers who are most suitable to solve a specific issue.
-  \item \textbf{What was the method?}
-    They employed an algorithm using activity profiles (i.e.\ assign, review,
-    resolve activity of the developer) such that, after detecting the prior
-    experience, developer's role, and involvement in the project, it could
-    recommend who should fix a specific bug. The average accuracy was around
-    88\%, much higher than the LDA-SVM technique.
-  \item \textbf{What did they learn?}
-    They found out that their approach was more accurate than previous work
-    done on assignee recommendation, but they think that it might even be
-    improved further by combining their technique with the classic LDA-SVM one.
-  \item \textbf{Relevance to our work}: this work complements the research
-    presented in Anvik et al. \cite{anvik2006should} and it will provide us
-    with valuable insight into how automatic triaging should be performed.
-\end{itemize}
-
-\textbf{Who should fix this bug?}\cite{anvik2006should}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors aimed to create a tool that could automatically assign the 
-    bug report to a specific developer based on his/her suitability for that
-    specific task.
-  \item \textbf{What was the method?}
-    They applied a supervised machine learning algorithm on the 
-    repositories to learn which developers were best suited for specific tasks,
-    thus when a new bug report would come in, a small set of people 
-    would be selected. In order to train the algorithm, they looked at
-    Bugzilla repositories and selected the free text form of tickets, trying
-    to label similar ones based on textual similarities. Once the tickets were 
-    labeled and grouped for specific developers, the algorithm would then be
-    able to present the triager the set of developers suitable to fix the bug.
-  \item \textbf{What did they learn?}
-    The most important lesson learned was that collecting data from bug reports 
-    and CVS logs was quite challenging. One of the major reasons why they 
-    found this aspect hard was that not all CVS comments referenced the 
-    specific bug report id.
-  \item \textbf{Relevance to our work}
-    The paper taught us that bug triaging is hard and that there is almost no 
-    automated tool that can choose the perfect developers to work on the task.
-    Moreover, the method applied by the authors could prove useful as a 
-    learning aid when working with the open source repositories 
-    chosen as data sets.
 \end{itemize}

### 2017-11-27 proposal/mprop.tex
Continue work on lit review

@@
 aggregated.
+
+The work of \citet{kitchenham1996software} looks specifically at defining
+quality in a software projects, as well as finding who are the people in charge of 
+this and how should they approach achieving it. They tried to define quality 
+in software projects and analyze techniques that measure such metrics by looking
+at other models proposed in different other researches, such as McCall's quality
+model or ISO 9126. However, they learned that quality is very hard to define and
+there are various factors which need to be taken into consideration, such as the
+business model of the company, the type of the software project (e.g. safety 
+critical, financial sector) or the actors who are involved and how they coordinate
+the software activities.
+
+One other piece of data that is probably the most crucial in a software project
+is code, and \citet{stamelos2002code} tried to discuss and examine the quality
+of the source code delivered by open source projects. They used a set of tools
+that could automatically inspect various aspects of source code, looking at
+the 6th release of the OpenSUSE project and its components defined by C
+functions. The research's results show that Linux applications have high quality 
+code standards that one might expect in an open source repository, but 
+the quality is lower than the one implied by the standard. More than half
+of the components were in a high state of quality, but on the other hand, 
+most lower quality components cannot be improved only by applying some
+corrective actions. Thus, even though not all the source code was in 
+an industrial standards shape, there is definitely room for further 
+improvement and open source repositories proved to be of good quality.
 
@@
 
+One other type of information that could be extracted and used for valuable
+purposes is the summary of a bug report, as shown in the work of 
+\citet{rastkar2010summarizing}. The authors wanted to determine if bug reports
+could be summarized effectively and automatically so that developers would
+need only to analyze summaries instead of full tickets. Firstly, they asked
+university students to volunteer to annotate the bug reports collected from
+various open sources projects (i.e. Eclipse, Mozilla, Gnome, KDE) by writing
+a summary of maximum 250 words in their own sentences. These human-produced 
+annotations were then used by algorithms to learn how to effectively summarize a 
+bug report.  Afterwards, the authors asked the end users of these bug reports, the 
+software developers, to rate the summaries against the original bug reports.
+They eventually learned that existing conversation-based extractive summary
+generators trained on bug reports produce the best results.
+
 A third technique for linking source code files from the textual description of a 
@@
 
-\textbf{Summarizing Software Artifacts: A Case Study of Bug Reports}\cite{rastkar2010summarizing}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The main goal of the research was to determine if software artifacts could be summarized effectively and automatically so that developers would need only to analyze summaries instead of full software artifacts (i.e.
-in our case, bug reports).
-  \item \textbf{What was the method?}
-  Firstly, they collected data to analyze from 4 different open source projects (Eclipse, Mozilla, Gnome, KDE).
-Then, they asked the volunteers (i.e.
-university students) to annotate the bug reports - write a summary of maximum 250 words in their own sentences.
-These human-produced annotations were then used by algorithms to learn how to effectively summarize a bug report.
-Afterwards, the authors asked the end users of these bug reports, the software developers, to rate the summaries against the original bug reports.
-  \item \textbf{What did they learn?}
-  They learned that existing conversation-based extractive summary generators trained on bug reports produce the best results. 
-  \item \textbf{Relevance to our work}:
-  As the paper revolves around conversations that are attached to a bug (i.e.
-comments) instead of the actual description of the bug, we can apply the technique described here maybe to generate summaries and analyze them as well in the overall context of ticket quality (maybe together with some sentiment analysis).
-\end{itemize}
-
-\textbf{Software Quality \- The Elusive Target}\cite{kitchenham1996software}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the paper is to determine what makes for a good quality
-    software project, as well as who are the people in charge of this aspect
-    and how should they approach achieving it.
-  \item \textbf{What was the method?}
-    They tried to define quality in software projects and analyze techniques that 
-    measure such quality by looking at other models proposed in different other  
-    papers (e.g.\ McCall's quality model, ISO 9126).
-  \item \textbf{What did they learn?}
-    They learned that quality is very hard to define and there are various 
-    factors which need to be taken into consideration, such as the business
-    model of the company, the type of the software project (e.g.\ safety
-    critical, financial) or the actors which are involved and how they
-    coordinate the software activities.
-  \item \textbf{Relevance to our work}: this paper is a key paper on software  
-    quality and it can prove beneficial in our research by
-    giving valuable insights into how software quality can be modeled, thus
-    helping us in selecting good quality open source repositories to work with 
-    (i.e.\ ticket selection and analysis).
-\end{itemize}
-
-\textbf{Code Quality Analysis in OSS}\cite{stamelos2002code}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The article tries to discuss and examine the quality of the source code
-    delivered by open source projects.
-  \item \textbf{What was the method?}
-    They used a set of tools that could automatically inspect various aspects
-    of source code. The authors analyzed the 6th release of the OpenSUSE project
-    and examined only the components, which are defined by C functions in the
-    programs.
-  \item \textbf{What did they learn?}
-    The research's results show that Linux applications have high quality 
-    code standards that one might expect in an open source repository, but 
-    the quality is lower than the one implied by the standard. More than half
-    of the components were in a high state of quality, but on the other hand, 
-    most lower quality components cannot be improved only by applying some
-    corrective actions. Thus, even though not all the source code was in 
-    an industrial standards shape, there is definitely room for further 
-    improvement and open source repositories proved to be of good quality.
-  \item \textbf{Relevance to our work}: this work completes the previous paper
-    on software quality in general by looking specifically at quality in
-    open source projects, which will be our main points for data collection.
-\end{itemize}
-
-\textbf{Analysis of Software Cost Estimation}\cite{grimstad2006framework}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors are trying to show that poor estimation analysis techniques 
-    in software projects will lead to wrong conclusions regarding cost 
-    estimation accuracy. Moreover, they also propose a framework for 
-    better analysis of software cost estimation error.
-  \item \textbf{What was the method?}
-    They approached a real-world company where they conducted analysis on
-    their cost estimation techniques.
-  \item \textbf{What did they learn?}
-    They learned that regular, straight-forward types of cost estimation analysis
-    techniques error lead them to wrong conclusions. 
-  \item \textbf{Relevance to our work}: it showed us that we need to be careful
-    when selecting techniques for cost estimation in our own research.
-\end{itemize}
-
 \subsection{Measuring Cost and Waste in Software Projects}
@@
   research paper.
+\end{itemize}
+
+\textbf{Analysis of Software Cost Estimation}\cite{grimstad2006framework}:
+\begin{itemize}
+  \item \textbf{What were the goals?}
+    The authors are trying to show that poor estimation analysis techniques 
+    in software projects will lead to wrong conclusions regarding cost 
+    estimation accuracy. Moreover, they also propose a framework for 
+    better analysis of software cost estimation error.
+  \item \textbf{What was the method?}
+    They approached a real-world company where they conducted analysis on
+    their cost estimation techniques.
+  \item \textbf{What did they learn?}
+    They learned that regular, straight-forward types of cost estimation analysis
+    techniques error lead them to wrong conclusions. 
+  \item \textbf{Relevance to our work}: it showed us that we need to be careful
+    when selecting techniques for cost estimation in our own research.
 \end{itemize}

### 2017-11-27 proposal/mprop.tex
Add paper to issue quality section of literature review

@@
 
-\textbf{Predicting the severity of a reported bug}\cite{lamkanfi2010predicting}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the research was to determine if, using textual analysis, one can
-    predict the severity of a bug. This main research question was further divided into
-    4 RQs:
-      \begin{itemize}
-        \item which terms in the textual description could serve as good indicators for
-        the bug severity;
-        \item what types of textual fields (e.g. summary, description) serve indicate the
-        bug severity best;
-        \item how many sample does one need to train an accurate predictor;
-        \item is it better to have a specialized predictor for each component or combine
-        bug reports over multiple components.
-      \end{itemize}
-  \item \textbf{What was the method?}
-    The authors conducted their research on the Mozilla, Eclipse and GNOME project. The 
-    approach can be divided into 5 steps:
+However, bug report assignment is not the only part of bug triaging that needs
+investigation. \citet{lamkanfi2010predicting} show a method through which one
+can predict the severity of a reported bug (i.e. assign story points to the 
+ticket) automatically. The authors conducted their research on the Mozilla,
+Eclipse and GNOME projects and divided their method into 5 steps:
   \begin{itemize}
     \item extract and organize bug reports;
-        \item preprocess bug reports (i.e. tokenization, stop word removal and stemming);
-        \item train the classifier on multiple datasets of bug reports (they used a ratio of
-        70\% - training, 30\% - evaluation);
+    \item pre-process bug reports - tokenization, stop word removal and stemming;
+    \item train the classifier on multiple datasets of bug reports - 70\% 
+      training and 30\% evaluation;
     \item apply the trained classifier on the evaluation set.
   \end{itemize}
-        Then, they used precision and recall to evaluate their results.
-  \item \textbf{What did they learn?}
-    The authors managed to answer all their 4 research questions:
+The conclusions they drew from running the evaluation process were rather 
+interesting:
   \begin{itemize}
-        \item terms such as deadlock, hand, crash, memory or segfault usually indicate a severe bug;
-        however, there are other terms that can indicate the opposite (i.e. non-severe bugs),
-        such as typo;
-        \item they switched from analysing only the one-line summary to analysing the whole
-        textual description as it contains more detailed information, thus the model can be
-        trained better; however, when they analysed the results and noticed that they had a large
-        number of false positives, which made them switch back to one-line summaries;
-        \item the classifier needs a large number of datasets in order to predict better on the
-        evaluation set;
-        \item it mainly depends on the type of project and how it is structured; thus, in Mozilla
-        and GNOME, which share problem-specific characteristics over different components, using a 
-        predictor across components sees improvements; however, the dataset needs to be even larger,
-        otherwise the performance starts to decrease.
-      \end{itemize}
-  \item \textbf{Relevance to our work}:
-    The authors' findings could help us in better understanding textual description analysis and how
-    it can indicate various aspects about a ticket, such as severity. Thus, we can apply the technique
-    described in order to differentiate between severe and non-severe bug reports so that we can 
-    focus on a specific category in our own research, if we want that.
+    \item terms such as deadlock, hand, crash, memory or segfault usually indicate
+      a severe bug; however, there are other terms that can indicate the opposite,
+      such as typos;
+    \item when analyzing the textual description they found that using simple
+      one line summaries resulted in less false positives and increased precision
+      levels;
+    \item the classifier needs a large dataset in order to predict correctly;
+    \item depending on how well a software project is componentized, one can 
+      use a predictor per component rather than an universal one.
   \end{itemize}

### 2017-11-27 proposal/mprop.tex
Finish issue quality section of the lit review

@@
 
+Other interesting findings regarding the quality of a software project's tickets
+are the ones elicited in \citet{bettenburg2008duplicate}. The authors examined
+whether duplicate bug reports are actually harmful to a project or they add 
+quality. They collected big amount of data from the Eclipse project and ran
+various kind of textual and statistical analysis on the data to find answers.
+They reached the conclusion that bug duplicates contain information that is not
+present in the master reports. This additional data can be helpful for developers
+and it can also aid automated triaging techniques.
+
 However, in order to model the quality of a bug report, one needs to be able to
@@
 
-Even though we have discussed about quality in bug reports and how it can be
-identified, we must also investigate if the platform where these bug reports 
+Having discussed automated linkage between source code files and bug reports, 
+\citet{fischer2003analyzing} presents a way to track certain features from the
+data residing in tickets. The authors employed a method to track features by 
+analyzing and relating bug report data filtered from a release history database.
+Features are then instrumented and tracked, relationships of modification and 
+problem reports to these features are established, and tracked features are
+visualized to illustrate their otherwise hidden dependencies. They managed to 
+successfully visualize the tracked features and illustrate their non apparent
+dependencies which can prove very useful in projects with a large number of
+components.
+
+Even though we have discussed about quality in bug reports, how it can be 
+identified and what state-of-the-art techniques can be used to extract and 
+link various components from tickets, we must also investigate if the platform 
+where these bug reports 
 reside (i.e. bug trackers) are properly fitting the software environment. 
@@
       use a predictor per component rather than an universal one.
-  \end{itemize}
-
-\textbf{Analyzing and Relating Bug Report Data for Feature Tracking}\cite{fischer2003analyzing}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The main goal of the paper was to analyze the proximity of software features based on modification and problem report data.
-  \item \textbf{What was the method?}
-  They employed a method to track features by analyzing and relating bug report data filtered from a release history database.
-Features are instrumented and tracked, relationships of modification and problem reports to these features are established, and tracked features are visualized to illustrate their otherwise hidden dependencies.
-  \item \textbf{What did they learn?}
-  The authors’ approach suggest first to instrument and track features, then establish the relationships of modification and problem reports to these features and lastly visualize the tracked features for illustrating their non apparent dependencies.
-  \item \textbf{Relevance to our work}:
-  This paper can give us insight into how bug reports can influence feature implementation throughout the lifetime of the ticket. 
-\end{itemize}
-
-\textbf{Duplicate Bug Reports Considered Harmful... 
-Really}\cite{bettenburg2008duplicate}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The authors wanted to test two main hypotheses, and these were: duplicate bug reports provide developers with information that was not present in the original report and the information in bug duplicates can improve automated triaging techniques.
-  \item \textbf{What was the method?}
-  They collected big amounts of data from the Eclipse open source project in XML form.
-Then, they ran different kinds of textual and statistical analysis on the data to find answers to their research questions.
-  \item \textbf{What did they learn?}
-  They reached the conclusion that bug duplicates contain information that is not present in the master reports.
-This additional data can be helpful for developers and it can also aid automated triaging techniques (e.g.
-decide who to assign a bug to).
-  \item \textbf{Relevance to our work}:
-  The findings presented in this paper could potentially make us consider duplicate tickets in a different way (i.e.
-do not treat it as disposable but analyze it and see if it maybe adds more information to the original/master report).
   \end{itemize}

### 2017-11-27 proposal/mprop.tex
Add sections in proposed approach and briefly outline what will be done
Continue work on software waste section in the literature review

@@
 
+Having talked about data and ticket quality and its characteristics, we have 
+another issue that inevitably arises in every software project: software waste. 
+There are different researches that try to define what waste in software 
+development is as well as its main types. One such paper is the one of 
+\citet{sedano2017software}. The authors conducted a participant-observation 
+study over a long period of time at Pivotal, a consultancy software development
+company. They also interviewed multiple engineering and balanced theoretical 
+sampling with analysis to elicit the following main types of waste in software
+project:
+  \begin{itemize}
+    \item building the wrong feature or product;
+    \item mismanaging backlog;
+    \item extraneous cognitive load;
+    \item rework;
+    \item ineffective communication;
+    \item waiting/multitasking;
+    \item solutions too complex;
+    \item psychological distress.
+    \item \textbf{Relevance to our work}: this paper complements the previous 
+      one on waste identification\cite{Korkala2014WasteIdentification}.
+  \end{itemize}
+
+Even though \citet{sedano2017software} look at waste generally in software 
+development, \citet{ikonen2010exploring} try to specifically investigate waste
+in kanban-based projects. They controlled a case study research at a company 
+called Software factory using semi-structured interviews. The authors reached
+two main conclusions:
+  \begin{itemize}
+    \item they couldn't explain the success of the project even though waste was 
+      found;
+    \item they identified 7 main types of waste throughout various development
+      stages: partially done work, extra processes, extra features, task 
+      switching, waiting, motion and defects.
+  \end{itemize}
+Apart from building the wrong feature/product, the 2 works differ in what types
+of waste they identified.
+
+However, defining waste and its main types is not enough - one needs also
+ways to identify such waste. \citet{Korkala2014WasteIdentification} propose a
+technique to identify communication waste in agile software projects 
+environments. The authors collaborated with a medium-sized American software 
+company and conducted a series of observations, informal discussions, documents 
+provided by the organization, as well as semi-structured interviews. Moreover,
+the data collection for waste identification was split into 2 parts:
+  \begin{itemize}
+    \item \textbf{pre-development}: occurred before the actual implementation
+      begun (e.g.\ backlog creation);
+    \item \textbf{development}: happened throughout the implementation
+      process (e.g.\ throughout sprints, retrospectives, sprint reviews,
+      communication media).
+  \end{itemize}
+Eventually they reached two main conclusions:
+  \begin{itemize}
+    \item this proposed approach was efficient and the authors recommend it to
+      companies if they'd like to conduct such processes internally;
+    \item the research elicits 5 main categories for communication waste: lack
+      of involvement, lack of shared understanding, outdated information, 
+      restricted access to information, scattered information.
+  \end{itemize}
+
 \textbf{Secret Life of Bugs}\cite{aranda2009secret}:
@@
 
-\textbf{Waste Identification}\cite{Korkala2014WasteIdentification}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The paper had two main goals: 
-    \begin{itemize}
-      \item a means to identify communication waste in agile software projects 
-        environments;
-      \item types of communication waste in agile projects.
-    \end{itemize}
-  \item \textbf{What was the method?}
-    The authors collaborated with a medium-sized American software company
-    and conducted a series of observations, informal discussions, documents 
-    provided by the organization, as well as semi-structured interviews. Moreover,
-    the data collection for waste identification was split into 2 parts:
-      \begin{itemize}
-        \item \textbf{pre-development}: occured before the actual implementation
-          begun (e.g.\ backlog creation);
-        \item \textbf{development}: happened throughout the implementation
-          process (e.g.\ throughout sprints, retrospectives, sprint reviews,
-          communication media).
-      \end{itemize}
-  \item \textbf{What did they learn?}
-    They realized the communication waste can be divided into 5 main categories:
-      \begin{itemize}
-        \item lack of involvement;
-        \item lack of shared understanding;
-        \item outdated information;
-        \item restricted access to information;
-        \item scattered information.
-      \end{itemize}
-    Also, they learned that their way of identifying these types of waste was
-    quite efficient and they even recommend it to companies if they'd like
-    to conduct such processes internally.
-  \item \textbf{Relevance to our work}: the waste identification process can
-    be applied to our work so that we can identify possible causes to poor 
-    quality tickets.
-\end{itemize}
-
-\textbf{Software Development Waste}\cite{sedano2017software}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the paper was to identify main types of waste in software
-    development projects.
-  \item \textbf{What was the method?}
-    They conducted a participant-observation study over a long period of time
-    at Pivotal, a consultancy software development company. They also interviewed
-    multiple engineers and balanced theoretical sampling with analysis to achieve
-    the conclusions.
-  \item \textbf{What did they learn?}
-    They found out there are nine main types of waste in software projects:
-    \begin{itemize}
-      \item building the wrong feature or product;
-      \item mismanaging backlog;
-      \item extraneous cognitive load;
-      \item rework;
-      \item ineffective communication;
-      \item waiting/multitasking;
-      \item solutions too complex;
-      \item psychological distress.
-      \item \textbf{Relevance to our work}: this paper complements the previous 
-    one on waste identification\cite{Korkala2014WasteIdentification}.
-    \end{itemize}
-\end{itemize}
-
-\textbf{Waste in Kanban Projects}\cite{ikonen2010exploring}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors are trying to find the main sources of waste in Kanban software
-    development projects and categorize/rank them based on severity.
-  \item \textbf{What was the method?}
-    A controlled case study research was employed in a company called Software
-    Factory. They conducted semi-structured interviews with 5 of the team
-    members both in the beginning in order to collect data as well as at the end 
-    of the whole process to categorize the seven types of waste found. Moreover,
-    they also measured the overall success of the project based on Shenar's
-    techniques (first-second-third-fourth; project efficiency-imapct on the
-    customer-business success-preparing for the future).
-  \item \textbf{What did they learn?}
-    They reached two main findings:
-      \begin{itemize}
-        \item they found 7 types of waste throughout the project at various
-          development stages:
-            \begin{itemize}
-              \item partially done work;
-              \item extra processes;
-              \item extra features;
-              \item task switching;
-              \item waiting;
-              \item motion;
-              \item defects.
-            \end{itemize}
-        \item they reached the conclusion that they couldn't explain the success
-          of the project even though waste was found.
-      \end{itemize}
-  \item \textbf{Relevance to our work}: this work completes the findings 
-    from the previous work presented as most of the projects we will work with
-    will be Agile, thus Kanban-based in terms of issue management.
-\end{itemize}
-
 \subsection{Sentiment Analysis}
@@
 
+\textbf{Research Questions}:
+\begin{itemize}
+  \item what makes for a quality software ticket that could help developers
+    fix the bug/implement the feature faster?
+  \item what can be changed in software ticket structure that could ease writing
+    such quality software tickets (e.g. add specific fields to the ticket in
+    Jira, add instructions as comments on how reporters should write such a 
+    ticket)?
+  \end{itemize}
+
+\textbf{Experimental design}: conduct a statistical analysis over popular 
+open source projects such as Mozilla or Apache and extract tickets via 
+some API (maybe REST based). Then, define what makes for 2 similar tickets
+(maybe look at story points assigned by experienced triagers; probably we also
+need to use only severe/critical ones as they will probably be fixed first
+and there will not be any delay, such as waiting for the main developer to come
+back from vacation) and then see how much time it took both to be completed
+so that we can infer what differences did those 2 tickets have (and see if, for
+example, stack traces influenced the duration of the ticket).
+
+\textbf{Independent Variables}: components of tickets - stack traces, steps
+to reproduce, grammar error free description and summary, succinct/detailed 
+summary, complex/light discussion in comments
+
+\textbf{Dependent Variable}: duration of the ticket between OPEN status and
+CLOSED status.
+
 Research questions, outline experimental design, independent variables, dependent variables.

### 2017-11-30 proposal/mprop.tex
Change proposal lightly
Add 2 papers on software waste to proposal

@@
 
-\textbf{Secret Life of Bugs}\cite{aranda2009secret}:
+Another work that is trying to analyze the waste around software coordination activities
+is the one of \citet{aranda2009secret}. They are trying to understand common bug fixing
+coordination activities in terms of software projects coordination and propose different
+directions on how to implement proper tools. Firstly, the conducted a field study which was
+split into two parts:
   \begin{itemize}
-\item What were the goals?
-  The paper tries to understand and analyze common bug fixing coordination
-  activities. Another goal of the paper was to analyze the reliability of
-  repositories in terms of software projects coordination and propose
-  different directions on how to implement proper tools.
-\item What was the method?
-  They executed a field study which was split into two parts:
-  \begin{itemize}
-  \item firstly, they did an exploratory case study of bug repos histories;
-  \item secondly, they conducted a survey with professionals (i.e.\ testers,
-    developers).
+    \item led an exploratory case study of bug repositories histories;
+    \item then, they conducted a survey with professionals (e.g. testers, developers).
   \end{itemize}
-  All data and interviews were conducted using Microsoft bug repositories and
-  employees.
-\item What did they learn?
-  They learned that there are multiple factors which influence the coordination
-  activities that revolve around bug fixing, such as organizational, social and
-  technical knowledge, thus one cannot infer any conclusions only by automatic
-  analysis of the bug repositories. Also, through surverying the professionals,
-  they reached the conclusion that there are 8 main goals which can be used for
-  better tools and practices:
-  \begin{itemize}
-  \item probing for ownership;
-  \item summit;
-  \item probing for expertise;
-  \item code review;
-  \item triaging;
-  \item rapid-fire emailing;
-  \item infrequent, direct email;
-  \item shotgun emails.
-  \end{itemize}
-\item Relevance to our work: this paper is one of the key papers for our
-  research paper.
-\end{itemize}
+After they finished the 2 phases, they learned that there are multiple factors which
+influence the coordination activities that revolve around bug fixing, such as organizational,
+social and technical knowledge, thus one cannot infer any conclusions only by automatic analysis 
+of the bug repositories. Also, through surveying the professionals, they reached the conclusion
+that there are \emph{eight main goals} which can be used for better tools and practices: summit, 
+probing for ownership, probing for expertise, code review, triaging, rapid-fire emailing, 
+shotgun emails and infrequent/direct email.
 
-\textbf{Analysis of Software Cost Estimation}\cite{grimstad2006framework}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The authors are trying to show that poor estimation analysis techniques 
-    in software projects will lead to wrong conclusions regarding cost 
-    estimation accuracy. Moreover, they also propose a framework for 
-    better analysis of software cost estimation error.
-  \item \textbf{What was the method?}
-    They approached a real-world company where they conducted analysis on
-    their cost estimation techniques.
-  \item \textbf{What did they learn?}
-    They learned that regular, straight-forward types of cost estimation analysis
-    techniques error lead them to wrong conclusions. 
-  \item \textbf{Relevance to our work}: it showed us that we need to be careful
-    when selecting techniques for cost estimation in our own research.
-\end{itemize}
+However, having discussed about software and communication waste, what work has been done
+around another major software activity, software cost estimation? The paper from 
+\citet{grimstad2006framework} tried to show that poor estimation analysis techniques
+in software projects will lead to wrong conclusions regarding cost estimation accuracy.
+Moreover, they also propose a framework for better analysis of software cost estimation
+error. They approached a real-world company where they conducted analysis on their cost
+estimation techniques. Eventually, they learned that regular, straight-forward types
+of cost estimation analysis techniques errors lead to wrong conclusions, thus increasing
+the risk of poor coordination activities.
 

### 2017-12-05 proposal/mprop.tex
Add paper on software waste

@@
 However, having discussed about software and communication waste, what work has been done
-around another major software activity, software cost estimation? The paper from 
+around another major software activity, i.e. software cost estimation? The paper from 
 \citet{grimstad2006framework} tried to show that poor estimation analysis techniques
@@
 
+But what happens when a project gains maturity? A work that investigates the effects of process
+maturity on quality, cycle time and effort is the one undergone by \citet{harter2000effects}. The
+research tries to prove or reject several hypotheses, such as higher levels of process maturity lead 
+to higher product quality, higher levels of process maturity are associated with increased cycle time,
+higher product quality is associated with lower cycle time, higher levels of process maturity lead 
+to increased development efforts in the project and higher product quality is associated with lower
+development effort. The authors examined data coming from 30 projects belonging to the systems 
+integration division from a large IT company and analyzed a couple of key variables and see how
+they interact (i.e. process maturity, product quality, cycle time, development effort, product
+size, domain/data/decision complexity and requirements ambiguity). They learned that the main
+features they inspected are additively separable and linear. Moreover, they found out that 
+higher levels of process maturity are associated with significantly higher quality, but also
+with increased cycle times and development efforts. On the other hand, the reductions in cycle
+time and effort resulting from improved quality outweigh the marginal increases from achieving
+more process maturity.
+
 \textbf{Effects of process maturity on quality, cycle time and effort in software product development}\cite{harter2000effects}:
@@
   \item \textbf{What were the goals?}
-  The research tries to investigate the relationship between process maturity, quality, cycle time and effort in software projects.
-The authors are mainly trying to prove/reject a couple of hypotheses: higher levels of process maturity lead to higher product quality in software projects, higher levels of process maturity are associated with increased cycle time in software products, higher product quality is associated with lower cycle time, higher levels of process maturity lead to increased development efforts in the project and higher product quality is associated with lower development effort.
+  The research tries to investigate the relationship between process maturity, quality, cycle time and effort in software projects. The authors are mainly trying to prove/
+  reject a couple of hypotheses: higher levels of process maturity lead to higher product quality in software projects, higher levels of process maturity are associated 
+  with increased cycle time in software products, higher product quality is associated with lower cycle time, higher levels of process maturity lead to increased 
+  development efforts in the project and higher product quality is associated with lower development effort.
   \item \textbf{What was the method?}
-  In order to test their hypotheses, the authors examined data coming from 30 projects belonging to the systems integration division from a large IT company.
-The process improvement data was collected via external divisions and by government agencies to provide independent assessments of the firm’s software development processes.
-Then, they analyzed a couple of key variables and see how they interact: process maturity, product quality, cycle time, development effort, product size, domain/data/decision complexity and requirements ambiguity.
+  In order to test their hypotheses, the authors examined data coming from 30 projects belonging to the systems integration division from a large IT company. The process 
+  improvement data was collected via external divisions and by government agencies to provide independent assessments of the firm’s software development processes. Then, 
+  they analyzed a couple of key variables and see how they interact: process maturity, product quality, cycle time, development effort, product size, domain/data/decision 
+  complexity and requirements ambiguity.
   \item \textbf{What did they learn?}
-  They learned that the main features they inspected are additively separable and linear.
-Moreover, they found out that higher levels of process maturity are associated with significantly higher quality, but also with increased cycle times and development efforts.
-On the other hand, the reductions in cycle time and effort resulting from improved quality outweigh the marginal increases from achieving more process maturity.
+  They learned that the main features they inspected are additively separable and linear. Moreover, they found out that higher levels of process maturity are associated 
+  with significantly higher quality, but also with increased cycle times and development efforts. On the other hand, the reductions in cycle time and effort resulting from 
+  improved quality outweigh the marginal increases from achieving more process maturity.
   \item \textbf{Relevance to our work}:
-  It can aid our research through better understanding of how various factors can influence the software development processes, thus giving more value to our own research (i.e.
-being able to automatically determine issue quality could improve better issue writing guidelines/better rules to be enforced, thus reduced triaging and development costs).
+  It can aid our research through better understanding of how various factors can influence the software development processes, thus giving more value to our own research 
+  (i.e. being able to automatically determine issue quality could improve better issue writing guidelines/better rules to be enforced, thus reduced triaging and 
+  development costs). 
 \end{itemize}

### 2017-12-05 proposal/mprop.tex
Add paper on sentiment analysis

@@
 
-\textbf{Effects of process maturity on quality, cycle time and effort in software product development}\cite{harter2000effects}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-  The research tries to investigate the relationship between process maturity, quality, cycle time and effort in software projects. The authors are mainly trying to prove/
-  reject a couple of hypotheses: higher levels of process maturity lead to higher product quality in software projects, higher levels of process maturity are associated 
-  with increased cycle time in software products, higher product quality is associated with lower cycle time, higher levels of process maturity lead to increased 
-  development efforts in the project and higher product quality is associated with lower development effort.
-  \item \textbf{What was the method?}
-  In order to test their hypotheses, the authors examined data coming from 30 projects belonging to the systems integration division from a large IT company. The process 
-  improvement data was collected via external divisions and by government agencies to provide independent assessments of the firm’s software development processes. Then, 
-  they analyzed a couple of key variables and see how they interact: process maturity, product quality, cycle time, development effort, product size, domain/data/decision 
-  complexity and requirements ambiguity.
-  \item \textbf{What did they learn?}
-  They learned that the main features they inspected are additively separable and linear. Moreover, they found out that higher levels of process maturity are associated 
-  with significantly higher quality, but also with increased cycle times and development efforts. On the other hand, the reductions in cycle time and effort resulting from 
-  improved quality outweigh the marginal increases from achieving more process maturity.
-  \item \textbf{Relevance to our work}:
-  It can aid our research through better understanding of how various factors can influence the software development processes, thus giving more value to our own research 
-  (i.e. being able to automatically determine issue quality could improve better issue writing guidelines/better rules to be enforced, thus reduced triaging and 
-  development costs). 
-\end{itemize}
-
-\subsection{Sentiment Analysis}
-
-\textbf{Thumbs Up or Thumbs Down}\cite{turney2002thumbs}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The main goal of the paper is to detect the overall sentiment transmitted
-    through reviews of various types.
-  \item \textbf{What was the method?}
-    The author created an unsupervised machine learning algorithm that was 
-    evaluated on more than 400 reviews on Epinions on various kinds of markets 
-    (e.g.\ automobiles, movie). The algorithm implementation was divided 
-    into three steps:
+As we want to analyze comments as well and how they influence the quality of a ticket, we
+need to investigate what state-of-the-art tools are available to perform sentiment analysis.
+One paper that tried to detect the overall sentiment transmitted through reviews of various 
+types is the research performed by \citet{turney2002thumbs}. The author created an unsupervised
+machine learning algorithm that was evaluated on more than 400 reviews on Epinions on various
+kins of markets. The algorithm implementation was divided into three steps:
   \begin{itemize}
@@
   \end{itemize}
-  \item \textbf{What did they learn?}
-    One thing the author learned that different categories will yield different 
-    results. For example, the automobile section on Epinions ranked much higher, 
-    84\%, compared to movie reviews, which had an accuracy of 65.83\%. Moreover, 
-    most pitfalls of the algorithm could be attributed to multiple factors, such 
-    as not using a supervised learning system or limitations of PMI-IR.
-  \item \textbf{Relevance to our work}: the method can be applied for extracting
-    sentiments from the tickets (description and comments) we will use 
-    in our own research.
-\end{itemize}
+The author learned that different categories will yield different results, such as the
+automobile section on Epinions ranked much higher, 84\%, compared to movie reviews, which
+had an accuracy of 65.83\%. Moreover, most pitfalls of the algorithm could be attributed
+to multiple factors, such as not using a supervised learning system or limitations of 
+PMI-IR.
+
+However, the work of \citet{turney2002thumbs} looks only at sentiment analysis without
+examining the context.
 

### 2017-12-05 proposal/mprop.tex
Finish background survey draft

@@
 However, the work of \citet{turney2002thumbs} looks only at sentiment analysis without
-examining the context.
-
-\textbf{Recognizing Contextual Polarity}\cite{wilson2005recognizing}:
-\begin{itemize}
-  \item \textbf{What were the goals?}
-    The paper's main goal is to find efficient ways to distinguish between 
-    contextual and prior polarity.
-  \item \textbf{What was the method?}
-    They used a two step method that used machine learning and a variety of
-    features. The first step classified each phrase which had a clue as either
-    neutral or polar, followed by taking all phrases marked in the previous step
-    and giving them a contextual polarity (e.g.\ positive, negative, 
-    both, neutral).
-  \item \textbf{What did they learn?}
-    Through the method the authors employed, they managed to automatically 
-    identify the contextual polarity. As most papers were only looking at the 
-    sentiment extracted from the overall document, they managed to get valuable 
-    results from looking at specific words and phrases.
-  \item \textbf{Relevance to our work}: when analyzing the description and
-    comments of the ticket, we can use their method for infering the sentiment 
-    transmitted probably more accurately than the technique used in 
-    Turney's paper\cite{turney2002thumbs}.
-\end{itemize}
-
-\subsection{Conclusion}
+examining the context. The research from \citet{wilson2005recognizing} tries to find
+efficient ways to distinguish between contextual and prior polarity. They used a two 
+step method that used machine learning and a variety of features. The first step 
+classified each phrase which had a clue as either neutral or polar, followed by 
+taking all phrases marked in the previous step and giving them a contextual polarity 
+(e.g. positive, negative, both, neutral). Through the method the authors employed,
+they managed to automatically identify the contextual polarity. As most papers were only
+looking at the sentiment extracted from the overall document, they managed to get 
+valuable results from looking at specific words and phrases.
 

### 2017-12-13 proposal/mprop.tex
Add first section of the introduction

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Software Ticket Quality}
+\title{Measuring Software Ticket Quality using Statistical Analysis}
 \author{Andrei-Mihai Nicolae}
@@
 \section{Introduction}\label{intro}
+% 2 - 3 pages tops
 
-% 2 - 3 pages tops
+Software engineering, compared to other engineering fields, such as
+mechanical or electrical engineering, is much more abstract - while 
+performing maintenance on a car engine or on some electric panel,
+you can actually touch the components, they are physical. However, in
+computer science and the engineering of software, you cannot see the whole picture.
+Of course one can actually open up a laptop or PC and see and touch the
+components, but the software, what is actually displayed to the user, 
+is just characters in some file that gets compiled/interpreted to machine
+code by other components which run on the operating system that, in turn,
+can communicate with the kernel (i.e. the component that sits exactly
+between the OS and the hardware) and perform the final step - send 
+different 1s and 0s encoded into electrical signals to the CPU and various
+other hardware components.
+
+Having discussed about the high level of abstraction computers expose to 
+their human operators, developing software that runs and performs as expected
+in agreement with its requirements is not trivial. Thus, developers have
+created software called \emph{issue tracking systems} that can manage
+and track \emph{tickets}, which can take various forms, such as bug 
+reports, feature requests etc. The aforementioned tickets can vary greatly
+and issue tracking systems usually allow developers to include many 
+types of information, such as:
+  \begin{itemize}
+    \item stack traces;
+    \item steps to reproduce a bug;
+    \item summary and description;
+    \item story points (e.g. how many units of time does it take one
+      developer to mark the ticket as resolved or completed).
+  \end{itemize}
+
+Thus, a still unresolved software engineering issue is how can one create
+valuable, high quality tickets?
 

### 2017-12-13 proposal/mprop.tex
Wrap up first subsection of the introduction

@@
 
+\subsection{Background}
+
 Software engineering, compared to other engineering fields, such as
@@
   \end{itemize}
+In order to create such tickets, the end users or the developers 
+themselves notice certain flaws in the software or propose new features
+to be implemented. Then, they head to the issue tracking system and 
+create tickets where they provide information wrapped up in a ticket.
+However, we are facing a main issue here, and that is what do developers 
+on the project find most important when fixing a bug/implementing a 
+new feature.
 
-Thus, a still unresolved software engineering issue is how can one create
-valuable, high quality tickets?
+Therefore, a software engineering issue still not completely resolved
+is how can one create valuable, high quality tickets?
+
+\subsection{Problem Statement}
+
+This research is trying to investigate the various components of a 
+issue tracking system ticket and specific characteristics
+
+\subsection{Research Questions and Contributions}
+
+\subsection{Proposal Structure}
 

### 2017-12-13 proposal/mprop.tex
Finish problem statement and almost complete research questions and contributions subsection

@@
 
-This research is trying to investigate the various components of a 
-issue tracking system ticket and specific characteristics
+This research is trying to investigate what makes for a high quality 
+ticket. More specifically, we are looking into the various components 
+of a ticket (e.g. summary, description, comments) and their characteristics
+in order to infer what combination of such components or what specific
+attributes help developers close the ticket quicker (i.e. time between
+ticket creation and when it is marked as CLOSED or RESOLVED).
+
+We believe that this study is valuable to the software engineering 
+community because solving the issue/ticket quality problem will help
+reduce both cost and effort in companies worldwide. 
+Having a clear understanding of what attributes make for 
+a high quality ticket will lead the project maintainers to write  
+specific guidelines in the ticket creation form (maybe even create an 
+automated system) that will help reporters include the most
+important details and structure them accordingly (e.g. for a specific
+type of project it might be essential to include stack traces so that
+developers can locate the bugs quicker), thus reducing the developers
+and triagers' effort as well as reducing costs for the companies.
+
+Furthermore, our study might also increase the likelihood of people
+reporting bugs or asking for features more often. Not having specific 
+guidelines or an automated system when creating a ticket many 
+non-technical users might be put off and give up creating the report. 
+However, if the company would put up a form where all the information
+needed can be very easily inserted, users might be more inclined 
+to report bugs and create feature requests, thus increasing the 
+software's overall quality on the long term.
 
 \subsection{Research Questions and Contributions}
+
+The main research question this study is trying to answer is 
+what makes for a valuable, high quality?
+
+However, as this is a broad research question, we have divided it into
+two sub-research questions which, when combined, would yield the 
+answer to our main research question:
+  \begin{itemize}
+    \item are there components which singularly affect the quality
+      of a ticket (e.g. well written summary) or only combinations of them 
+      (e.g. stack traces together with steps to reproduce)?
+    \item how much do specific components or combinations of them 
+      affect the quality of a ticket?
+    \item can quality be inferred solely from the ticket or do we also
+      need to consider the surrounding context (e.g. details related to
+      the version control system)?
+  \end{itemize}
 

### 2017-12-13 proposal/mprop.tex
Complete reserach questions and contributions section

@@
 
+Even though there have been many studies related to issue/ticket quality,
+most of them have looked at it qualitatively, not quantitatively (e.g. 
+\citet{bettenburg2008makes}, \citet{bettenburg2007quality}). This is 
+the first contribution of our study - we will explore the area of 
+ticket quality from a statistical point of view, not through interviews
+or other human-centered data gathering (i.e. we want to inspect several
+open source repositories and collect tickets through the issue tracking
+system's APIs).
+
+Moreover, another contribution that our study is trying to bring is that,
+even though most studies so far have looked solely at ticket 
+features/components, we want to inspect both tickets and other components
+of the software project, such as version control system and how various
+attributes affect the time-to-close for a particular ticket.
+
+The third contribution that this research tries to achieve is to
+propose a model for bug reports and/or feature requests. After collecting
+data and finding which components together with their afferent attributes
+make for a high quality ticket, we will propose a model for best practices
+in terms of creating tickets.
+
 \subsection{Proposal Structure}
-
-\begin{itemize}
-\item Background briefly explain the context of the project problem
-\item Problem statement and justification. Clearly state the problem to be addressed in your forthcoming project.
-  Explain why it would be worthwhile to solve this problem.
-
-\item Research questions and contributions
-\item Structure of the rest of the document
-\end{itemize}
 

### 2017-12-13 proposal/mprop.tex
Add some work on proposed approach

@@
 The main research question this study is trying to answer is 
-what makes for a valuable, high quality?
+what makes for a valuable, high quality ticket?
 
@@
 
+The rest of this project proposal is structured as follows:
+  \begin{itemize}
+    \item Section \ref{background_survey} presents both the study design 
+      and the background survey, which in turn is divided into three 
+      subsection:
+        \begin{itemize}
+          \item subsection \ref{data_quality} describes the literature
+            review on data quality and metrics;
+          \item subsection \ref{issue_quality} describes the background
+            survey on issue/ticket quality;
+          \item subsection \ref{waste} elicits literature on 
+            waste in software projects;
+        \end{itemize}
+    \item Section \ref{proposed_approach} describes how we would like 
+      to conduct the research;
+    \item Section \ref{work_plan} shows how we broke down the work
+      so that we keep a consistent pace throughout the lifecycle of 
+      the research.
+  \end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background Survey}
+\section{Background Survey}\label{background_survey}
 % 10 - 12 pages
@@
 
-\subsection{Data Quality and Metrics}
+\subsection{Data Quality and Metrics}\label{data_quality}
 
@@
 
-\subsection{Issue Quality}
+\subsection{Issue Quality}\label{issue_quality}
 
@@
 
-\subsection{Measuring Cost and Waste in Software Projects}
+\subsection{Measuring Cost and Waste in Software Projects}\label{waste}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proposed Approach}
+\section{Proposed Approach}\label{proposed_approach}
 
-% 3- 4 pages
+\subsection{Experimental Design}
 
-What are we actually going to do?
-
-\textbf{Research Questions}:
-\begin{itemize}
-  \item what makes for a quality software ticket that could help developers
-    fix the bug/implement the feature faster?
-  \item what can be changed in software ticket structure that could ease writing
-    such quality software tickets (e.g. add specific fields to the ticket in
-    Jira, add instructions as comments on how reporters should write such a 
-    ticket)?
-  \end{itemize}
-
-\textbf{Experimental design}: conduct a statistical analysis over popular 
-open source projects such as Mozilla or Apache and extract tickets via 
-some API (maybe REST based). Then, define what makes for 2 similar tickets
+We would like to begin the research by conducting a statistical analysis 
+over popular open source projects such as Mozilla or Apache and extract 
+tickets most probably via REST APIs, however the final list of projects
+will be finalized once some tests will be run. Then, define what makes for 2 similar tickets
 (maybe look at story points assigned by experienced triagers; probably we also
@@
 example, stack traces influenced the duration of the ticket).
+
+\subsection{Variables Tested}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Work Plan}
+\section{Work Plan}\label{work_plan}
 

### 2017-12-14 proposal/mprop.tex
Finish experimental design subsection

@@
 over popular open source projects such as Mozilla or Apache and extract 
-tickets most probably via REST APIs, however the final list of projects
-will be finalized once some tests will be run. Then, define what makes for 2 similar tickets
-(maybe look at story points assigned by experienced triagers; probably we also
-need to use only severe/critical ones as they will probably be fixed first
-and there will not be any delay, such as waiting for the main developer to come
-back from vacation) and then see how much time it took both to be completed
-so that we can infer what differences did those 2 tickets have (and see if, for
-example, stack traces influenced the duration of the ticket).
+tickets most probably via REST APIs, however the list of projects
+will be finalized once some tests will be run, and that is because
+maybe some projects will have more valuable tickets for us to analyze and
+we also decided that we want to analyze multiple issue tracking systems 
+(e.g. Apache uses Jira \citep{jira} while Mozilla uses Bugzilla 
+\citep{bugzilla}).
+
+Then, as most issue tracking systems respond with JSON payloads through 
+their REST APIs, we can easily extract components such as summary or 
+description and analyze them. We have defined that the initial list of 
+components that we want to inspect into three main categories:
+  \begin{itemize}
+    \item regular text - summary, description, story points, 
+      text in comments, status (e.g. OPEN, WONTFIX, CLOSED);
+    \item non-regular text (i.e. special structures) - stack traces,
+      steps to reproduce;
+    \item non-text - attachments in comments (e.g. images, screenshots
+      when trying to show steps to reproduce).
+  \end{itemize}
+
+Extracting text from components is rather trivial, but extracting and 
+analyzing non-text data such as images or non-regular text will be 
+more complex.
+
+For images, there are two very popular REST APIs that 
+we can use for analysis: Google Cloud Vision \citep{vision} and 
+AWS Rekognition \citep{rekognition}. When an image is sent via the API,
+the servers respond with detailed information about what can be found
+in the image, thus we can detect if the image was for example a 
+simple screenshot or if it contained multiple screenshots that were aimed
+at visually showing steps to reproduce a bug.
+
+In terms of non-regular text, steps to reproduce are usually trivial to
+retrieve (if they are not images, for which we have presented a solution
+in the above paragraph), they will most probably be written as bullet
+lists or a sequence of lines starting with \emph{Step [number] ...}, thus
+a simple regex will probably suffice. However, for stack traces, as they
+are more complex, there are no commercial or open source applications
+that could help them extract them easily, thus we will compose a special
+regex depending on the language of the project (e.g. Apache heavily 
+uses Java, thus we can look for lines starting with java.*.*Exception ...).
+
+In order to detect what features make for a high quality ticket, we need 
+to compare two \emph{similar} tickets and then analyze their components
+for differences. Thus, one of the biggest issues we will be facing is how 
+can we say that two tickets are similar. We have two initial approaches
+that we want to test to see which one is more efficient:
+  \begin{itemize}
+    \item look solely at the issue tracking system and use story points
+      to detect similar tickets; one limitation of this approach is that
+      either the triager is not experienced and might assign wrong story
+      point values or the initial story point values are not properly
+      assigned and they will be corrected during the ticket's lifecycle;
+    \item look at the version control system and compare changesets for
+      similar work effort; however, this approach has one limitation - 
+      solely looking at source code changes might not encapsulate the
+      whole effort needed to solve the task (e.g. the developers on the
+      team might spend extra hours only on designing the fix).
+  \end{itemize}
+However, this list is not final, so if we find some other method 
+while running the experiment, we shall switch to that.
+
+Finally, having similar tickets grouped together, we can then test 
+the variances in component features they possess and see which features
+affected the time-to-close the most.
 
@@
 
+The study has 
 \textbf{Independent Variables}: components of tickets - stack traces, steps

### 2017-12-14 proposal/mprop.tex
Finish proposed approach section

@@
 
-The study has 
-\textbf{Independent Variables}: components of tickets - stack traces, steps
-to reproduce, grammar error free description and summary, succinct/detailed 
-summary, complex/light discussion in comments
+The independent variables we would like to test are:
+  \begin{itemize}
+    \item presence and number of stack traces in a ticket;
+    \item steps to reproduce (as described above - images or text);
+    \item presence of screenshots in tickets;
+    \item text components (e.g. summary, description) being either 
+      succinct or detailed;
+    \item grammar-free textual description;
+    \item overall sentiment drawn from comments (e.g. angry or calm);
+    \item complex or light discussion in comments.
+  \end{itemize}
 
-\textbf{Dependent Variable}: duration of the ticket between OPEN status and
-CLOSED status.
-
-Research questions, outline experimental design, independent variables, dependent variables.
-
-state how you propose to solve the software development problem. Show that your proposed approach is feasible, but identify any risks.
+In terms of dependant variables, we only have one - the time it takes
+between when the ticket was created and marked as OPEN until when it
+is finished and marked as CLOSED or RESOLVED.
 

### 2017-12-14 proposal/mprop.tex
Add programming languages to experimental design
Create bullet pointed list for work plan section

@@
 
+Implementation wise, we would like to develop the application that will
+perform both scraping, extraction and inspection in either Go or Java
+as I am the most proficient with these two programming languages.
+
 In order to detect what features make for a high quality ticket, we need 
@@
 
+\begin{itemize}
+  \item decide which repositories to use for data (e.g. Apache, Mozilla, Eclipse);
+  \item create scraping/extraction/inspection tool using either Go or Java;
+  \item decide which approach to use for detecting similar tickets (the two
+    approaches are listed above) after testing them on the tickets retrieved
+    with the application;
+  \item collect data, run the analysis and decide which components have
+    the biggest impact on creating high quality tickets;
+  \item write abstract, introduction, related work;
+  \item write methodology and how we conducted the experiment (collecting
+    data, running analysis);
+  \item write results, contributions and conclusion for the paper.
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-12-14 proposal/mprop.tex
Complete final draft for the paper

--- 2017-12-14 proposal/mprop.tex
@@
 
-% 1 - 2 pages  structure as work packages (don't bother with a chart).
+The work on the actual project in the second semester will start off 
+with deciding and analyzing which repositories to use for ticket data.
+We have several popular open source options, such as Apache, Mozilla or
+Eclipse, so settling on a couple of options will be the first step in our
+research. We believe that this step will be finished \emph{by the end of
+January}.
 
-show how you plan to organize your work, identifying intermediate deliverables and dates.
+The next step will be to create the scraping, extraction and inspection
+tool which will be implemented in either Go or Java. This will be a vital
+component of the whole research so we believe that it will be ready to run
+\emph{by the end of February}.
 
+Then, concomitantly with the previous work package, we will decide on
+what method to use to detect similar tickets. This step will be performed
+during the creation of the tool because we can only test efficiency once
+we have some tickets to validate our ideas. Thus, the proposed deadline
+for this work package is \emph{the end of February} as well.
+
+Following we will run the the tool on the tickets we have collected. This
+is expected to be quite trivial once all the other work packages are 
+completed as we will simply need to run the application. The expected
+deadline is \emph{by 4\textsuperscript{th} of March}.
+
+Then, the actual write-up of the paper will be structured as follows:
+  \begin{itemize}
+    \item write abstract, introduction, related work - this is expected
+      to be completed \emph{by mid March};
+    \item write methodology and how we conducted the experiment (collecting
+      data, running analysis) - expected to be finished \emph{by the 
+      beginning of April};
+    \item write results, contributions and conclusion for the paper - 
+      we expect to complete it \emph{by 18\textsuperscript{th} of April}.
+  \end{itemize}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-12-18 proposal/mprop.tex
Remove commented packages
Fix up introduction section

@@
 \usepackage{natbib}
-
-% alternative font if you prefer
-%\usepackage{times}
-
-% for alternative page numbering use the following package
-% and see documentation for commands
-%\usepackage{fancyheadings}
-
-% other potentially useful packages
-%\uspackage{amssymb,amsmath}
-%\usepackage{url}
-%\usepackage{fancyvrb}
-%\usepackage[final]{pdfpages}
 
@@
 mechanical or electrical engineering, is much more abstract - while 
-performing maintenance on a car engine or on some electric panel,
+performing maintenance on a car engine or on an electric panel,
 you can actually touch the components, they are physical. However, in
@@
 components, but the software, what is actually displayed to the user, 
-is just characters in some file that gets compiled/interpreted to machine
-code by other components which run on the operating system that, in turn,
+is a multitude of layers on top of each other: it starts with a number of characters in some file;
+then, that file gets compiled or interpreted to machine
+code by other components which run on the operating system; then, these components
 can communicate with the kernel (i.e. the component that sits exactly
-between the OS and the hardware) and perform the final step - send 
+between the OS and the hardware) and eventually perform the final step - send 
 different 1s and 0s encoded into electrical signals to the CPU and various
@@
 
-Having discussed about the high level of abstraction computers expose to 
-their human operators, developing software that runs and performs as expected
-in agreement with its requirements is not trivial. Thus, developers have
+As previously mentioned, there are many levels of abstraction that computers expose to 
+their human operators, thus developing software that runs and performs as expected
+in agreement with its requirements is not trivial. Therefore, developers have
 created software called \emph{issue tracking systems} that can manage
-and track \emph{tickets}, which can take various forms, such as bug 
+and track \emph{tickets} of various forms such as bug 
 reports, feature requests etc. The aforementioned tickets can vary greatly
@@
 to be implemented. Then, they head to the issue tracking system and 
-create tickets where they provide information wrapped up in a ticket.
-However, we are facing a main issue here, and that is what do developers 
-on the project find most important when fixing a bug/implementing a 
+create tickets containing the necessary information.
+However, we are facing a main issue here, and that is understanding the
+key elements the developers look for when fixing a bug or implementing a 
 new feature.
@@
 Therefore, a software engineering issue still not completely resolved
-is how can one create valuable, high quality tickets?
+is how can one create valuable, high quality tickets.
 
@@
 
-This research is trying to investigate what makes for a high quality 
-ticket. More specifically, we are looking into the various components 
+This research is investigating the features of a high quality ticket.
+More specifically, it is looking into the various components 
 of a ticket (e.g. summary, description, comments) and their characteristics
@@
 type of project it might be essential to include stack traces so that
-developers can locate the bugs quicker), thus reducing the developers
-and triagers' effort as well as reducing costs for the companies.
+developers can locate the bugs quicker), which will in turn reduce
+overall costs and developers/triagers' effort.
 
 Furthermore, our study might also increase the likelihood of people
-reporting bugs or asking for features more often. Not having specific 
+reporting bugs or asking for more specific features more often. Not having specific 
 guidelines or an automated system when creating a ticket many 
@@
 However, as this is a broad research question, we have divided it into
-two sub-research questions which, when combined, would yield the 
+three sub-research questions which, when combined, would yield the 
 answer to our main research question:
@@
 
-Moreover, another contribution that our study is trying to bring is that,
+Moreover, another contribution is that,
 even though most studies so far have looked solely at ticket 
@@
 
-The third contribution that this research tries to achieve is to
-propose a model for bug reports and/or feature requests. After collecting
-data and finding which components together with their afferent attributes
+The third contribution is a proposed model for bug reports and/or feature requests.
+After collecting data and finding which components together with their afferent attributes
 make for a high quality ticket, we will propose a model for best practices

### 2017-12-18 proposal/mprop.tex
Fix up second section

@@
 attributes help developers close the ticket quicker (i.e. time between
-ticket creation and when it is marked as CLOSED or RESOLVED).
+ticket creation and marked as CLOSED or RESOLVED).
 
@@
 We analyzed data quality mainly in software organizations and looked at what metrics
-are most useful when trying to perform measurements. We also tried to find different
+are most useful when performing measurements. We also found different
 methodologies that either measure data quality or calculate the impact of poor data
@@
 features are most important in improving the quality of a ticket, the issue quality
-literature I have reviewed proved to be beneficial and provided valuable insight into
+literature reviewed proved to be beneficial and provided valuable insight into
 how other researchers tried to approach this problem.
 
-The third topic was waste in software projects and how it impacts them. We needed to
+The third topic was waste and its impact on software projects. We needed to
 look into various communication and tool-related waste in software projects because
@@
 compromise the evaluation process. We investigated researches that looked into what
-are the main types of waste in software projects and how it can be avoided so that
+the main types of waste are and how it can be avoided so that
 we could apply the findings into selecting the projects.
@@
 to analyze the textual representation of comments and see if the overall 
-sentiment influences the time it takes to close a ticket (i.e. maybe a negative 
-conversation in comments might increase the time it takes to solve the issue).
+sentiment influences the time it takes to close a ticket (i.e. a conversation
+might unnecessarily delay solving the ticket).
 
@@
 literature review process was finding relevant papers that could aid us in
-our research and splitting them into the categories mentioned above. There were
-a couple of key search phrases that I started with (along with slight variations):
+our research and splitting them into the categories mentioned above. The
+key search phrases used (with slight variations) are as follows:
   \begin{itemize}
@@
 
-Then, after reading the papers retrieved when searching for the above-mentioned
-phrases, I also applied the snowballing research technique as per Dr. Storer's 
-advice. This extra step was helpful and allowed me to easily find linked 
-papers and correlate them in this literature review.
-
-Moreover, when reading papers, one key aspect for selecting and including it
-in the literature review was citation count. Thus, after finding the most 
-cited papers, I then checked to see the journal where it was published so that
-we would only have material from the most important journals.
-
-Even though the literature review contains around 40 papers, there were
-around 80 papers that were reviewed but roughly half of them were excluded 
-because they eventually proved to not be so relevant to our research.
+The snowballing research technique was also applied when retrieving papers for the
+background review. Citation count and publication journal were two important aspects 
+when selecting papers - the most cited papers, published in the top quality journals were reviewed.
 
@@
 software projects, both open source (5 projects) as well as closed source (1 
-project), in order to infer what determines if it has quality. They selected 
+project), in order to infer what determines their quality. They selected 
 various sources of information, among which bug tracking 
@@
 the logs with the bug tracker contents as they are not integrated by default. 
-On the other hand, \citet{strong1997data} conducted a qualitative analysis
+A different approach was taken by \citet{strong1997data} who conducted a qualitative analysis
 instead of quantitative by collecting data from 42 data quality projects by 
@@
 The work of \citet{kitchenham1996software} looks specifically at defining
-quality in a software projects, as well as finding who are the people in charge of 
-this and how should they approach achieving it. They tried to define quality 
+quality in a software project, as well as finding who the people in charge of this 
+are and how they should approach achieving it. They tried to define quality 
 in software projects and analyze techniques that measure such metrics by looking
-at other models proposed in different other researches, such as McCall's quality
+at other models proposed in different researches, such as McCall's quality
 model or ISO 9126. However, they learned that quality is very hard to define and
@@
 the 6th release of the OpenSUSE project and its components defined by C
-functions. The research's results show that Linux applications have high quality 
+functions. The results show that Linux applications have high quality 
 code standards that one might expect in an open source repository, but 
@@
 
-After defining what data quality is and what are its characteristics, the next 
-step would be how to measure data or information quality in a project.
+After defining what data quality is and its characteristics, the next 
+step would be data measurement or information quality in a project.
 
@@
   \end{itemize} 
-After developing the technique, they applied it at 5 different organizations and
+After developing the technique, they applied it in 5 different organizations and
 found that the tool proved to be practical.
@@
 Another important area of data quality is what methodologies or techniques can 
-be applied by organizations in order to improve data quality. 
+be applied by organizations in order to improve it. 
 There are several studies that tried to propose such methodologies. A general 
@@
 However, there are other aspects that can be investigated when trying to improve
-data quality. For example, \citet{prybutok2008evaluating} tried to find if 
+data quality. For example, \citet{prybutok2008evaluating} tested whether  
 leadership and information quality can lead to positive outcomes in an 
@@
 One such research is the one done by \citet{gorla2010organizational}. They wanted
-to examine what influences do system quality, service quality and data quality
-have on an organization, as well as what effect does system quality have on
+to examine the influences of system quality, service quality and data quality
+on an organization, as well as what effect does system quality have on
 data quality. After conducting a construct measurement for the information
@@
 knowledge at work in the data production process and if these gaps are not 
-bridged it might lead to decrased data quality.
+bridged it might lead to decreased data quality.
 
@@
 Issue quality is the main topic of this literature review as it revolves around
-software tickets and what are the characteristics of a well-written and 
+software tickets and the characteristics of a well-written and 
 informative bug report, how efficient are bug tracking systems, what defines
@@
 
-\citet{bettenburg2008makes} have tried, through their work, to analyze what 
+\citet{bettenburg2008makes} analyzed what 
 makes for a good bug report through qualitative analysis. They interviewed over
@@
 linking the stack traces to changes in the source code (change logs) by mining
-the version repository of the Eclipse project. The results were that 
+the version repository of the Eclipse project. The results showed that 
 around 60\% of the bugs that contained stack traces in their reports were fixed
@@
 
-Following on the conclusions of \citet{bettenburg2008makes} we have found out
-that the investigations undertaken by \citet{bettenburg2007quality} reveal 
-very similar results. They performed the same type of evaluation method (i.e. 
+After examining the work of \citet{bettenburg2007quality}, we noticed that
+the authors found very similar results to the ones presented in the research of \citet{bettenburg2008makes}. 
+They performed the same type of evaluation method (i.e. 
 interviews with developers) and confirmed that steps to reproduce and stack traces
@@
 However, \citet{kim2013should} propose a rather different technique than the one
-exposed in \citet{bettenburg2012using}. The authors have employed a two-phase
+exposed in \citet{bettenburg2012using}. The authors employed a two-phase
 recommendation model that would locate the necessary fixes based on information
@@
 could be summarized effectively and automatically so that developers would
-need only to analyze summaries instead of full tickets. Firstly, they asked
+need only analyze summaries instead of full tickets. Firstly, they asked
 university students to volunteer to annotate the bug reports collected from
@@
 bug report is the one proposed by \citet{zhou2012should}. The authors
-firstly performed a textual analysis, looking for similarities between the bug 
+first performed a textual analysis, looking for similarities between the bug 
 report description and the source code files. Then, it analyzed previous bugs in 
@@
 based on the information available, determine their severity and assign them to the
-most qualified available developer to fix them. If the ticket would be valuable
-and have an increased index of quality, the triaging process would be quicker and,
+most qualified available developer to fix them. If the ticket was valuable and had 
+an increased index of quality, the triaging process would be quicker and,
 thus, reduce the cost for the organization. There are several researches that 
@@
 
-One such example is the work of \citet{anvik2006automating}. The authors tried
-to automate the process of bug report assignment by employing a machine learning 
+One such example is the work of \citet{anvik2006automating}. The authors
+automated the process of bug report assignment by employing a machine learning 
 algorithm which, after receiving as input various types of information (e.g. 
@@
 discover developer networks and team structures, as well as help to better assign 
-developers to bug reports. They analyzed 145.000 bug reports from Eclipse and 
-300000 from Mozilla and then, using statistical analysis on the bug reports in 
+developers to bug reports. They analyzed 145,000 bug reports from Eclipse and 
+300,000 from Mozilla and then, using statistical analysis on the bug reports in 
 order to find evolution histories and changes throughout the lifetime of the 
@@
 ticket) automatically. The authors conducted their research on the Mozilla,
-Eclipse and GNOME projects and divided their method into 5 steps:
+Eclipse and GNOME projects and divided their method into four steps:
   \begin{itemize}
@@
 coordination activities in terms of software projects coordination and propose different
-directions on how to implement proper tools. Firstly, the conducted a field study which was
+directions on how to implement proper tools. They conducted a field study which was
 split into two parts:
@@
 around another major software activity, i.e. software cost estimation? The paper from 
-\citet{grimstad2006framework} tried to show that poor estimation analysis techniques
+\citet{grimstad2006framework} showed that poor estimation analysis techniques
 in software projects will lead to wrong conclusions regarding cost estimation accuracy.
@@
 maturity on quality, cycle time and effort is the one undergone by \citet{harter2000effects}. The
-research tries to prove or reject several hypotheses, such as higher levels of process maturity lead 
+research proves and rejects several hypotheses, such as higher levels of process maturity lead 
 to higher product quality, higher levels of process maturity are associated with increased cycle time,
@@
 However, the work of \citet{turney2002thumbs} looks only at sentiment analysis without
-examining the context. The research from \citet{wilson2005recognizing} tries to find
+examining the context. The research from \citet{wilson2005recognizing} found
 efficient ways to distinguish between contextual and prior polarity. They used a two 

### 2017-12-18 proposal/mprop.tex
Finish fixing up proposal

@@
 maybe some projects will have more valuable tickets for us to analyze and
-we also decided that we want to analyze multiple issue tracking systems 
+we want to analyze multiple issue tracking systems 
 (e.g. Apache uses Jira \citep{jira} while Mozilla uses Bugzilla 
@@
 Implementation wise, we would like to develop the application that will
-perform both scraping, extraction and inspection in either Go or Java
-as I am the most proficient with these two programming languages.
+perform both scraping, extraction and inspection in either Go or Java.
 
@@
 to compare two \emph{similar} tickets and then analyze their components
-for differences. Thus, one of the biggest issues we will be facing is how 
-can we say that two tickets are similar. We have two initial approaches
+for differences. Thus, one of the biggest issues we will be facing is 
+comparing and contrasting tickets. We have two initial approaches
 that we want to test to see which one is more efficient:
@@
 
-Finally, having similar tickets grouped together, we can then test 
+Finally, grouping similar tickets together allows testing 
 the variances in component features they possess and see which features
@@
 
-The independent variables we would like to test are:
+The independent variables proposed for testing are:
   \begin{itemize}
@@
 
-In terms of dependant variables, we only have one - the time it takes
+In terms of dependent variables, there is only one - the time it takes
 between when the ticket was created and marked as OPEN until when it
@@
 with deciding and analyzing which repositories to use for ticket data.
-We have several popular open source options, such as Apache, Mozilla or
+There are several popular open source options, such as Apache, Mozilla or
 Eclipse, so settling on a couple of options will be the first step in our
@@
 
-Then, concomitantly with the previous work package, we will decide on
-what method to use to detect similar tickets. This step will be performed
-during the creation of the tool because we can only test efficiency once
-we have some tickets to validate our ideas. Thus, the proposed deadline
-for this work package is \emph{the end of February} as well.
+Then, concomitantly with the previous work package, the method used to 
+detect similar tickets will be decided on. This step will be performed
+during the creation of the tool because efficiency can only be evaluated
+once ideas have been validated via execution of several mock tickets. 
+Thus, the proposed deadline for this work package is \emph{the end of February} as well.
 
-Following we will run the the tool on the tickets we have collected. This
-is expected to be quite trivial once all the other work packages are 
-completed as we will simply need to run the application. The expected
-deadline is \emph{by 4\textsuperscript{th} of March}.
+Following, tickets collected will be run in the tool created as per the previous steps. 
+The expected deadline is \emph{by 4\textsuperscript{th} of March}.
 
@@
       to be completed \emph{by mid March};
-    \item write methodology and how we conducted the experiment (collecting
+    \item write methodology (collecting
       data, running analysis) - expected to be finished \emph{by the 

### 2017-12-18 proposal/mprop.tex
Add reference to Brooks' mythical man month

@@
 Software engineering, compared to other engineering fields, such as
-mechanical or electrical engineering, is much more abstract - while 
+mechanical or electrical engineering, is much more abstract \citep{brooks1995mythical}- while 
 performing maintenance on a car engine or on an electric panel,

### 2017-12-18 proposal/mprop.tex
Add papers between brackets on proposal summary at the top

@@
 can communicate with the kernel (i.e. the component that sits exactly
-between the OS and the hardware) and eventually perform the final step - send 
-different 1s and 0s encoded into electrical signals to the CPU and various
-other hardware components.
+between the OS and the hardware) and eventually, after several other layers, 
+perform the final step - send different 1s and 0s encoded into electrical signals 
+to the CPU and various other hardware components.
 
@@
 from software projects and the tools that revolve around them, such as issue 
-trackers and version control systems. Thus, \emph{data quality} is an important 
-topic that needed to be explored in order to infer appropriate conclusions.
+trackers and version control systems. Thus, \emph{data quality} (\cite{bachmann2009software}, 
+\cite{strong1997data}, \cite{kitchenham1996software},
+\cite{stamelos2002code}, \cite{lee2002aimq}, \cite{Heinrich2007MetricsDataQuality},
+\cite{nelson2005antecedents}, \cite{pipino2002data}, \cite{wang1998product},
+\cite{prybutok2008evaluating}, \cite{gorla2010organizational}, \cite{swanson1997maintaining},
+\cite{redman1998impact}, \cite{lee2003knowing}) is an important topic that needed to be explored in order to infer 
+appropriate conclusions.
 
@@
 
-Secondly, probably the topic of most interest to our research is \emph{issue quality}.
+Secondly, probably the topic of most interest to our research is \emph{issue quality}
+(\cite{bettenburg2008makes}, \cite{hooimeijer2007modeling}, \cite{schroter2010stack},
+\cite{bettenburg2008extracting}, \cite{bettenburg2007quality}, \cite{bettenburg2008duplicate},
+\cite{bettenburg2012using}, \cite{kim2013should}, \cite{rastkar2010summarizing}, 
+\cite{zhou2012should}, \cite{fischer2003analyzing}, \cite{just2008towards}, 
+\cite{anvik2006automating}, \cite{anvik2011reducing}, \cite{anvik2006should}, 
+\cite{jeong2009improving}, \cite{Naguib2013BugReportAssignee}, \cite{lamkanfi2010predicting})
 This field is mainly concerned with software tickets and their characteristics: how
@@
 
-The third topic was waste and its impact on software projects. We needed to
+The third topic was \emph{waste} (\cite{sedano2017software}, \cite{Korkala2014WasteIdentification},
+\cite{ikonen2010exploring}, \cite{aranda2009secret}, \cite{grimstad2006framework},
+\cite{harter2000effects}, \cite{turney2002thumbs}, \cite{wilson2005recognizing}) and its impact on software projects. We needed to
 look into various communication and tool-related waste in software projects because

### 2017-12-18 proposal/mprop.tex
Finish proposal

@@
 step would be data measurement or information quality in a project. 
-
 There are several research papers that try to find the answer, among which the 
@@
     \item psychological distress.
-    \item \textbf{Relevance to our work}: this paper complements the previous 
-      one on waste identification\cite{Korkala2014WasteIdentification}.
   \end{itemize}
@@
   \end{itemize}
-Eventually they reached two main conclusions:
+They reached two main conclusions:
   \begin{itemize}
@@
 
-But what happens when a project gains maturity? A work that investigates the effects of process
-maturity on quality, cycle time and effort is the one undergone by \citet{harter2000effects}. The
+\citet{harter2000effects} explored the effects of process maturity on quality, cycle time and effort. The
 research proves and rejects several hypotheses, such as higher levels of process maturity lead 
@@
 
-\subsection{Experimental Design}
+Having reviewed the literature on state of the art approaches to what features
+are most important when composing a high quality ticket, our work will
+build on top of these methods and will try to improve the validity of the
+results through statistical analysis. In the following subsections 
+(\ref{experimental_design}, \ref{variables_tested} \ref{contributions}) we will
+discuss how the experiment was designed, what variables were chosen
+as dependent and independent as well as what contributions our study will bring.
 
-We would like to begin the research by conducting a statistical analysis 
+\subsection{Experimental Design}\label{experimental_design}
+
+The study we will undergo tries to identify the key components that make
+for a valuable, high quality ticket. We would like to begin the research by 
+conducting a statistical analysis 
 over popular open source projects such as Mozilla or Apache and extract 
@@
 Then, as most issue tracking systems respond with JSON payloads through 
-their REST APIs, we can easily extract components such as summary or 
+their REST APIs, we can extract components such as summary or 
 description and analyze them. We have defined that the initial list of 
@@
 
-Implementation wise, we would like to develop the application that will
+Implementation wise, we will develop the application that will
 perform both scraping, extraction and inspection in either Go or Java.
@@
 
-\subsection{Variables Tested}
+\subsection{Variables Tested}\label{variables_tested}
 
@@
     \item steps to reproduce (as described above - images or text);
-    \item presence of screenshots in tickets;
+    \item presence of screenshots in tickets and associated image quality metrics;
     \item text components (e.g. summary, description) being either 
@@
 is finished and marked as CLOSED or RESOLVED.
+
+\subsection{Contributions}\label{contributions}
+
+As we have previously mentioned, the main three contributions we will 
+bring are as follows:
+  \begin{itemize}
+    \item explore the area of ticket quality through statistical analysis;
+    \item inspect both tickets and other components of the software project
+      (e.g. version control system) when analysing ticket quality;
+    \item propose model for bug reports and/or feature requests.
+  \end{itemize}
 

### 2017-12-18 proposal/mprop.tex
Fix bug

@@
 results through statistical analysis. In the following subsections 
-(\ref{experimental_design}, \ref{variables_tested} \ref{contributions}) we will
+(\ref{experimental_design}, \ref{variables_tested}, \ref{contributions}) we will
 discuss how the experiment was designed, what variables were chosen

### 2018-04-17 paper/paper.tex
Refactor the tex file for the paper
Add title and reformat intro page
Create skeleton for the whole paper with sections in the right places

--- 2017-10-14 paper/example.tex
@@
-%% example.tex
-%% Jeremy Singer
-%% 16 Oct 12
-
 \documentclass{mpaper}
@@
 
-\title{An Example Paper for MSci Submission}
-\author{Jeremy Singer}
-\matricnum{12345678}
+\title{Measuring Software Ticket Quality using Statistical Analysis}
+\author{Andrei-Mihai Nicolae}
+\matricnum{2147392}
 
@@
 \begin{abstract}
-According to Simon Peyton Jones, an abstract should address
-four key questions. First, what is the problem that this
-paper tackles? Second, why is this an interesting problem?
-Third, what is the solution this paper proposes?
-Finally, why is the proposed solution a good one?
+
 \end{abstract}
@@
 
-\section{Background}
+\section{Related Work}
 
@@
 
-\section{The WizWoz System}
+\section{Building the Data Set}
 
@@
 
-\section{Evaluation}
+\section{Characterising the Data Set}
 
@@
 
+\section{Correlations}
+
+\section{Future Work}
+
 \section{Conclusions}
 
-The standard Lorem Ipsum passage, used since the 1500s
-
-``Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.''
 \vskip8pt \noindent
 {\bf Acknowledgments.}
-This is optional; it is a location for you to thank people
+Tim, my parents, Corina.
 
 \bibliographystyle{abbrv}
-\bibliography{example}
+\bibliography{paper}
 

### 2018-04-17 paper/paper.tex
Complete abstract section

@@
 \begin{abstract}
-
+Software tickets are of valuable importance to the whole computing science 
+field - they guide engineers towards better planning, management 
+and tracking of their progress throughout complex projects. However, there
+are few studies that investigate what makes for a high quality,
+valuable ticket. This can lead to multiple issues in a company, such as 
+increased communication friction between developers and end users filing bug
+reports, as well as increased overall costs due to waste of development effort. 
+In this research paper, we present our findings after 
+investigating a large number of variables surrounding software tickets, 
+such as whether the presence of stack traces influence the time 
+to close for the ticket. Our results show that the presence and type of attachments,
+comments complexity (i.e. number of comments per ticket), grammar correctness scores
+as well as the sentiment drawn from the comments can influence the quality of the ticket.
+We bring a couple of novel aspects to the research
+community including one of the largest dataset statistically analysed in the field,
+as well as state-of-the-art sentiment and grammar correctness analysis.
 \end{abstract}
@@
 In earlier years, MSci students at the School of Computing
-Science\footnote{\url{http://www.dcs.gla.ac.uk}},
+Science,
 University of Glasgow, were expected to produce a full-length
@@
 paper on his
-website\footnote{\url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}}.
+website.
 Personally, I put URLs in footnotes and \emph{bona fide} references
@@
 
-\begin{quotation}
- The Assyrian came down like the wolf on the fold,
- And his cohorts were gleaming in purple and gold;
- And the sheen of their spears was like stars on the sea,
- When the blue wave rolls nightly on deep Galilee.
-
- Like the leaves of the forest when Summer is green,
- That host with their banners at sunset were seen:
- Like the leaves of the forest when Autumn hath blown,
- That host on the morrow lay withered and strown.
-\end{quotation}
-
 \section{Correlations}

### 2018-04-17 paper/paper.tex
Complete introduction section

@@
 
-This paper outlines the standard template for an MSci submission.
-In earlier years, MSci students at the School of Computing
-Science,
-University of Glasgow, were expected to produce a full-length
-dissertation. Now, the requirement is for MSci students to
-write a paper of up to 14 pages in length, using the supplied
-\texttt{mpaper} \LaTeX style file.
+In the past decade, technology has drastically increased its influence on 
+virtually every aspect of our society. Therefore, software projects have 
+inherently become more complex and require increasing number of developers in
+the team. Due to this, software engineers have created issue tracking systems,
+a means of planning, managing and tracking work products in the form of 
+\emph{software tickets} or \emph{issues}.
 
-The precise structure of an MSci paper is not mandated, but it should
-probably cover in detail the following aspects of the project.
-\begin{enumerate}
-\item General description of the problem, motivation, relevance
-\item Background information, possibly including a literature survey
-\item Description of approach taken to solve the problem, including
-  high-level design and lower-level implementation details as appropriate
-\item Evaluation, qualitative or quantitative as appropriate
-\item Conclusion, including scope for future work
-\end{enumerate}
+There are multiple platforms for providing such issue tracking systems, among which
+the most popular are Jira \cite{jira} and Bugzilla \cite{bugzilla}. For both platforms,
+the tickets are split into two main categories: feature requests (i.e. feature to be 
+implemented into the system) and bug reports (i.e. issue encountered by an end user or
+discovered by a developer in the codebase). Regardless of the type of ticket, they provide
+various types of information that can be filled in by the reporter, including:
+  \begin{itemize}
+    \item summary - short description of the feature to be implemented/encountered bug;
+    \item description - longer textual field which goes into more detail regarding the ticket;
+    it can include various types of information, such as stack traces or steps to reproduce a bug;
+    \item attachments - screenshots, snippets of code or configuration files that might help
+    close the ticket faster;
+    \item comments - each ticket can have any number of comments where the people interested in 
+    it can talk about what might have caused the bug, how to fix it etc.
+  \end{itemize}
+
+Even though tickets provide such comprehensive information regarding a specific task, studies have shown 
+that fixing bugs is one of the most common tasks performed by developers \cite{latoza2006maintaining}. One of
+the reasons for this is the communication friction between developers and end users \cite{Korkala2014WasteIdentification}
+as developers might need clarification regarding what information the users have provided (e.g. cannot reproduce the bug, 
+screenshot is unclear). Another main reason for this waste of effort on solving tickets, according to 
+Just et. al \cite{just2008towards} and Zimmermann et. al \cite{zimmermann2009improving}, is the generally poor design of issue 
+tracking systems. This can lead to various issues, including increased costs for the company, wasted development effort, 
+decreased customer satisfaction and overall poor performance.
+
+Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
+that would improve the overall performance of the development team and, inherently, the company. As there are many 
+fields in a ticket, the number of unanswered questions is rather large: do stack traces have an influence on the quality
+of a ticket? What about attachments and whether a screenshot is more helpful than a snippet of code? Does a negative sentiment
+drawn from comments increase or decrease the time taken to solve a bug? How does grammar correctness influence the 
+communication friction?
+
+In this research paper, we present and discuss our findings after running a statistical analysis 
+on over 300,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
+with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
+from a Jira instance, analyze them, generate plots and run statistical tests.
+
+During the analysis part, we investigate several variables in correlation with \emph{time-to-complete}, 
+which we define as the \emph{metric of quality} (\emph{time-to-complete} represents the period of time between the creation 
+and the closing of a ticket). There are multiple novel aspects brought by our study, among which is the fact that it is one of 
+the very few studies that have tackled this issue using a quantitative rather than a qualitative approach (with a very 
+large number of tickets analysed) and also that it uses state-of-the-art sentiment \cite{wilson2005recognizing} as well as 
+grammar correctness analysis techniques \cite{wilson2005recognizing}. We believe that our results are valuable 
+contributions to the research community and the database produced after the analysis can help further studies with 
+analyzed and well-tested data.
 
@@
 \texttt{table*} environments. For an example, see Figure \ref{fig-eg}.
-
-\begin{table}
-\begin{tabular}{l||c||p{2cm}}
-\emph{Operating System} & \emph{Version} & \emph{Verdict} \\ \hline \hline
-Ubuntu & 12.04 & Everyone's favourite Linux, unless you grew up with
-RedHat \\ \hline
-Slackware & xxx & Pseudo-hacker's Linux, how often do you recompile
-your kernel? \\ \hline
-Mac OS & 10.7 & For people with more money than sense \\ \hline
-\end{tabular}
-\caption{\label{tab-eg}Single column table of figures}
-\end{table}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.3]{images/alice.pdf}
-\end{center}
-\caption{\label{fig-eg}An example figure stretching over two columns}
-\end{figure*}
 
@@
 \end{document}
+
+% \begin{table}
+% \begin{tabular}{l||c||p{2cm}}
+% \emph{Operating System} & \emph{Version} & \emph{Verdict} \\ \hline \hline
+% Ubuntu & 12.04 & Everyone's favourite Linux, unless you grew up with
+% RedHat \\ \hline
+% Slackware & xxx & Pseudo-hacker's Linux, how often do you recompile
+% your kernel? \\ \hline
+% Mac OS & 10.7 & For people with more money than sense \\ \hline
+% \end{tabular}
+% \caption{\label{tab-eg}Single column table of figures}
+% \end{table}
+
+% \begin{figure*}
+% \begin{center}
+% \includegraphics[scale=0.3]{images/alice.pdf}
+% \end{center}
+% \caption{\label{fig-eg}An example figure stretching over two columns}
+% \end{figure*}

### 2018-04-17 paper/paper.tex
Include flow figure and start completing the data set section

@@
 
-This \LaTeX template is based on the ACM \texttt{sig-alternate} class.
-The layout is two-column text. Generally figures and tables only
-extend to one column width, e.g.\ Table \ref{tab-eg},
-but it is possible to make them
-stretch over both columns using the \texttt{figure*} and
-\texttt{table*} environments. For an example, see Figure \ref{fig-eg}.
-
 \section{Building the Data Set}
 
-Again, Simon Peyton Jones has a lovely description of how to write a
-paper on his
-website.
-Personally, I put URLs in footnotes and \emph{bona fide} references
-in the bibliography. For instance, Turing \cite{turing37computable}
-and Knuth \cite{knuth68art} would not be out of place in list of
-references.
-How many references? Hard to say. Five is not enough, 50 is pushing
-it.
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.3]{images/flow.png}
+\end{center}
+\caption{\label{fig-eg}Flow of the whole application.}
+\end{figure*}
 
-\subsection{User Interface}
+The first step to building the data set was to create a tool that was able to execute all the commands that we required:
+fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
+automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
+we decided that Go was the best way to go for various reasons:
+  \begin{itemize}
+    \item it is designed with simplicity in min, thus making it easier for others who might join the project to read 
+    and understand the codebase;
+    \item it is compiled, statically typed, which implies that it is a much faster candidate than other interpreted languages
+    such as Ruby or Python;
+    \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
+  \end{itemize}
 
-Blah blah blah
-Blah blah blah
-Blah blah blah
-Blah blah blah
+Figure \ref{} The following two subsections will describe in detail how the process of building the data set was undergone.
 
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Foo}
+\subsection{Fetch and Store}
 
-Blah blah blah
-Blah blah blah
-Blah blah blah
+This is the first command implemented in our tool - it is desgined to fetch, from any valid Jira URL, any number of tickets 
+and then store everything inside an instance of BoltDB \cite{bolt}, which is a very simple yet powerful key-value pair 
+database. The whole process is parallelized with the possibility of scaling even up to hundreds of goroutines
+(i.e. lightweight threads) running concurrently.
 
-\subsubsection{Bar}
-\textsf{Blah} \textit{blah} \textbf{blah}
+In terms of projects selected, we have opted for the Apache Software Foundation which open-sourced some of the most popular
+software applications. Moreover, they have all their projects' issue tracking systems hosted on Jira, thus we could also 
+achieve consistency easier.
+
+\subsection{Analyse}
 
@@
 
-Graphs are always good. I recommend getting to grips with Matlab, R or
-gnuplot rather than exporting horribly Excel bitmapped graphs.
+\subsection{Attachments}
+
+\subsection{Comments}
+
+\subsection{Summary and Description}
+
+\subsection{Grammar Correctness}
+
+\subsection{Sentiment Analysis}
+
+\subsection{Steps to Reproduce}
+
+\subsection{Stack Traces}
 

### 2018-04-17 paper/paper.tex
Improve title of the paper
Make flow image show in the pdf
Add analyse subsection for paper

@@
 
-\title{Measuring Software Ticket Quality using Statistical Analysis}
+\title{Measuring Software Ticket Quality using Quantitative Data Analysis}
 \author{Andrei-Mihai Nicolae}
@@
 \section{Introduction}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{images/flow.pdf}
+\end{center}
+\caption{\label{fig-eg}Application flow of the Go tool.}
+\end{figure*}
 
@@
 
-In this research paper, we present and discuss our findings after running a statistical analysis 
+In this research paper, we present and discuss our findings after running a quantitative data analysis 
 on over 300,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
@@
 \section{Building the Data Set}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.3]{images/flow.png}
-\end{center}
-\caption{\label{fig-eg}Flow of the whole application.}
-\end{figure*}
-
-The first step to building the data set was to create a tool that was able to execute all the commands that we required:
+The first step towards building the data set was to create a tool that was able to execute all the commands that we required:
 fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
@@
 
-Figure \ref{} The following two subsections will describe in detail how the process of building the data set was undergone.
+Then, we split our tool into four main commands: \emph{store}, \emph{analyse}, \emph{plot} and \emph{stats}. They all 
+follow the flow shown in figure \ref{fig-eg} and complete the whole application cycle, in the end producing a database 
+of analysed tickets, as well as plots and statistics for investigating correlations, saved on the filesystem.
+
+In the following two subsections we describe how we designed and implemented the commands mentioned above.
 
@@
 
-In terms of projects selected, we have opted for the Apache Software Foundation which open-sourced some of the most popular
-software applications. Moreover, they have all their projects' issue tracking systems hosted on Jira, thus we could also 
-achieve consistency easier.
+We have interacted with the Jira Server REST API which has very good documentation written by the Atlassian team. After getting
+familiar with all the features the REST API offers, we have opted for getting paginated issues from the server, which means 
+slicing the whole set of tickets into multiple smaller arrays to improve performance and reduce the load on the server. We also
+specified to Jira exactly what set of issue fields to return and, eventually, while responses were retrieved from the instance,
+we began storing them into our Bolt DB instance. The way we chose to store them was to set the issue key (i.e. unique 
+identifier that differentiates a ticket from all others across all projects inside a Jira instance) as the key of the pair and
+the value is the whole representation of an issue (e.g. attachments, story points, priority) as a JSON encoded value. This
+helped us reduce the size of the database once we reached hundreds of thousands of tickets.
 
@@
 
+Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
+fetches all the issues in the database. Then, it runs in parallel the \emph{seven types of analysis}:
+\begin{itemize}
+  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
+  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
+  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
+  influence the quality of a ticket;
+  \item \emph{stack traces} - runs complex regex for detecting stack traces in either summary, description or comments 
+  and verifies whether their presence influence Time-To-Close for the ticket;
+  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
+  having many words or comments decreases or increases Time-To-Close for the ticket;
+  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description;
+  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
+  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
+  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
+  (e.g. unknown token, misspell);
+  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
+  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
+  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 is completely negative, 1 is completely 
+  positive).
+\end{itemize}
+
+Implementation wise, the application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
+but heavy on resource utilization) or slices them into smaller arrays to get processed afterwards (harder to parse as it 
+eventually requires re-creation of the whole array of tickets before inserting back into the database, but it is much 
+lighter on computing power). After having the tickets available, we start looping through them and perform all 
+analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
+its corresponding field in the ticket struct and subsequently stored back in the database. We chose this approach because 
+we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
+already available there. Moreover, for external analysis such as hitting Google Cloud Platform APIs, there are costs for 
+running the analysis, thus in this way we drastically reduce overall costs for the project.
+
+\subsection{Plot and Statistical Tests}
+
 \section{Characterising the Data Set}
+
+\section{Correlations}
 
@@
 \subsection{Stack Traces}
-
-\section{Correlations}
 

### 2018-04-18 paper/paper.tex
Add additional information to introduction and finalize analyse subsection

@@
 \section{Introduction}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=\textwidth]{images/flow.pdf}
-\end{center}
-\caption{\label{fig-eg}Application flow of the Go tool.}
-\end{figure*}
 
@@
 that would improve the overall performance of the development team and, inherently, the company. As there are many 
-fields in a ticket, the number of unanswered questions is rather large: do stack traces have an influence on the quality
+fields in a ticket, there are numerous unanswered questions: do stack traces have an influence on the quality
 of a ticket? What about attachments and whether a screenshot is more helpful than a snippet of code? Does a negative sentiment
@@
 During the analysis part, we investigate several variables in correlation with \emph{time-to-complete}, 
-which we define as the \emph{metric of quality} (\emph{time-to-complete} represents the period of time between the creation 
-and the closing of a ticket). There are multiple novel aspects brought by our study, among which is the fact that it is one of 
-the very few studies that have tackled this issue using a quantitative rather than a qualitative approach (with a very 
-large number of tickets analysed) and also that it uses state-of-the-art sentiment \cite{wilson2005recognizing} as well as 
-grammar correctness analysis techniques \cite{wilson2005recognizing}. We believe that our results are valuable 
-contributions to the research community and the database produced after the analysis can help further studies with 
-analyzed and well-tested data.
+which we define as the \emph{metric of quality}. \emph{time-to-complete} represents the period of time between the creation 
+and the closing of a ticket; more specifically, the creation of the ticket is marked when the status of the ticket is set to 
+\emph{Open} and the closing of a ticket is considered when the ticket status is set to \emph{Closed} (or some similar status, 
+such as \emph{Fixed}, \emph{Resolved}). \emph{Time-To-Complete} is our dependent variable, and as independent variables 
+(i.e. variables controlled in order to test the effects on the dependent variable) we have set a number of ticket fields.
 
-\section{Related Work}
+This study brings several contributions to the research community:
+\begin{itemize}
+  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000) spanning
+  across a variety of projects (i.e. 21 projects);
+  \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
+  \item it is, to our knowledge, the first study to conduct sentiment and grammar correctness analyses on software tickets.
+\end{itemize}
 
-\section{Building the Data Set}
+In Section \ref{related_work} we iterate over state-of-the art studies in the field and then continue with 
+Section \ref{building} where we discuss how the ticket data set was collected and analysed. We continue with describing 
+the data set (Section \ref{characterising}) where we provide insights into various aspects of the data (e.g. size of database,
+number of tickets with attachments) and then discuss about correlations between the variables (Section \ref{correlations}).
+Finally, we provide future research directions in Section \ref{future_work} and present our conclusions in Section \ref{conclusions}.
+
+\section{Related Work}\label{related_work}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{images/flow.pdf}
+\end{center}
+\caption{\label{fig-eg}Application flow of the Go tool.}
+\end{figure*}
+
+\section{Building the Data Set}\label{building}
 The first step towards building the data set was to create a tool that was able to execute all the commands that we required:
@@
 analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
-its corresponding field in the ticket struct and subsequently stored back in the database. We chose this approach because 
+its corresponding field in the ticket struct and subsequently is stored back in the database. We chose this approach because 
 we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
@@
 
-\section{Characterising the Data Set}
+Afterwards, we have created two extra commands for automatically generating plots (i.e. scatter plots and bar charts) and 
+running statistical tests on the collected data.
 
-\section{Correlations}
+For plotting the data, we first connect again to the Bolt database instance and then filter out only the issues that have 
+the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance). Afterwards,
+we either save scatter plots or bar charts to disk.
+
+Also, in order to validate our findings, the statistics command fetches all the data from the database and
+
+\section{Characterising the Data Set}\label{characterising}
+
+\section{Correlations}\label{correlations}
 
@@
 
-\section{Future Work}
+\section{Future Work}\label{future_work}
 
-\section{Conclusions}
+\section{Conclusions}\label{conclusions}
 

### 2018-04-18 paper/paper.tex
Add to characterising section inside the paper

@@
 implemented into the system) and bug reports (i.e. issue encountered by an end user or
-discovered by a developer in the codebase). Regardless of the type of ticket, they provide
-various types of information that can be filled in by the reporter, including:
-  \begin{itemize}
-    \item summary - short description of the feature to be implemented/encountered bug;
-    \item description - longer textual field which goes into more detail regarding the ticket;
-    it can include various types of information, such as stack traces or steps to reproduce a bug;
-    \item attachments - screenshots, snippets of code or configuration files that might help
-    close the ticket faster;
-    \item comments - each ticket can have any number of comments where the people interested in 
-    it can talk about what might have caused the bug, how to fix it etc.
-  \end{itemize}
+discovered by a developer in the codebase). Regardless of the type of ticket, they possess
+various information that can be filled in by the reporter (i.e. person who created the ticket; 
+can be both an end user or a developer in the team), providing the developers
+a detailed view of what is requested or what went wrong.
 
-Even though tickets provide such comprehensive information regarding a specific task, studies have shown 
+Even though tickets provide such comprehensive data regarding a specific task, studies have shown 
 that fixing bugs is one of the most common tasks performed by developers \cite{latoza2006maintaining}. One of
@@
 that would improve the overall performance of the development team and, inherently, the company. As there are many 
-fields in a ticket, there are numerous unanswered questions: do stack traces have an influence on the quality
-of a ticket? What about attachments and whether a screenshot is more helpful than a snippet of code? Does a negative sentiment
-drawn from comments increase or decrease the time taken to solve a bug? How does grammar correctness influence the 
-communication friction?
+fields in a ticket, there are numerous unanswered questions, such as whether stack traces have an influence on the quality
+of a ticket?
 
@@
 
-Also, in order to validate our findings, the statistics command fetches all the data from the database and
+Also, in order to validate our findings, the statistics command fetches all the data from the database and runs two types of 
+tests: Welch's T Test \cite{welch1947generalization} for analysing categorical data (e.g. has/does not have attachments)
+and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. how do different 
+grammar correctness scores change \emph{Time-To-Complete}).
 
 \section{Characterising the Data Set}\label{characterising}
+
+The data that we collected is stored, as previously mentioned, in a Bolt database instance which is around 6 GB in size. 
+All tickets are stored as key-value pairs, where the key is the ticket's unique ID (e.g. KAFKA-100) and the value is the 
+JSON encoded representation of the ticket. The tickets stored have the following fields available for investigation:
+\begin{itemize}
+  \item attachments - files or images attached to tickets;
+  \item summary - short description of the ticket;
+  \item description - more detailed information regarding what is requested or what bug was encountered;
+  \item time estimate - estimated number of hours to complete the task (set by triagers or developers);
+  \item time spent - time period between opening the ticket and a specific point in time;
+  \item created timestamp;
+  \item issue status - jira specific statuses, including Open, Closed, Awaiting Review, Patch Submitted;
+  \item due date - optional deadline for when the ticket should get closed;
+  \item comments - discussion around the ticket conducted by developers, end users, triagers;
+  \item priority - it can range from low priority (minor) to critical/blocker;
+  \item issue type - specific Jira field that specifies whether the ticket is either a bug, a feature request or a general task.
+\end{itemize}
+
+There are other fields that can be configured inside Jira, including custom fields, but we did not collect them as they would not 
+have been helpful in conducting the analysis. However, in addition to the fields we saved, we also store grammar correctness scores 
+(i.e. number of grammar mistakes identified in summary, description and comments), sentiment scores (i.e. sentiment drawn from summary 
+and description), whether they have steps to reproduce, if stack traces are present and number of words in comments, summary and description. 
+Even though all of them, apart from grammar and sentiment scores, can be computed locally, we store them because of performance issues
+due to the very large size of the database.
 

### 2018-04-18 paper/paper.tex
Include all images in the dissertation
Add to characterising the data set section

@@
 \author{Andrei-Mihai Nicolae}
-\matricnum{2147392}
+\matricnum{21473292}
 
@@
 In this research paper, we present and discuss our findings after running a quantitative data analysis 
-on over 300,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
+on over 3200,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
 with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
@@
 
-During the analysis part, we investigate several variables in correlation with \emph{time-to-complete}, 
-which we define as the \emph{metric of quality}. \emph{time-to-complete} represents the period of time between the creation 
+During the analysis part, we investigate several variables in correlation with \emph{Time-To-Close}, 
+which we define as the \emph{metric of quality}. \emph{Time-To-Close} represents the period of time between the creation 
 and the closing of a ticket; more specifically, the creation of the ticket is marked when the status of the ticket is set to 
 \emph{Open} and the closing of a ticket is considered when the ticket status is set to \emph{Closed} (or some similar status, 
-such as \emph{Fixed}, \emph{Resolved}). \emph{Time-To-Complete} is our dependent variable, and as independent variables 
+such as \emph{Fixed}, \emph{Resolved}). \emph{Time-To-Close} is our dependent variable, and as independent variables 
 (i.e. variables controlled in order to test the effects on the dependent variable) we have set a number of ticket fields.
@@
 \begin{itemize}
-  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000) spanning
+  \item it is one of the very few research projects that investigates such a large number of tickets (over 3200,000) spanning
   across a variety of projects (i.e. 21 projects);
@@
 and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. how do different 
-grammar correctness scores change \emph{Time-To-Complete}).
+grammar correctness scores change \emph{Time-To-Close}).
 
@@
 \subsection{Attachments}
+\begin{figure}
+  \begin{center}
+  \includegraphics[scale=0.2]{images/attachments.png}
+  \end{center}
+  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \end{figure}
 
 \subsection{Comments}
+\begin{figure}
+  \begin{center}
+  \includegraphics[scale=0.2]{images/comment_complexity.png}
+  \end{center}
+  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \end{figure}
 
 \subsection{Summary and Description}
+\begin{figure}
+  \begin{center}
+  \includegraphics[scale=0.2]{images/fields_complexity.png}
+  \end{center}
+  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \end{figure}
 
 \subsection{Grammar Correctness}
+\begin{figure}
+  \begin{center}
+  \includegraphics[scale=0.2]{images/grammar_correctness.png}
+  \end{center}
+  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \end{figure}
 
-\subsection{Sentiment Analysis}
+\subsection{Sentiment Scores}
+\begin{figure}
+  \begin{center}
+  \includegraphics[scale=0.2]{images/sentiment_analysis.png}
+  \end{center}
+  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \end{figure}
 
 \subsection{Steps to Reproduce}
+\begin{figure}
+  \begin{center}
+  \includegraphics[scale=0.2]{images/steps_to_reproduce.png}
+  \end{center}
+  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \end{figure}
 
 \subsection{Stack Traces}
+\begin{figure}
+  \begin{center}
+  \includegraphics[scale=0.2]{images/stack_traces.png}
+  \end{center}
+  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \end{figure}
 
@@
 
-% \begin{figure*}
+% \begin{figure}
 % \begin{center}
-% \includegraphics[scale=0.3]{images/alice.pdf}
+% \includegraphics[scale=0.32]{images/alice.pdf}
 % \end{center}

### 2018-04-18 paper/paper.tex
Add significant portion of the characterising the data set section

@@
 to close for the ticket. Our results show that the presence and type of attachments,
-comments complexity (i.e. number of comments per ticket), grammar correctness scores
+comments complexity (i.e. number of comments per ticket and total number of words), 
+summary and description complexity, grammar correctness scores
 as well as the sentiment drawn from the comments can influence the quality of the ticket.
@@
 \begin{itemize}
-  \item it is one of the very few research projects that investigates such a large number of tickets (over 3200,000) spanning
-  across a variety of projects (i.e. 21 projects);
+  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000) spanning
+  across 38 different projects;
   \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
@@
 
+In total, we have collected 303,138 tickets spanned across 38 projects from the Apache Software Foundation: Impala, Eagle, Groovy, Lucene,
+Hadoop, Kafka, Apache Infrastructure project, Tika, Solr, ActiveMQ, ZooKeeper, Velocity, Tez, Storm, Stratos, CouchDB, Cassandra, 
+Beam, Aurora, Bigtop, Camel, CarbonData, Cloudstack, Flex, Flink, Ignite, HBase, Mesos, Ambari, Cordova, Avalon, Atlas, 
+Cactus, Flume, Felix, Geode, Ivy and Phoenix. These projects are using a large varieties of programming languages, ranging from Java, C, 
+Go to Python and Ruby \cite{apache_projects}. Moreover, in terms of contributors, the projects we selected range from small teams of people
+such as Tika to large numbers of developers spread across the globe, such as the people working on Kafka. We came to this final number 
+and range of tickets and projects because of a couple of reasons: 
+\begin{itemize}
+  \item the study needed as much diversity as possible in order to correctly analyse and validate the data;
+  \item these are the most important, up-to-date and contributed to Apache projects by the open source world;
+  \item Apache is one of the few companies/foundations that use Jira exclusively for their projects and it is public (they do 
+  provide a Bugzilla alternative, but it is rarely updated compared to Jira).
+\end{itemize}
+
+More specifically, we computed the following numbers for the tickets we collected:
+\begin{itemize}
+  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
+  fetched them from the Jira instance;
+  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
+  \item 103,397 tickets have attachments which we split in the following categories:
+    \begin{itemize}
+      \item 4,082 have code attachments (e.g. Go, Java, Python);
+      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
+      \item 164 have video attachments (e.g. mkv, avi, mp4);
+      \item 13,990 have text attachments (e.g. txt, md, doc(x));
+      \item 918 have config attachments (e.g. json, xml, yml);
+      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
+      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
+      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
+    \end{itemize}
+  \item 270,907 tickets have comments;
+  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
+  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
+  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
+  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
+  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
+  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
+  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
+  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs;
+\end{itemize}
+
 \section{Correlations}\label{correlations}
@@
   \begin{center}
-  \includegraphics[scale=0.2]{images/attachments.png}
+  \includegraphics[scale=0.25]{images/attachments.png}
   \end{center}
-  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \caption{\label{attachments}Application flow of the Go tool.}
   \end{figure}
@@
   \begin{center}
-  \includegraphics[scale=0.2]{images/comment_complexity.png}
+  \includegraphics[scale=0.25]{images/comment_complexity.png}
   \end{center}
-  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \caption{\label{comments}Application flow of the Go tool.}
   \end{figure}
@@
   \begin{center}
-  \includegraphics[scale=0.2]{images/fields_complexity.png}
+  \includegraphics[scale=0.25]{images/fields_complexity.png}
   \end{center}
-  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \caption{\label{fields}Application flow of the Go tool.}
   \end{figure}
@@
   \begin{center}
-  \includegraphics[scale=0.2]{images/grammar_correctness.png}
+  \includegraphics[scale=0.25]{images/grammar_correctness.png}
   \end{center}
-  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \caption{\label{grammar}Application flow of the Go tool.}
   \end{figure}
@@
   \begin{center}
-  \includegraphics[scale=0.2]{images/sentiment_analysis.png}
+  \includegraphics[scale=0.25]{images/sentiment_analysis.png}
   \end{center}
-  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \caption{\label{sentiment}Application flow of the Go tool.}
   \end{figure}
@@
   \begin{center}
-  \includegraphics[scale=0.2]{images/steps_to_reproduce.png}
+  \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
   \end{center}
-  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \caption{\label{steps}Application flow of the Go tool.}
   \end{figure}
@@
   \begin{center}
-  \includegraphics[scale=0.2]{images/stack_traces.png}
+  \includegraphics[scale=0.25]{images/stack_traces.png}
   \end{center}
-  \caption{\label{fig-eg}Application flow of the Go tool.}
+  \caption{\label{stack_traces}Application flow of the Go tool.}
   \end{figure}

### 2018-04-18 paper/paper.tex
Add new references and complete related work section

@@
 
+In order to provide answers to what factors influence quality in a software ticket, we answer the following seven research 
+questions in this paper (Section \ref{correlations}):
+
 This study brings several contributions to the research community:
@@
 \section{Related Work}\label{related_work}
+
+The study of Bettenburg et. al \cite{bettenburg2008makes} showed what 
+makes for a valuable bug report through qualitative analysis. 
+After conducting interviews with over 450 developers, one of the main factors
+behind a quality ticket is grammar correctness in summary and description. Another
+aspect which was flagged as helpful by the interviewees was the presence of stack 
+traces and steps to reproduce in tickets. A further contribution brought by the
+authors to the community is the creation of a tool called Cuezilla which is able 
+to automatically predict the quality of a bug report with an accuracy of around 40\%.
+
+Strengthening the argument that readability matters considerably in bug report 
+quality is the work of Hooimeijer et. al \cite{hooimeijer2007modeling}. They ran an analysis over
+27000 bug reports from the Mozilla Firefox project, looking at self-reported 
+severity, readability, daily load, submitter reputation and changes over time. 
+After running the evaluation, they not only found out about the importance of
+readability in bug reports, but also that attachment and comment counts are 
+valuable for faster triaging and that patch count, for example, does not
+contribute in the same manner as the previous two.
+
+Another research that agrees that stack traces are helpful in solving bug
+reports faster is the one performed by Schroter et. al \cite{schroter2010stack}. They conducted
+the whole experiment on the Eclipse project. They first extracted the stack
+traces using the infoZilla tool(\cite{bettenburg2008extracting}), followed by
+linking the stack traces to changes in the source code (change logs) by mining
+the version repository of the Eclipse project. The results showed that 
+around 60\% of the bugs that contained stack traces in their reports were fixed
+in one of the methods in the frame, with 40\% being fixed in exactly the first
+stack frame.
+
+Other interesting findings regarding the quality of a software project's tickets
+are the ones elicited in \cite{bettenburg2008duplicate}. The authors examined
+whether duplicate bug reports are actually harmful to a project or they add 
+quality. They collected big amount of data from the Eclipse project and ran
+various kind of textual and statistical analysis on the data to find answers.
+They reached the conclusion that bug duplicates contain information that is not
+present in the master reports. This additional data can be helpful for developers
+and it can also aid automated triaging techniques.
+
+Bettenburg et. al \cite{bettenburg2012using} present in their work an application
+called infoZilla. This tool can
+parse bug reports and correctly extract stack traces, patches and source code. 
+When evaluated on over 150,000 bug reports, it proved to have a very high rate of over 97\% accuracy.
+We applied some of the techniques shown in the study and successfully managed to 
+retrieve stack traces as well with a great accuracy.
+
+One other type of information that could be extracted and used for valuable
+purposes is the summary of a bug report, as shown in the work of 
+Rastkar et. al \cite{rastkar2010summarizing}. The authors wanted to determine if bug reports
+could be summarized effectively and automatically so that developers would
+need only analyze summaries instead of full tickets. Firstly, they asked
+university students to volunteer to annotate the bug reports collected from
+various open sources projects (i.e. Eclipse, Mozilla, Gnome, KDE) by writing
+a summary of maximum 250 words in their own sentences. These human-produced 
+annotations were then used by algorithms to learn how to effectively summarize a 
+bug report.  Afterwards, the authors asked the end users of these bug reports, the 
+software developers, to rate the summaries against the original bug reports.
+They eventually learned that existing conversation-based extractive summary
+generators trained on bug reports produce the best results.
+
+We tried to apply the technique presented in the work of Fischer et. al \cite{fischer2003analyzing},
+where they present a way to track specific version controlled branches from information
+in software tickets.  They managed to successfully visualize the tracked features and illustrate 
+their non apparent dependencies which can prove very useful in projects with a large number of
+components.
+
+The work of Just et. al \cite{just2008towards} examines a rather different aspect
+of quality in tickets - they are investigating the quality of the underlying issue 
+tracking systems instead. 
+The authors ran a survey on 175 developers from Eclipse, Apache and Mozilla
+Then, they applied a card sort in order to organize the comments into hierarchies to 
+identify common patterns. Their findings can be summarized in the following top seven
+suggestions:
+  \begin{itemize}
+    \item create differentiation between bug report difficulty levels between 
+    novices and experiences reporters;
+    \item encourage users to input as much information as possible;
+    \item add ability to merge tickets when needed;
+    \item recognise and reward valuable bug reporters;
+    \item integrate reputation into user profiles to mark experienced reporters;
+    \item to be able to easily and expressively search through tickets.
+  \end{itemize}
+
+However, bug report assignment is not the only part of bug triaging that needs
+investigation. Lamkanfi et. al \cite{lamkanfi2010predicting} show a method through which one
+can predict the severity of a reported bug (i.e. assign story points to the 
+ticket) automatically. The authors conducted their research on the Mozilla,
+Eclipse and GNOME projects and divided their method into four steps:
+  \begin{itemize}
+    \item extract and organize bug reports;
+    \item pre-process bug reports - tokenization, stop word removal and stemming;
+    \item train the classifier on multiple datasets of bug reports - 70\% 
+      training and 30\% evaluation;
+    \item apply the trained classifier on the evaluation set.
+  \end{itemize}
+The conclusions they drew from running the evaluation process were rather 
+interesting:
+  \begin{itemize}
+    \item terms such as deadlock, hand, crash, memory or segfault usually indicate
+      a severe bug; however, there are other terms that can indicate the opposite,
+      such as typos;
+    \item when analyzing the textual description they found that using simple
+      one line summaries resulted in less false positives and increased precision
+      levels;
+    \item the classifier needs a large dataset in order to predict correctly;
+    \item depending on how well a software project is componentized, one can 
+      use a predictor per component rather than an universal one.
+  \end{itemize}
 
@@
 
-Then, we split our tool into four main commands: \emph{store}, \emph{analyse}, \emph{plot} and \emph{stats}. They all 
+Throughout the entire application, we tried to apply the UNIX philosophy of creating small applications that do one thing, but 
+do it well. Therefore, we implemented clean and simple packages where we tried to use the standard library as much as possible
+so that potential contributors coming to the project would find it easy to start working directly on the code. Also, we designed 
+the tool with extensibility in mind, so that other database providers (e.g. CockroachDB) or issue tracking systems (e.g. Bugzilla) 
+could be easily implemented - this was achieved using the elegant Go interfaces.
+
+We split our tool into four main commands: \emph{store}, \emph{analyse}, \emph{plot} and \emph{stats}. They all 
 follow the flow shown in figure \ref{fig-eg} and complete the whole application cycle, in the end producing a database 
@@
 
-In the following two subsections we describe how we designed and implemented the commands mentioned above.
+In the following three subsections we describe how we designed and implemented the commands mentioned above.
 
@@
 
+The decision of choosing Bolt in favor of well tested, more traditional databases such as Postgres or MySQL came naturally when 
+we noticed that we did not need to query the database often, but rather get the whole array of tickets and manipulate them. Moreover, 
+a MongoDB or Postgres DB would have required a running server. Even though the server could have been running on the local machine, 
+Bolt instances are actually files with the extension \emph{db} saved on disk, thus it is trivial to create backups.
+
 We have interacted with the Jira Server REST API which has very good documentation written by the Atlassian team. After getting
@@
 specified to Jira exactly what set of issue fields to return and, eventually, while responses were retrieved from the instance,
-we began storing them into our Bolt DB instance. The way we chose to store them was to set the issue key (i.e. unique 
-identifier that differentiates a ticket from all others across all projects inside a Jira instance) as the key of the pair and
-the value is the whole representation of an issue (e.g. attachments, story points, priority) as a JSON encoded value. This
-helped us reduce the size of the database once we reached hundreds of thousands of tickets.
+we began storing them into our Bolt DB instance.
+
+The way we chose to store them was to set the issue key (i.e. unique identifier that differentiates a ticket from all others across all 
+projects inside a Jira instance) as the key of the pair and the value is the JSON representation of the ticket. This helped us reduce 
+the size of the database once we reached hundreds of thousands of tickets.
 
@@
 
+Another component of issues that we stored and proved to be crucial in our analysis is changelog histories together with their 
+corresponding items. They represent the whole history of a ticket and can show status transitions, story points modifications, 
+summary/description editing etc. What made them useful for our study was that we needed to see when tickets were marked closed and, 
+as Jira does not provide this in a separate field, we looped through all changelog history items and saved when the transition to 
+Closed or a similar status was made.
+
 There are other fields that can be configured inside Jira, including custom fields, but we did not collect them as they would not 
-have been helpful in conducting the analysis. However, in addition to the fields we saved, we also store grammar correctness scores 
-(i.e. number of grammar mistakes identified in summary, description and comments), sentiment scores (i.e. sentiment drawn from summary 
-and description), whether they have steps to reproduce, if stack traces are present and number of words in comments, summary and description. 
+have been helpful in conducting the analysis. However, in addition to the fields we saved, we also stored grammar correctness scores, 
+sentiment scores, whether they have steps to reproduce, if stack traces are present and number of words in comments, summary and description. 
 Even though all of them, apart from grammar and sentiment scores, can be computed locally, we store them because of performance issues
@@
   \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
-  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs;
+  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
 \end{itemize}
+
+All these numbers are also stored inside the database in a different bucket for easier access in the future. Moreover, the statistical 
+tests we ran on the tickets are saved as well in the database.
 

### 2018-04-18 paper/paper.tex
Add some todos in the paper
Include another contribution in the introduction and add research questions
Refactor

@@
 questions in this paper (Section \ref{correlations}):
+\begin{itemize}
+  \item does the presence of attachments and their type (e.g. code snippet, screenshot) influence the \emph{Time-To-Close} for 
+  a ticket?
+  \item does the presence of stack traces improve the ticket quality?
+  \item does the presence of steps to reproduce reduce the \emph{Time-To-Close}?
+  \item is there a relationship between the number of comments influence \emph{Time-To-Close}?
+  \item is there a relationship between 
+\end{itemize}
 
@@
 \begin{itemize}
-  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000) spanning
-  across 38 different projects;
+  \item an innovative tool was built for the purpose of this project, its strengths lying in its simplicity, speed and
+  extensability;
   \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
+  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000)
+  extracted from 38 different projects;
   \item it is, to our knowledge, the first study to conduct sentiment and grammar correctness analyses on software tickets.
@@
 
+%TODO: modify here
 Strengthening the argument that readability matters considerably in bug report 
@@
 
+%TODO: modify here
 Another research that agrees that stack traces are helpful in solving bug
@@
 
+%TODO: modify here
 Other interesting findings regarding the quality of a software project's tickets
@@
 
+%TODO: modify here
 One other type of information that could be extracted and used for valuable
@@
 \end{document}
-
-% \begin{table}
-% \begin{tabular}{l||c||p{2cm}}
-% \emph{Operating System} & \emph{Version} & \emph{Verdict} \\ \hline \hline
-% Ubuntu & 12.04 & Everyone's favourite Linux, unless you grew up with
-% RedHat \\ \hline
-% Slackware & xxx & Pseudo-hacker's Linux, how often do you recompile
-% your kernel? \\ \hline
-% Mac OS & 10.7 & For people with more money than sense \\ \hline
-% \end{tabular}
-% \caption{\label{tab-eg}Single column table of figures}
-% \end{table}
-
-% \begin{figure}
-% \begin{center}
-% \includegraphics[scale=0.32]{images/alice.pdf}
-% \end{center}
-% \caption{\label{fig-eg}An example figure stretching over two columns}
-% \end{figure*}

### 2018-04-18 paper/paper.tex
Add more information in the related work section

@@
 
-%TODO: modify here
-Strengthening the argument that readability matters considerably in bug report 
-quality is the work of Hooimeijer et. al \cite{hooimeijer2007modeling}. They ran an analysis over
-27000 bug reports from the Mozilla Firefox project, looking at self-reported 
-severity, readability, daily load, submitter reputation and changes over time. 
-After running the evaluation, they not only found out about the importance of
-readability in bug reports, but also that attachment and comment counts are 
-valuable for faster triaging and that patch count, for example, does not
-contribute in the same manner as the previous two.
+Another research paper that strenghtens the argument that readability is a quality 
+factor in software tickets is the one presented by Hooimeijer et. al \cite{hooimeijer2007modeling}.
+They conducted their analysis on over 25,000 bug reports from the Mozilla project, 
+investigating readability, daily load, submitter reputation, the whole changelog histories 
+and severity. They conclude that not only readability in the textual fields of a ticket
+influence the \emph{Time-To-Close}, but also that the presence of attachments and 
+the number of comments have a clear effect on the duration of triaging. On the 
+other hand, the patch count and other similar fields did not provide significant 
+value to the quality of tickets.
 
-%TODO: modify here
-Another research that agrees that stack traces are helpful in solving bug
-reports faster is the one performed by Schroter et. al \cite{schroter2010stack}. They conducted
-the whole experiment on the Eclipse project. They first extracted the stack
-traces using the infoZilla tool(\cite{bettenburg2008extracting}), followed by
-linking the stack traces to changes in the source code (change logs) by mining
-the version repository of the Eclipse project. The results showed that 
+However, there are other types on information typically included in software tickets 
+which might prove beneficial for developers and subsequently improve the ticket quality.
+One such type is stack traces and Schroter et. al \cite{schroter2010stack} analyse how 
+quickly tickets are closed when they either have stack traces included in their fields 
+(e.g. description) or not. They collected their data from the Eclipse project using 
+the InfoZilla tool proposed by Bettenburg et. al \cite{bettenburg2008extracting}.
+Then, they linked the stack traces to changes in source code by mining the Eclipse version 
+controlled repository. The results showed that 
 around 60\% of the bugs that contained stack traces in their reports were fixed
-in one of the methods in the frame, with 40\% being fixed in exactly the first
-stack frame.
+in one of the methods in the frame. Moreover, more than 40\% of the tickets having stack traces
+got fixed in the first stack frame.
 
-%TODO: modify here
 Other interesting findings regarding the quality of a software project's tickets
-are the ones elicited in \cite{bettenburg2008duplicate}. The authors examined
+are the ones elicited in the study of Bettenburg et. al \cite{bettenburg2008duplicate}. The authors examined
 whether duplicate bug reports are actually harmful to a project or they add 

### 2018-04-18 paper/paper.tex
Complete another study in the related work section

@@
 
-Other interesting findings regarding the quality of a software project's tickets
-are the ones elicited in the study of Bettenburg et. al \cite{bettenburg2008duplicate}. The authors examined
-whether duplicate bug reports are actually harmful to a project or they add 
-quality. They collected big amount of data from the Eclipse project and ran
+Software tickets can have duplicates, usually meaning that the most important fields, such 
+as summary or description, describe the same feature request or bug report. Even though 
+one might believe that they cannot bring any value to a software project, the work of 
+Bettenburg et. al \cite{bettenburg2008duplicate} shows the contrary.
+The authors collected large amounts of data from the Eclipse open source project and ran
 various kind of textual and statistical analysis on the data to find answers.
-They reached the conclusion that bug duplicates contain information that is not
-present in the master reports. This additional data can be helpful for developers
-and it can also aid automated triaging techniques.
+After the results were computed, they concluded that usually bug duplicates contain 
+information that is not present in the master report (i.e. the original report that was 
+filed). Moreover, developers also specified that they have often found value in these 
+duplicate bug reports and that they can even aid automated triaging techniques.
 
@@
 \subsection{Attachments}
+
+A Welch T Test was computed to test the difference between tickets with attachments and those 
+without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
+average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
+for tickets without attachments.
+
 \begin{figure}
@@
 
+\subsection{Steps to Reproduce}
+
+A Welch T Test was computed to test the difference between tickets with attachments and those 
+without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
+average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
+for tickets without attachments.
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
+  \end{center}
+  \caption{\label{steps}Application flow of the Go tool.}
+  \end{figure}
+
+\subsection{Stack Traces}
+
+A Welch T Test was computed to test the difference between tickets with attachments and those 
+without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
+average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
+for tickets without attachments.
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[scale=0.25]{images/stack_traces.png}
+  \end{center}
+  \caption{\label{stack_traces}Application flow of the Go tool.}
+  \end{figure}
+
 \subsection{Comments}
+
+A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
+with \emph{r} = \dots, \emph{p} = \dots.
+
 \begin{figure}
@@
 \subsection{Summary and Description}
+
+A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
+with \emph{r} = \dots, \emph{p} = \dots.
+
 \begin{figure}
@@
 \subsection{Grammar Correctness}
+
+A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
+with \emph{r} = \dots, \emph{p} = \dots.
+
 \begin{figure}
@@
 \subsection{Sentiment Scores}
+
+A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
+with \emph{r} = \dots, \emph{p} = \dots.
+
 \begin{figure}
@@
   \caption{\label{sentiment}Application flow of the Go tool.}
-  \end{figure}
-
-\subsection{Steps to Reproduce}
-\begin{figure}
-  \begin{center}
-  \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
-  \end{center}
-  \caption{\label{steps}Application flow of the Go tool.}
-  \end{figure}
-
-\subsection{Stack Traces}
-\begin{figure}
-  \begin{center}
-  \includegraphics[scale=0.25]{images/stack_traces.png}
-  \end{center}
-  \caption{\label{stack_traces}Application flow of the Go tool.}
   \end{figure}

### 2018-04-19 paper/paper.tex
Complete another paper inside the related work section

@@
 
-%TODO: modify here
-One other type of information that could be extracted and used for valuable
-purposes is the summary of a bug report, as shown in the work of 
-Rastkar et. al \cite{rastkar2010summarizing}. The authors wanted to determine if bug reports
-could be summarized effectively and automatically so that developers would
-need only analyze summaries instead of full tickets. Firstly, they asked
-university students to volunteer to annotate the bug reports collected from
-various open sources projects (i.e. Eclipse, Mozilla, Gnome, KDE) by writing
-a summary of maximum 250 words in their own sentences. These human-produced 
-annotations were then used by algorithms to learn how to effectively summarize a 
-bug report.  Afterwards, the authors asked the end users of these bug reports, the 
-software developers, to rate the summaries against the original bug reports.
-They eventually learned that existing conversation-based extractive summary
-generators trained on bug reports produce the best results.
-
-We tried to apply the technique presented in the work of Fischer et. al \cite{fischer2003analyzing},
-where they present a way to track specific version controlled branches from information
-in software tickets.  They managed to successfully visualize the tracked features and illustrate 
-their non apparent dependencies which can prove very useful in projects with a large number of
-components.
+The first information to be filled in by end users or developers on any issue tracking system
+is the summary field, which holds a small description, usually between 5 and 30 words, of 
+the request or bug being reported. In the study conducted by Rastkar et. al \cite{rastkar2010summarizing}, 
+the authors investigated whether tickets could be summarized automatically and efficiently. What 
+that implies is that developers would not be required to look at complete tickets comprised 
+of a large number of fields, but rather at a simple summary of a couple of lines 
+encapsulating the whole information. The authors selected the Mozilla, Eclipse, Gnome and KDE 
+open source projects and then they asked volunteering university students to annotate 
+the tickets in the issue tracking systems. More specifically, they had to write a summary 
+of maximum 250 words using both technical and non-technical terms, depending on their expertise. 
+Then, the study presents Machine Learning algorithms employed to parse these summaries and 
+learn how to efficiently create automated summaries for new bug reports. Afterwards, they asked 
+software developers to rate these auto-generated summaries against the original ones and 
+the conclusion was that existing conversation-based extractive summary generators used 
+for software tickets produce the best results.
 
@@
 
-However, bug report assignment is not the only part of bug triaging that needs
-investigation. Lamkanfi et. al \cite{lamkanfi2010predicting} show a method through which one
+Lamkanfi et. al \cite{lamkanfi2010predicting} show a method through which one
 can predict the severity of a reported bug (i.e. assign story points to the 

### 2018-04-19 paper/paper.tex
Add paper inside the related work section

@@
 
-Lamkanfi et. al \cite{lamkanfi2010predicting} show a method through which one
-can predict the severity of a reported bug (i.e. assign story points to the 
-ticket) automatically. The authors conducted their research on the Mozilla,
-Eclipse and GNOME projects and divided their method into four steps:
+Having discussed about various factors that can influence the quality in software tickets, 
+we also need to take into account how can we apply this knowledge to solving the issue of 
+poor design in issue tracking systems and how the ticket creation process could be improved. 
+The study conducted by Lamkanfi et. al \cite{lamkanfi2010predicting} looks at this aspect and
+shows how issue tracking systems could be extended in order to automatically generate the severity 
+of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
+GNOME and Eclipse and projects and split their approach into four steps:
   \begin{itemize}
-    \item extract and organize bug reports;
-    \item pre-process bug reports - tokenization, stop word removal and stemming;
-    \item train the classifier on multiple datasets of bug reports - 70\% 
+    \item extract and organize tickets;
+    \item pre-process tickets (i.e. tokenization, stop word removal and stemming);
+    \item train the classifier on two datasets of tickets - 70\% 
       training and 30\% evaluation;
@@
   \begin{itemize}
-    \item terms such as deadlock, hand, crash, memory or segfault usually indicate
-      a severe bug; however, there are other terms that can indicate the opposite,
-      such as typos;
+    \item terms such as segfault, deadlock, crash, hand or memory typically indicate
+      a severe bug;
     \item when analyzing the textual description they found that using simple
@@
       levels;
-    \item the classifier needs a large dataset in order to predict correctly;
-    \item depending on how well a software project is componentized, one can 
-      use a predictor per component rather than an universal one.
+    \item the classifier needs a large number of tickets in order to predict correctly;
+    \item depending on how well a software project is modularised, one can 
+      use a predictor per module rather than a universal one.
   \end{itemize}

### 2018-04-19 paper/paper.tex
Complete the related work section

@@
   \end{itemize}
+
+Another overall aspect of software tickets and issue tracking systems that could be improved through 
+determining the quality factors for tickets is automatically assigning a bug report or a feature request 
+to the most suitable developer (or team of developers). Anvik et. al \cite{anvik2011reducing}
+propose a Machine Learning technique that could automatically assign a bug report to the developer 
+with the most expertise in that specific area. Firstly, the algorithm takes as input various types of information from 
+tickets: textual description and summary, operating system used when the bug occurred, developer 
+who owns the source code, which developers have lighter workloads at that point in time etc. After the 
+tool was evaluated, the authors concluded that it can be used in production as it provides a high 
+rate of accuracy when assigning the developers, but it needs more data so that the model is trained 
+properly.
 

### 2018-04-19 paper/paper.tex
Center all the images properly and add some text inside the correlations section

@@
 
+In this section we present our results to the research questions we set to answer. We have computed charts for all 
+independent variables using either scatter plots for continuous variables (e.g. number of comments/time-to-close) 
+or bar charts for categorical variables (e.g. presence of attachments). We also computed statistical analysis for 
+all variables to test their significance and rank correlation coefficient and we will present each of them in their 
+corresponding subsection. Lastly, we also discuss possible reasons why certain correlations occured.
+
 \subsection{Attachments}
+
+\begin{figure}[ht]
+  \begin{center}
+  \includegraphics[scale=0.23]{images/attachments.png}
+  \end{center}
+  \caption{\label{attachments}Attachments analysis.}
+\end{figure}
+
+Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
+snippets written in Java to tar archives. We have analyzed all the high priority tickets
 
@@
 
-\begin{figure}
+\subsection{Steps to Reproduce}
+
+\begin{figure}[ht]
   \begin{center}
-  \includegraphics[scale=0.25]{images/attachments.png}
+    \includegraphics[scale=0.23]{images/steps_to_reproduce.png}
   \end{center}
-  \caption{\label{attachments}Application flow of the Go tool.}
+  \caption{\label{steps}Steps to reproduce analysis.}
 \end{figure}
-
-\subsection{Steps to Reproduce}
 
@@
 
-\begin{figure}
+\subsection{Stack Traces}
+
+\begin{figure}[ht]
   \begin{center}
-  \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
+    \includegraphics[scale=0.23]{images/stack_traces.png}
   \end{center}
-  \caption{\label{steps}Application flow of the Go tool.}
+  \caption{\label{stack_traces}Stack traces analysis.}
 \end{figure}
-
-\subsection{Stack Traces}
 
@@
 
-\begin{figure}
+\subsection{Comments}
+
+\begin{figure}[ht]
   \begin{center}
-  \includegraphics[scale=0.25]{images/stack_traces.png}
+    \includegraphics[scale=0.23]{images/comment_complexity.png}
   \end{center}
-  \caption{\label{stack_traces}Application flow of the Go tool.}
+  \caption{\label{comments}Comments complexity analysis.}
 \end{figure}
-
-\subsection{Comments}
 
@@
 
-\begin{figure}
+\subsection{Summary and Description}
+
+\begin{figure}[ht]
   \begin{center}
-  \includegraphics[scale=0.25]{images/comment_complexity.png}
+    \includegraphics[scale=0.23]{images/fields_complexity.png}
   \end{center}
-  \caption{\label{comments}Application flow of the Go tool.}
+  \caption{\label{fields}Fields complexity analysis.}
 \end{figure}
-
-\subsection{Summary and Description}
 
@@
 
-\begin{figure}
+\subsection{Grammar Correctness}
+
+\begin{figure}[ht]
   \begin{center}
-  \includegraphics[scale=0.25]{images/fields_complexity.png}
+    \includegraphics[scale=0.23]{images/grammar_correctness.png}
   \end{center}
-  \caption{\label{fields}Application flow of the Go tool.}
+  \caption{\label{grammar}Grammar correctness score analysis.}
 \end{figure}
-
-\subsection{Grammar Correctness}
 
@@
 
-\begin{figure}
+\subsection{Sentiment Scores}
+
+\begin{figure}[ht]
   \begin{center}
-  \includegraphics[scale=0.25]{images/grammar_correctness.png}
+    \includegraphics[scale=0.23]{images/sentiment_analysis.png}
   \end{center}
-  \caption{\label{grammar}Application flow of the Go tool.}
+  \caption{\label{sentiment}Sentiment score analysis.}
 \end{figure}
-
-\subsection{Sentiment Scores}
 
@@
 with \emph{r} = \dots, \emph{p} = \dots.
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[scale=0.25]{images/sentiment_analysis.png}
-  \end{center}
-  \caption{\label{sentiment}Application flow of the Go tool.}
-  \end{figure}
 

### 2018-04-19 paper/paper.tex
Add attachments correlations subsection to the paper

@@
 Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
-snippets written in Java to tar archives. We have analyzed all the high priority tickets
+snippets written in Java to tar archives. We have analyzed all tickets that were both of high priority tickets and
+were marked as Closed by the time we collected the data. Then we split all these tickets into two main categories: 
+with attachments and without attachments. Furthermore, the tickets that were marked as having attachments were split 
+into the categories specified in Section \ref{characterising}.
+
+Using the plot package in our Go tool, we automatically generated the bar chart shown in Figure \ref{attachments}. 
+As it can be seen, various types of attachments can produce completely different \emph{times-to-close}. For 
+tickets with archive we can see the longest time-to-close mean while tickets having text attachments are at 
+the other end of the spectrum. The smallest mean is for other attachments, which is represented by any file 
+that does not have an extension specified in one of the other categories.
+
+We assume that image attachments are screenshots attached to the ticket in order to help developers see and 
+subsequently reproduce the bug. Thus, we can clearly see that the difference between the means of time-to-close 
+for tickets without attachments and tickets with screenshots is significantly in favor of the latter. This can 
+indicate that developers indeed find screenshots helpful in solving the ticket faster.
+
+Another insightful result is the fact that having text, config and spreadsheet attachments significantly 
+reduces the time-to-close for the ticket. This can imply that developers find value in various steps to reproduce, 
+config values used by users when the bug encountered or data in a spreadsheet format (e.g. csv) that can be 
+found in such files and helps them lower the time-to-close for the ticket.
+
+On the other hand, having no attachments does not necessarily mean that the ticket will get closed after 
+a longer period of time. As it can be seen in the figure, the mean time-to-close value for tickets without 
+attachments is somewhat neutral in the entire data set.
 
 A Welch T Test was computed to test the difference between tickets with attachments and those 
-without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
-average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
+without attachments. The analysis revealed significant difference with $p > 0.01$ with an
+average of $1380.551$ hours for tickets with attachments and an average of $3180.882$ hours
 for tickets without attachments.
+
+Thus, our analysis shows that having attachments in most formats, ranging from markdown files to PNG screenshots 
+and snippets of code, can help developers solve the tickets faster. We believe that the solution of making attachments
+provide the most value to the software project would be if issue tracking systems would make explicit to the reporters 
+that uploading a screenshot or a code snippet can help reduce the time-to-close for the ticket.
 
@@
 
-A Welch T Test was computed to test the difference between tickets with attachments and those 
-without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
-average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
-for tickets without attachments.
+A Welch T Test was computed to test the difference between tickets with attachments (i.e. all categories 
+shown in the graph and those without attachments. The analysis revealed significant difference with 
+\emph{p} < 0.01 with an average of \emph{X <change this>} for tickets with attachments and an average of 
+\emph{Y <change this>} for tickets without attachments.
 

### 2018-04-19 paper/paper.tex
Add subsection on steps to reproduce correlation

@@
 
-A Welch T Test was computed to test the difference between tickets with attachments (i.e. all categories 
-shown in the graph and those without attachments. The analysis revealed significant difference with 
-\emph{p} < 0.01 with an average of \emph{X <change this>} for tickets with attachments and an average of 
-\emph{Y <change this>} for tickets without attachments.
+Steps to reproduce are a means of specifying to the developers what actions they need to undergo in order 
+to reproduce a certain bug. They can take various forms, but as Jira uses a wiki style markdown format for 
+their description and comments fields, they can be inserted as a bullet point list which can be easily 
+extracted with a regular expression.
+
+Figure \ref{steps} shows the bar chart representing all closed, high priority tickets with or without steps 
+to reproduce in either the description field or in any of the comments.
+
+As it can be shown in the figure, having steps to reproduce can significantly reduce the time-to-close 
+for the ticket. Even though the data collected does not have such many tickets with steps to reproduce 
+(39,988 compared to the total number of 238,286 closed tickets), it is still a valuable finding which shows 
+that steps to reproduce are indeed a quality factor for software tickets.
+
+What we can infer from this result is that steps to reproduce reduce the communication friction between 
+the reporters and the developers - in the case of a bug which is harder to reproduce (e.g. maybe the 
+bug occurs only on Linux and the developer is running MacOS, but the reporter did not specify his/her 
+operating system in the ticket), the developer might need to contact the reported either directly or 
+through commenting on the issue. What this implies is waiting time until the reporter comes back on the 
+issue tracking system or sees the notification that he/she received a new message, which subsequently makes 
+the ticket remain open for a longer period of time.
+
+A Welch T Test was computed to test the difference between tickets with steps to reproduce 
+and those without steps to reproduce. The analysis revealed significant difference with 
+$p < 0.01$ with an average of $1596.714$ for tickets with steps to reproduce and an average of 
+$2609.142$ for tickets without steps to reproduce.
+
+Thus, the answer to our research question is that the presence of steps to reproduce in tickets 
+has a positive influence on the time-to-close. One solution that we propose for maximizing their benefit 
+is that issue tracking systems should include hints on the ticket creation form specifying that 
+steps to reproduce should be included as developers would be able to fix the bug faster. Moreover, 
+issue tracking systems could also automatically add a new system field (like summary or description) 
+for any project created and the project maintainers or administrators could make them mandatory for 
+when a ticket is created by reporters.
 

### 2018-04-19 paper/paper.tex
Add acknowledgements section on paper

@@
 
-A Welch T Test was computed to test the difference between tickets with attachments and those 
-without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
-average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
-for tickets without attachments.
+Stack traces are active stack frames at a certain point in time while the program is executing. 
+Many programming languages provide stack traces through their standard libraries, but the most 
+popular proponents are Java and C\#. As Java is the main programming language used throughout 
+the Apache Software Foundation projects (231 projects \cite{apache_projects}), many of the projects 
+we collected (22) are also written in Java, thus we had a considerable chunk of data to analyze.
+
+For this analysis, we only looked at tickets of high priority, closed and the project they correspond 
+is written in Java. We then ran a complex regular expression derived from the works of Bettenburg et. al 
+\cite{bettenburg2012using} and Moreno et. al \cite{moreno2014use} and collected all the tickets that have 
+stack traces. In the end, we got a total number of 256 tickets that had at least an exception stack trace 
+attached in either summary, description or any of the comments.
+
+As shown in Figure \ref{stack_traces}, we can see that the presence of exception stack traces can 
+reduce the time-to-close of a ticket in orders of magnitude. This could imply that stack traces help 
+developers working on the project localise the code that is running exceptions
+
+We computed a Welch T Test to test the difference between tickets with stack traces and tickets that 
+do not have stack traces. The analysis revealed significant difference with $p < 0.01$ with an
+average of $1475.074$ for tickets with stack traces and an average of $2441.877$
+for tickets without them.
 
@@
 
+The first extension to the Go tool we created would be to add support for Bugzilla as an issue tracking system
+
 \section{Conclusions}\label{conclusions}
@@
 {\bf Acknowledgments.}
-Tim, my parents, Corina.
+I would first like to thank Dr. Storer for the amazing work he has put in helping me go through with finishing 
+this project. I would definitely not have been able to achieve what we've achieved with any other supervisor, so 
+thank you, Tim, for all the support, kindness and advice you have given me throughout this academic year. I would 
+also like to thank you for being the lecturer who has taught me the most throughout all my years at the university
+and whose advice and ideas I have applied at all my work places and my personal projects.
+The next huge thank you would have to go to my parents, the most amazing family in the world! Without them I would 
+not be here and I wouldn't have had anything of what I have now, both personally and professionally. 
+I will always treasure the unconditional support you have always offered me! Thank you for being my parents, Mom and Dad!
+And last but not least, I want to thank my partner in \"crime\" and in life, Corina! Without her, I would not be who I 
+am today. You have been with me through thick and thin, in both bad moments (such as the endless nights working 
+on ticket statistics) and best moments in my life! Thank you for everything! I will always love you!
 

### 2018-04-19 paper/paper.tex
Complete future work section and also add to the conclusions section

@@
 
-The first extension to the Go tool we created would be to add support for Bugzilla as an issue tracking system
+The first extension to the Go tool we created would be to add support for Bugzilla. We already achieved this 
+when we were first prototyping the application, but we decided to proceed exclusively with Jira mainly because 
+the APIs proved to be more reliable and also versatile in terms of what data you could collect. Another 
+reason was that we were time retricted, thus we wanted to have first a well tested and stable solution for Jira and 
+only after add support for other issue tracking systems. However, we already prepared for other potential systems by 
+adding interfaces for tickets and REST clients, making Bugzilla, Manuscript, YouTrack or any 
+other issue tracking system straightforward to add to the application.
+
+Another extension to the app could be adding the possibility of selecting what database provider to use 
+for storing tickets. As we previously mentioned, we currently provide only Bolt DB support, but adding others is 
+again straightforward, mainly because we already store tickets as arrays of bytes representing the JSON encoded 
+value. Thus, if we add a new database provider, if they allow us to store items as raw bytes (which most DBs already 
+do), then the necessary code changes would be minimal.
+
+One other improvement to the application could be adding more robust support for statistical analysis. At the moment, 
+our tool uses our own custom types and functions for generating Welch T Test and Spearman R Test results, and even if 
+it produces the expected \emph{p} and \emph{r coefficient} values, end users of the application might want to 
+analyse even more possible correlations. As the Go community lacks native libraries to perform statistical tests, 
+the users of our tool might miss the simplicity of running such tests in R. A solution can be to integrate the 
+Roger library \cite{r_stats} inside the stats package, which basically allows any Go application to communicate with 
+R via TCP.
+
+There is also room for future work in terms of the data collected. Even though the database we collected 
+is large, there is never enough tickets to analyse. Thus, the store command of the tool could be run against 
+other Jira instances apart from Apache's and collect tickets from other projects, thus improving the diversity 
+and the total number of tickets to be analysed. As we did not have access to any cluster or virtual machines in 
+the cloud, we ran all our analyses on local machines (laptops) and it could still take well over two hours to complete 
+with over 10 GB of RAM and 70\% CPU in usage.
+
+Furthermore, the project could greatly benefit from having access to closed source repositories in addition to the 
+open source ones. Most closed source projects have much more structured planning, tracking and management activities - as 
+Crowston et. al \cite{crowston2012free} present in their study, open source projects lack organized coordination which,
+in the context of our study, means that people do not invest much effort into properly creating tickets in issue tracking 
+systems, triaging efficiently, planning the work and tracking it. On the other hand, closed source projects follow 
+more strict guidelines: standard working hours (would make tracking and linking the source code changes to tickets easier), 
+adding story points (i.e. adding estimated difficulty or time to complete) and properly planning tickets before work 
+starts on the task, tickets properly distributed to developers based on availability and expertise etc. These benefits 
+of closed source projects would prove helpful for our analysis.
+
+Another aspect that could be improved is having access to funds in order to buy Google Cloud Platform credits. This 
+would be required to use the Natural Language Processing APIs on large amounts of data. We used the credits provided 
+in the free trial but quickly ran out completely after only 160,000 tickets. Also, credits on Microsoft Azure would 
+prove useful as their Spell Check API is the most efficient at the moment.
+
+A major future work candidate is availability of a technique to calculate the difficulty of a ticket based on the information
+inside it. Unfortunately, at the moment, the research community has not come up with such an approach. 
+Vijayakumar et. al \cite{vijayakumar2014much} proposed a method of predicting how much effort is required for fixing 
+a bug, but after running it on our data, it did not prove successful. After such a technique becomes available, we could 
+incorporate it inside our tool and group the tickets compared in all analysis types based on their difficulty in order to 
+have better results.
 
 \section{Conclusions}\label{conclusions}
+
+Software tickets are a vital part of every software project's lifecycle. Even though there might be other means
+of planning, managing and tracking work for a software team, issue tracking systems are deployed in virtually any company
+that provides a computer application or service.
+
+Deriving a quality score only from textual information and other non-structured data such as images is not trivial. 
+However, in this study we managed to answer all seven research questions and find factors that can posittively or 
+negatively affect the quality of a ticket.
+
+In this study, we have answered all the research 
+questions we set to answer and successfully proven that all of our results are statistically significant.
 
@@
 and whose advice and ideas I have applied at all my work places and my personal projects.
+
 The next huge thank you would have to go to my parents, the most amazing family in the world! Without them I would 
@@
 I will always treasure the unconditional support you have always offered me! Thank you for being my parents, Mom and Dad!
+
 And last but not least, I want to thank my partner in \"crime\" and in life, Corina! Without her, I would not be who I 

### 2018-04-19 paper/paper.tex
Finish conclusions section

@@
 Deriving a quality score only from textual information and other non-structured data such as images is not trivial. 
-However, in this study we managed to answer all seven research questions and find factors that can posittively or 
-negatively affect the quality of a ticket.
+However, in this study we managed to create an application that can automatically fetch and store tickets from any 
+Jira instance, analyse them and compute statistical tests and graphs.
 
-In this study, we have answered all the research 
-questions we set to answer and successfully proven that all of our results are statistically significant.
+We manager to answer all seven research questions and find factors that can posittively or 
+negatively affect the quality of a ticket. All of our results are statistically significant and we can summarise 
+them as follows:
+\begin{itemize}
+  \item the presence of steps to reproduce increases the quality of a ticket;
+  \item the presence of stack traces increases the quality of a ticket;
+  \item the presence of attachments increases the quality of a ticket - more specifically tickets with screenshots, 
+  config files or text files have lower times-to-complete than tickets without attachments;
+  \item higher numbers of grammar errors impply lower quality scores for a ticket;
+  \item higher sentiment scores imply higher quality scores for a ticket;
+  \item higher numbers of words in comments imply lower quality scores for a ticket;
+  \item higher number of words in description and summary imply lower quality scores for a ticket.
+\end{itemize}
+
+We intend to continue work on the project and implement the points we have listed in Section \ref{future_work}. We believe
+that by open sourcing the application and making the data publicly available, we can provide a valuable starting point 
+for other studies investigating this particular field of software engineering.
 

### 2018-04-19 paper/paper.tex
Small fixes to building the data set section
Start adding info regarding API rate limits for GCP and Microsoft Azure

@@
 the tool with extensibility in mind, so that other database providers (e.g. CockroachDB) or issue tracking systems (e.g. Bugzilla) 
-could be easily implemented - this was achieved using the elegant Go interfaces.
+could be easily implemented - this was achieved using the elegant Go interfaces and the idea of composition.
 
@@
   sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
-  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 is completely negative, 1 is completely 
-  positive).
+  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
+  positive);
 \end{itemize}
+
+We hit several issues when working with Google Cloud Platform and Bing Spell
 

### 2018-04-19 paper/paper.tex
Add some other information to the building the data set section of the report

@@
 
-\section{Introduction}
+\section{Introduction}\label{intro}
 
@@
 Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
-fetches all the issues in the database. Then, it runs in parallel the \emph{seven types of analysis}:
+fetches all the issues in the database. The next step is to filter out the tickets based on the following criteria:
+\begin{itemize}
+  \item tickets are \emph{High Priority} - the ticket status was marked either Blocker, Critical, Major or High;
+  \item tickets were closed and had a maximum \emph{Time-To-Close} value of 27,000 hours (roughly 3 years) (we added the 
+  higher bound as well in order to eliminate outliers produced by wrong data retrieved by Jira);
+  \item remove outliers for all categories - some fields for a small number of tickets that had wrong values (e.g. one ticket
+  had over 270,000 comments) introduced by the team behind the project and we needed to exclude them so that the analysis 
+  produced correct results.
+\end{itemize}
+
+Then, it runs in parallel the \emph{seven types of analysis} for answering the research questions outlied in Section \ref{intro}, 
+each in its own separate goroutine in order to speed up the process:
 \begin{itemize}
@@
   influence the quality of a ticket;
-  \item \emph{stack traces} - runs complex regex for detecting stack traces in either summary, description or comments 
-  and verifies whether their presence influence Time-To-Close for the ticket;
+  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
+  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
+  written in Java as it is the most popular proponent built-in of stack traces;
   \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
-  having many words or comments decreases or increases Time-To-Close for the ticket;
-  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description;
+  the number of words in comments has an impact on the Time-To-Close for the ticket;
+  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
   \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
@@
 
-We hit several issues when working with Google Cloud Platform and Bing Spell
+We needed to be extra cautious when working with Google Cloud Platform and Bing Spell Check APIs, especially 
+regarding rate limiting. Google's NLP APIs have a maximum rate of 10 requests per second, while Microsoft APIs 
+have a maximum rate of  100 requests per second, thus we needed to conform to their guidelines and restrict our 
+application to send more than allowed, otherwise our IP addresses could have been blacklisted. We also did not want 
+to exceed our free trial credits, therefore we calculated in advance how many requests we had available and computed 
+scores only for those tickets.
 
-Implementation wise, the application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
+The application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
 but heavy on resource utilization) or slices them into smaller arrays to get processed afterwards (harder to parse as it 
@@
 analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
-its corresponding field in the ticket struct and subsequently is stored back in the database. We chose this approach because 
+its corresponding field in the ticket struct and is subsequently stored back in the database. We chose this approach because 
 we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
-already available there. Moreover, for external analysis such as hitting Google Cloud Platform APIs, there are costs for 
-running the analysis, thus in this way we drastically reduce overall costs for the project.
+already available there. Moreover, for analysis depending on third party services such as the Google Cloud Platform 
+Natural Processing Language API, we would incur costs, thus having everything saved in the database and running the 
+analysis only if the value has not been already computed allowed us to investigate the tickets without exceeding the 
+free trial credits.
 

### 2018-04-19 paper/paper.tex
Complete plot and statistical tests subsection

@@
 For plotting the data, we first connect again to the Bolt database instance and then filter out only the issues that have 
-the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance). Afterwards,
-we either save scatter plots or bar charts to disk.
+the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance). 
+In order to compute correct results, we run the same checks on issues as the ones listed in the analyse command (e.g. plot 
+only tickets of high priority). Afterwards, we either save scatter plots or bar charts to disk presenting correlations 
+between all the variables we tested.
+
+In terms of technology used for plotting the data, we have used a library called go-chart \cite{go-chart} created by 
+Will Charczuk. It is an extensible library with a focus on extensability - it does not provide the end user a large number 
+of default options, but rather let him/her extend their graphs as much as it is needed (e.g. add specific labels for axes, 
+plot a secondary Y axis).
 
@@
 and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. how do different 
-grammar correctness scores change \emph{Time-To-Close}).
+grammar correctness scores change \emph{Time-To-Close}). For computing Spearman R Tests we made use of a simple 
+statistics library created by Damian Gryski called onlinestats \cite{onlinestats}, while for Welch T Tests we created our 
+own custom types and functions.
+
+They have both been created with extensability in mind - we believe that in the future work we proposed to conduct on the 
+project, we might need to use other statistical tests as well, such as Mann-Whitney U tests \cite{mann1947test}. Also, before
+we ran both statistical tests and the plotting command, we tested them thoroughly and checked whether the libraries compute 
+stable and robust results.
 

### 2018-04-19 paper/paper.tex
Finish comments complexity subsection

@@
   \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
+  \item 201,786 tickets have all our requirements for running the analysis: were closed by the time we fetched the data, 
+  are of high priority and are not \emph{wrong} values retrieved from Jira (i.e. outliers);
   \item 103,397 tickets have attachments which we split in the following categories:
@@
 with attachments and without attachments. Furthermore, the tickets that were marked as having attachments were split 
-into the categories specified in Section \ref{characterising}.
+into the categories specified in Section \ref{characterising}. In total, we looked at 201,786 tickets, among which 
+98,311 had attachments and 103,475 without any attachments.
 
@@
 Figure \ref{steps} shows the bar chart representing all closed, high priority tickets with or without steps 
-to reproduce in either the description field or in any of the comments.
+to reproduce in either the description field or in any of the comments. We looked in total at 201,786 tickets 
+among which 31,732 tickets had steps to reproduce and 170,054 did not have.
 
@@
 For this analysis, we only looked at tickets of high priority, closed and the project they correspond 
-is written in Java. We then ran a complex regular expression derived from the works of Bettenburg et. al 
+is written in Java. In total, we investigated looked at We then ran a complex regular expression derived from the works of Bettenburg et. al 
 \cite{bettenburg2012using} and Moreno et. al \cite{moreno2014use} and collected all the tickets that have 
@@
 
-A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
-with \emph{r} = \dots, \emph{p} = \dots.
+The comment field is comprised of a textual body, a corresponding author, its time of creation and any updates 
+that were performed on it throughout its lifecycle. They provide a space for developers and end users to discuss 
+anything related to the ticket they belong to. Any popular issue tracking system, such as Jira, does not enforce 
+any limit on any component of a comment, thus the number of words for a single comment can range from only 5 
+to well over 1,000.
+
+We firstly concatenated all comments into a single large string in order to be analysed for total number of words.
+We ran our comments analysis on 201,786 tickets among which 113,344 had comments and 88,442 did not have any comments.
+
+In Figure \ref{comments} we present the correlations between the total number of words in comments per ticket and 
+the corresponding Time-To-Close for that ticket. We can observe in the scatter plot that most tickets tend to 
+have up to around 3,200 words in total. However, there are tickets that have a total number of words as high as 
+around 25,000.
+
+From the figure we cannot clearly deduce whether increased number of words in comments influence 
+the Time-To-Close positively or negatively. However, a correlational analysis releaved a weak 
+positive relationship with $r = 0.271$ and $p < 0.01$. This implies a statistically significant finding - 
+as the number of comments increases, the quality of the ticket decreases.
+
+Even though this might be surprising at first, we need to analyse the possible context where such large 
+number of words in comments occur. What if the bug was so hard to reproduce that the developers needed to 
+ask more than one user how they experienced the issue in the tool? Another case might be that even though 
+the comments start by discussing fixing or implementing a feature, the developers and end users might 
+engage in new conversations about the product in general or other features that they might want to see 
+implemented. Also, what if comments are a means of communication for developers in the team? There are studies, 
+such as the one conducted by Lotufo et. al \cite{lotufo2015modelling}, that show the importance of comments 
+in software tickets in relation to communication activities surrounding the project. Another possible explanation 
+for having increased number of comments increase the Time-To-Close value and, thus, decrease quality, is that 
+having many comments or very verbose comment can lead to more difficult information extraction. On the other 
+hand, if there would be a light discussion, the developers would be able to quickly analyse all the comments 
+and collect whatever is necessary to resolve the ticket.
+
+One possible solution that we propose to this correlation is to have the ability to limit the number of 
+comments per ticket. As to our knowledge, one cannot do this in neither Jira nor Bugzilla. However, if it were 
+possible, we believe that this might help developers find the information they need quicker. But what happens 
+if the treshold is reached and there is still a need for clarifying certain aspects? We believe that having 
+a button redirecting anyone still interesting in commenting on the ticket to a messaging tool, such as 
+Slack, would be beneficial for the project overall. Thus, if they were redirected to let's say Slack, a small 
+tool could automatically be run that creates a new channel specifically for that ticket with the name set 
+to the unique ticket key (e.g. LUCENE-2901). We believe that such a solution could aid both developers in 
+completing tasks quicker but also end users for feeling more involved and valuable to the project.
 
@@
 \end{figure}
+
+Summary and description are the two most important and most frequently completed fields in a ticket on any
+issue tracking system. Even though summary is required on any issue tracking system, description might 
+be omitted if the reporter does not feel the need of adding any extra detail other than what is in the summary. 
+However, as bug reports are usually complex, there is a very small percentage of descriptions not filled in 
+by the reporters. They do not typically have any word limits, thus the reporter can add as much information as 
+they see fit.
+
+Figure \ref{fields} shows the scatter plot for the sum of numbers of words in summary and description, as well 
+as the Time-To-Close for the ticket. We have analysed a total number of 238,286 (all our closed tickets as they 
+all have), all having both summaries and descriptions.
+
+From the
 

### 2018-04-19 paper/paper.tex
Complete fields complexity subsection

@@
 
-From the
+The Figure shows a very similar correlation to the one for comments complexity. A correlational analysis revealed 
+a weak positive relationship with $r = 0.178$ and $p < 0.01$. This implies both that our results are statistically 
+significant and also that as number of words in summary and description increase, the Time-To-Close increases, thus 
+the quality of the ticket decreases.
 
-A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
-with \emph{r} = \dots, \emph{p} = \dots.
+This is not a surprise - as previously mentioned, summary and description are the core components of any ticket. 
+As summary is described by Jira, it should represent a short textual description of the bug or the feature request. However,
+we have identified tickets having summaries with even more than 200 words. This is not optimal and might obfuscate
+the essential reason of filing that ticket from triagers and developers working on the project. One of the findings 
+Zimmermann et. al \cite{zimmermann2010makes} present in their study is that a good, succint summary can significantly 
+reduce the effort invested by the developers.
+
+Description, on the other hand, even though it is made to be a more detailed summary of the report, it should still be
+in some reasonable parameters. During our analysis process, we identified more than 50 tickets having descriptions 
+with more than 4,000 words. Even though they included various types of information, including steps to reprodce, 
+we believe that the reason why Jira and the other popular issue tracking systems created so many fields for bug reports 
+is that the information that could all be put in description should be split across these fields: 
+\begin{itemize}
+  \item if there are stack traces or steps to reproduce, as we mentioned above, there should be specific fields 
+  created exclusively for them; 
+  \item if the end user is an experienced one and has reported numerous bugs or feature requests for the project, 
+  they might also be able to provide an estimate for the difficulty of the task; however, that should be stored in the 
+  Jira system field called \"Story Points\";
+  \item the user might also want to provide excerpts of code or previous discussions with other end users/developers; 
+  however, they should not upload it inside the description field, but rather create a text attachment (e.g. markdown
+  document) and attach it separately so that they keep the description clean and easy to follow.
+\end{itemize}
+
+A solution for this issue could be the freedom of easily selecting the total number of words allowed for summary and 
+description. Even though this is possible with Jira, the process of configuring it is not trivial, thus many 
+administrators do not perform this step. An even better approach would be to have a tool automatically generating 
+word limits based on, for example, the experience of the reporter - if he/she has significant knowledge regarding 
+the project, they should be allowed to include lengthier summaries or descriptions mainly because they are more inclined 
+to know that without a very good reason, following this approach is not the most optimal way.
+
+Another simple and straightforward solution can be the simple addition of hints below or above the text boxes for summary 
+and description where administrators can write succint messages adivising reporters to not write verbose paragraphs 
+unless they really have a very good reason to do so.
 

### 2018-04-19 paper/paper.tex
Complete grammar correctness subsection in the paper

@@
 Figure \ref{fields} shows the scatter plot for the sum of numbers of words in summary and description, as well 
-as the Time-To-Close for the ticket. We have analysed a total number of 238,286 (all our closed tickets as they 
-all have), all having both summaries and descriptions.
+as the Time-To-Close for the ticket. We have analysed a total number of 238,286 tickets, as they all have both 
+summaries and descriptions.
 
@@
 
-A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
-with \emph{r} = \dots, \emph{p} = \dots.
+Through calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
+managed to calculate the total number of grammar errors in summary, description and comments for a total number 
+of 133,689 tickets. As shown in a number of studies, the number of spelling errors can influence the quality of a ticket. 
+However, in the work conducted by Schugerl et. al \cite{schugerl2008mining}, the authors found that spelling errors 
+can be found in both high and low quality tickets, thus should not be considered as a reliable factor for determining
+the Time-To-Close for a ticket. In the rest of this section we will demonstrate the contrary - tickets with more 
+grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
+tickets.
+
+This analysis type is called grammar correctness rather than spelling scores because the range of errors returned 
+by Bing Spell Check API are of many types, some of which are:
+\begin{itemize}
+  \item spelling errors - e.g. Hwo are you today? However, they go much further than a simple character mistyped - for example,
+  if one would type Micrsft, it would automatically flag it as a grammar error because it also takes into account a large 
+  database of words not in standard dictionaries, but also popular words in the tech world (e.g. company names) or 
+  jargon language (e.g. dab dance);
+  \item contextual errors - e.g. I ate a book today; even though this is not a misspell, the API will return \emph{book} as 
+  a grammar error due to the fact that it is used in the wrong context;
+  \item it can detect the wrong usage of a verb tense in a specific context;
+  \item it can flag wrong conjugations of verbs;
+\end{itemize}
+
+After concatenating the strings for all comments, summary and description, we ran our analysis and then plotted the 
+data which is depicted in Figure \ref{grammar}. A correlational analysis revealed a weak positive
+relationship with $r = 0.134$ and $p < 0.01$. Thus, our results are statistically significant, implying that 
+having more grammar errors in a ticket will increase the Time-To-Close for a ticket and, thus, decrease the quality.
+
+This is expectable as having a text difficult to grasp and understand makes it harder to reason about what needs 
+to be done in order to fix a ticket. As it can be seen in the graph, most tickets are concentrated in the range of 
+0 to 40 grammar errors per ticket. Having 40 grammar errors in a ticket is quite a large number, considering the fact 
+that many tickets don't have comments at all and summary and description are not large in general.
+
+However, we can not automatically change this through automation like the solutions we presented in the previous 
+analysis types. We cannot call, for example, the Bing Spell Check API every couple of seconds on the text the user 
+is inputting in the ticket as the costs would become unbearable very soon. Thus, what can be done to fix this? It is, 
+after all, in the human nature to make mistakes, and typing is no exception. The solution we are proposing implies a 
+local, lightweight spell checker that is run automatically as the user types. This tool would not make any external 
+calls, so there would be no costs and the load on the server would also be lower. There are already local applications 
+that can be used for performing such real-time analysis on the text, one of them being LibreOffice's built-in 
+spell checker.
 

### 2018-04-19 paper/paper.tex
Almost complete the entire draft for the paper

@@
 There are multiple platforms for providing such issue tracking systems, among which
-the most popular are Jira \cite{jira} and Bugzilla \cite{bugzilla}. For both platforms,
+the most popular are Jira and Bugzilla. For both platforms,
 the tickets are split into two main categories: feature requests (i.e. feature to be 
@@
 
+%TODO: add a bit more info here and add summary for all analyses (which one is significant, what does each of them imply)
+
 \subsection{Attachments}
@@
 is inputting in the ticket as the costs would become unbearable very soon. Thus, what can be done to fix this? It is, 
-after all, in the human nature to make mistakes, and typing is no exception. The solution we are proposing implies a 
-local, lightweight spell checker that is run automatically as the user types. This tool would not make any external 
-calls, so there would be no costs and the load on the server would also be lower. There are already local applications 
-that can be used for performing such real-time analysis on the text, one of them being LibreOffice's built-in 
-spell checker.
+after all, in the human nature to make mistakes, and typing is no exception. If we, for example, have some hint or a rule
+in the code of conduct for the project stating that everything should be 100\% gramatically correct, many reporters not 
+having English as their primary language would feel unwelcomed and they might not get involved in the project anymore.
+
+The solution we are proposing implies a local, lightweight spell checker that is run automatically as the user types. 
+This tool would not make any external calls, so there would be no costs and the load on the server would also be lower. 
+There are already local applications that can be used for performing such real-time analysis on the text, one of them 
+being LibreOffice's built-in spell checker.
 
@@
 
-A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
-with \emph{r} = \dots, \emph{p} = \dots.
+Sentiment analysis is a technique of employing Machine Learning algorithms in order to infer a sentiment 
+score from textual information. These algorithms need to be trained on very large data sets in order to 
+produce valuable results. Moreover, we would have also needed an already annotated data set, which means 
+a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
+there are open source libraries that can help creating and employing the algorithms, such as TensorFlow, 
+we would still have needed tickets where we defined what do we mean by positive/negative tickets, as well as
+manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
+Cloud Platform Natural Language Processing, considered the best such service at the moment.
+
+After we concatenated summaries, descriptions and all the comments for every ticket, we started sending our 
+requests to Google and we plotted the data shown in Figure \ref{sentiment}. A correlational analysis revealed a 
+weak negative relationship with $r = -0.114$, $p < 0.01$. Therefore, we obtained statistically significant 
+results implying that as the sentiment decreases (i.e. becomes more negative), the Time-To-Close increases, thus 
+decreasing the quality of a ticket.
+
+We can see in the Figure that neutral scores (i.e. between -0.42 and 0.42) show rather neutral results, which 
+was expectable: this most probably implies that the discussions and descriptions for these tickets revolved 
+completely around the ticket and nothing else.
+
+However, as the sentiment decreases, we can clearly observe that the sentiment scores increase significantly. 
+This might signify that once the discussion becomes \"heated\", the developers might lose interest in solving 
+the task anymore. Also, rude language might be a driver for increased Times-To-Close because when developers are 
+answering questions from the reporters (or vice versa), the other person might become rude or unpolite, which can 
+make them feel unwelcomed and start to lose interest in helping the project anymore.
+
+On the other side of the spectrum, having a more positive score leads to higher quality in tickets. Calefato et. al 
+\cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
+the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general.
 

### 2018-04-19 paper/paper.tex
Complete final draft of paper

@@
 manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
-Cloud Platform Natural Language Processing, considered the best such service at the moment.
+Cloud Platform Natural Language Processing, considered the best such service at the moment. This API returns 
+a score between -1 (most negative) and +1 (most positive) for any text encoded in the HTTP request.
 
@@
 \cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
-the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general.
+the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general. This 
+implies that when developers and triagers treat their reporters respectfully and offer support whenever possible, 
+the users will feel more welcomed and willing to help report other bugs in the future as well. We also have scores of 
+over 0.9, meaning that the actors participating in the discussion (or the reported summary/description) might compliment 
+each other for doing a great job.
+
+We strongly believe that having a positive sentiment score for tickets is valuable for absolutely everyone: the company
+behind the projects sees increased overall performance and productivity, developers feel better working in the team or
+on that specific tool and reporters will be more willing to contribute in the future with other tickets.
+
+A solution for pushing towards this ideal scenario would be expensive for the company, but the most efficient - have a 
+sentiment analysis tool running in the background as the user is typing in any text box. If they reach a certain low 
+treshold and it is believed that they are becoming rude or unpolite, there could be a warning/pop-up on the screen advising 
+them to not do that as it wouldn't help any party, but rather try to be polite, engaging and friendly. One other solution
+is a much more cost-effective one, but less efficient - the issue tracking system administrators could include a section 
+in the code of conduct for the project stating that promoting a positive environment will help everyone. This way, people 
+revolving around the project might be more inclined to be friendly.
 

### 2018-04-19 paper/paper.tex
Complete first final draft of the paper

@@
 all variables to test their significance and rank correlation coefficient and we will present each of them in their 
-corresponding subsection. Lastly, we also discuss possible reasons why certain correlations occured.
+corresponding subsection.
 
-%TODO: add a bit more info here and add summary for all analyses (which one is significant, what does each of them imply)
+The answers to our research questions are all statistically significant and they can summarised as follows:
+\begin{itemize}
+  \item having attachments improves the quality of a ticket;
+  \item having steps to reproduce improves the quality of a ticket;
+  \item having stack traces improves the quality of a ticket;
+  \item more grammar errors imply lower ticket quality;
+  \item lower sentiment scores result in lower ticket quality;
+  \item verbose comments result in lower ticket quality;
+  \item verbose summary and description imply lower ticket quality.
+\end{itemize}
+
+For every type of analysis, we also discuss possible reasons why certain correlations occured. Furthermore, for all 
+of them we give possible solutions that could be implemented in order to maximise the ticket quality as cost-effective 
+and efficient as possible.
 

### 2018-04-19 paper/paper.tex
Fix typos and abstract structure for the paper

@@
 investigating a large number of variables surrounding software tickets, 
-such as whether the presence of stack traces influence the time 
-to close for the ticket. Our results show that the presence and type of attachments,
-comments complexity (i.e. number of comments per ticket and total number of words), 
-summary and description complexity, grammar correctness scores
-as well as the sentiment drawn from the comments can influence the quality of the ticket.
-We bring a couple of novel aspects to the research
-community including one of the largest dataset statistically analysed in the field,
-as well as state-of-the-art sentiment and grammar correctness analysis.
+Our results show that the presence and type of attachments,
+comments complexity, summary and description complexity, presence of stack traces, presence
+of steps to reproduce, grammar correctness scores,
+as well as the sentiment analysis scores can significantly influence 
+the quality of the ticket. We bring a couple of novel aspects to the research
+community including one of the largest dataset statistically analysed in this particular field,
+as well as state-of-the-art sentiment and grammar correctness analyses.
 \end{abstract}

### 2018-04-20 paper/paper.tex
Fix errors in abstract

@@
 \begin{abstract}
-Software tickets are of valuable importance to the whole computing science 
-field - they guide engineers towards better planning, management 
-and tracking of their progress throughout complex projects. However, there
+Issue trackins systems have become the defacto standard for tracking work items in 
+software projects - they guide engineers towards better planning and 
+managing their progress throughout complex projects. However, there
 are few studies that investigate what makes for a high quality,
@@
 comments complexity, summary and description complexity, presence of stack traces, presence
-of steps to reproduce, grammar correctness scores,
-as well as the sentiment analysis scores can significantly influence 
-the quality of the ticket. We bring a couple of novel aspects to the research
-community including one of the largest dataset statistically analysed in this particular field,
-as well as state-of-the-art sentiment and grammar correctness analyses.
+of steps to reproduce, grammar correctness scores, as well as sentiment can significantly influence 
+the quality of the ticket. We supply one of the largest dataset statistically 
+analysed in this particular field, as well as state-of-the-art sentiment and grammar correctness analyses.
 \end{abstract}

### 2018-04-20 paper/paper.tex
Change introduction section - first paragraph

@@
 
-In the past decade, technology has drastically increased its influence on 
-virtually every aspect of our society. Therefore, software projects have 
-inherently become more complex and require increasing number of developers in
-the team. Due to this, software engineers have created issue tracking systems,
-a means of planning, managing and tracking work products in the form of 
-\emph{software tickets} or \emph{issues}.
+In the past decade software projects have inherently become more complex and require increasing number of developers in
+the team. Studies such as the one conducted by Herbsleb \cite{herbsleb2007global} show how software engineering teams have 
+transitioned from small, collocated to globally distributed teams. One reason elicited in the paper is the increasing 
+popularity of communication tools, such as Slack or Google Hangouts. Due to this, developers have created issue tracking 
+systems as means of planning, managing and tracking work products in the form of \emph{software tickets} or \emph{issues}.
 
@@
 Even though tickets provide such comprehensive data regarding a specific task, studies have shown 
-that fixing bugs is one of the most common tasks performed by developers \cite{latoza2006maintaining}. One of
+that fixing bugs is one of the most common and time consuming tasks performed by developers \cite{latoza2006maintaining}. One of
 the reasons for this is the communication friction between developers and end users \cite{Korkala2014WasteIdentification}

### 2018-04-20 paper/paper.tex
Fix the whole introduction paragraph

@@
   \item does the presence of steps to reproduce reduce the \emph{Time-To-Close}?
-  \item is there a relationship between the number of comments influence \emph{Time-To-Close}?
-  \item is there a relationship between 
+  \item is there a relationship between the number of words in comments and \emph{Time-To-Close}?
+  \item does the total number of words in summary and description have an impact on \emph{Time-To-Close}?
+  \item does the number of grammar errors in summary, description and comments have an effect on the quality of a ticket?
+  \item does a positive or negative ticket influence its \emph{Time-To-Close}?
 \end{itemize}
@@
 \begin{itemize}
-  \item an innovative tool was built for the purpose of this project, its strengths lying in its simplicity, speed and
-  extensability;
+  \item an innovative tool was built for the purpose of this project, providing efficient data collection and analysis of
+  tickets;
   \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
@@
 
-In Section \ref{related_work} we iterate over state-of-the art studies in the field and then continue with 
-Section \ref{building} where we discuss how the ticket data set was collected and analysed. We continue with describing 
-the data set (Section \ref{characterising}) where we provide insights into various aspects of the data (e.g. size of database,
-number of tickets with attachments) and then discuss about correlations between the variables (Section \ref{correlations}).
-Finally, we provide future research directions in Section \ref{future_work} and present our conclusions in Section \ref{conclusions}.
+The rest of the paper is structured as follows. In Section \ref{related_work} we iterate over state-of-the art studies in 
+the field and then continue with Section \ref{building} where we discuss how the ticket data set was collected and 
+analysed. We continue with describing the data set (Section \ref{characterising}) where we provide insights into various 
+aspects of the data (e.g. size of database, number of tickets with attachments) and then discuss correlations between 
+the variables (Section \ref{correlations}). Finally, we provide future research directions in Section \ref{future_work} 
+and present our conclusions in Section \ref{conclusions}.
 

### 2018-04-20 paper/paper.tex
Add latest version of the paper

@@
 makes for a valuable bug report through qualitative analysis. 
-After conducting interviews with over 450 developers, one of the main factors
+After conducting interviews with over 450 developers, Bettenburg et. al concluded that one of the main factors
 behind a quality ticket is grammar correctness in summary and description. Another

### 2018-04-21 paper/paper.tex
Fix issues inside paper

@@
 
+In this section we will present what are the state-of-the art studies in the issue/ticket quality 
+field. More specifically, we will look at research papers that investigated what makes for a valuable ticket, 
+how can one extract structured/unstructured data from tickets (e.g. stack traces), ticket duplication and its 
+positive and negative outcomes, quality of modern issue tracking systems as well as automating the process 
+of summarizing tickets or the optimal assignee.
+
 The study of Bettenburg et. al \cite{bettenburg2008makes} showed what 
@@
 information that is not present in the master report (i.e. the original report that was 
-filed). Moreover, developers also specified that they have often found value in these 
+filed). Also, developers also specified that they have often found value in these 
 duplicate bug reports and that they can even aid automated triaging techniques.
+
+%TODO: ADD HERE PROPER PAPER
+However, the study conducted by Cavalcanti et. al \cite{cavalcanti2013bug} shows completely 
+different results. The authors investigated around 280,000 tickets from multiple open and 
+closed source repositories and found that having bug duplicates
+97,000 tickets from the Mozilla repository in order to infer the quality of merging duplicate
+bug reports. Their results are statistically significant and they show that merging bug report 
+duplicates improved the overall quality of the project (i.e. )
 

### 2018-04-21 paper/paper.tex
Fix more issues inside the paper

@@
 of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
-GNOME and Eclipse and projects and split their approach into four steps:
-  \begin{itemize}
-    \item extract and organize tickets;
-    \item pre-process tickets (i.e. tokenization, stop word removal and stemming);
-    \item train the classifier on two datasets of tickets - 70\% 
-      training and 30\% evaluation;
-    \item apply the trained classifier on the evaluation set.
-  \end{itemize}
+GNOME and Eclipse and projects and split their approach into four steps: extract and organize tickets, 
+pre-process tickets (i.e. tokenization, stop word removal and stemming), train the classifier on two datasets 
+of tickets - 70\% training and 30\% evaluation and apply the trained classifier on the evaluation set.
 The conclusions they drew from running the evaluation process were rather 
@@
   \begin{itemize}
-    \item it is designed with simplicity in min, thus making it easier for others who might join the project to read 
-    and understand the codebase;
-    \item it is compiled, statically typed, which implies that it is a much faster candidate than other interpreted languages
-    such as Ruby or Python;
+    \item it is designed with simplicity in mind, thus making it easy for others who might join the project to read 
+    and understand the codebase; this would prove useful for us as developing the tool further is on our list of future 
+    work items;
+    \item it is a compiled, statically typed language that produces cross-platform executables when building the application;
+    this is helpful for our research as we can use any machine or cluster of computers regardless of the operating system 
+    running on them and collect even larger number of tickets than what we have collected so far;
     \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
+    in our case, why it helps us is by allowing access to goroutines, very lightweight threads that can scale even up to 
+    millions; we use this powerful concept while fetching tickets from Jira or storing in the database - at one point, we had 
+    more than 30,000 goroutines running at the same time.
   \end{itemize}
@@
   \item tickets were closed and had a maximum \emph{Time-To-Close} value of 27,000 hours (roughly 3 years) (we added the 
-  higher bound as well in order to eliminate outliers produced by wrong data retrieved by Jira);
-  \item remove outliers for all categories - some fields for a small number of tickets that had wrong values (e.g. one ticket
+  higher bound as well in order to eliminate outliers retrieved by Jira);
+  \item remove outliers for all categories - some fields for a small number of tickets that had extreme values (e.g. one ticket
   had over 270,000 comments) introduced by the team behind the project and we needed to exclude them so that the analysis 
@@
 
-Then, it runs in parallel the \emph{seven types of analysis} for answering the research questions outlied in Section \ref{intro}, 
-each in its own separate goroutine in order to speed up the process:
+Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
+outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
 \begin{itemize}
@@
   \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
-  influence the quality of a ticket;
+  influence the quality of a ticket; the regular expression was adapted after the general guidelines elicited by 
+  Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
+  steps to reproduce are a subset);
   \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
@@
 lighter on computing power). After having the tickets available, we start looping through them and perform all 
-analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
+analysis types mentioned above. Once a value is computed (e.g. grammar correctness score), it gets set in 
 its corresponding field in the ticket struct and is subsequently stored back in the database. We chose this approach because 

### 2018-04-21 paper/paper.tex
Add more fixes to the paper

@@
   \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
+  we applied the general guidelines described by Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured 
+  data (including steps to reproduce) from tickets in order to create a regular expression for capturing them;
   \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
@@
 attachments is somewhat neutral in the entire data set.
+
+However, we need to take into consideration tickets that have code attachments which are a \emph{thread to validity}. 
+When a snippet of code is attached, it might result in more complex tickets due to developers spending more time on 
+understanding what is going on and reasoning about the attached code. Also, engineers might need to run or test 
+the code attached which can again increase the Time-To-Close.
 

### 2018-04-21 paper/paper.tex
Fix other issues inside the paper

@@
 This is the first command implemented in our tool - it is desgined to fetch, from any valid Jira URL, any number of tickets 
-and then store everything inside an instance of BoltDB \cite{bolt}, which is a very simple yet powerful key-value pair 
+and then store everything inside an instance of BoltDB \cite{bolt}, a key-value pair 
 database. The whole process is parallelized with the possibility of scaling even up to hundreds of goroutines
@@
 we noticed that we did not need to query the database often, but rather get the whole array of tickets and manipulate them. Moreover, 
-a MongoDB or Postgres DB would have required a running server. Even though the server could have been running on the local machine, 
-Bolt instances are actually files with the extension \emph{db} saved on disk, thus it is trivial to create backups.
+a MongoDB or Postgres DB would have required a running server.
 
-We have interacted with the Jira Server REST API which has very good documentation written by the Atlassian team. After getting
-familiar with all the features the REST API offers, we have opted for getting paginated issues from the server, which means 
+The goroutines interact with the Jira Server REST API. The goroutines exploit the pagination facility in the API, which means 
 slicing the whole set of tickets into multiple smaller arrays to improve performance and reduce the load on the server. We also
-specified to Jira exactly what set of issue fields to return and, eventually, while responses were retrieved from the instance,
+specified to Jira exactly what set of issue fields to return and, while responses were retrieved from the instance,
 we began storing them into our Bolt DB instance.
@@
 The way we chose to store them was to set the issue key (i.e. unique identifier that differentiates a ticket from all others across all 
-projects inside a Jira instance) as the key of the pair and the value is the JSON representation of the ticket. This helped us reduce 
-the size of the database once we reached hundreds of thousands of tickets.
+projects inside a Jira instance) as the key of the pair and the value is the JSON representation of the ticket. This storage method, in conjunction
+with how simple Bolt is designed, helped us reduce the size of the database significantly. For small databases, 
+using RDBMSs (e.g. Postgres, MySQL, Oracle) is not performance critical, but when the data set is large such as in our study, bottlenecks might start affecting 
+the progress of the project. This is mainly due to the structure of how Jira returns the tickets; for example, all issues have comments as 
+a field, consisting of an array of structs with body, author, created time etc. Then, each comment has a changelog history attached to it, 
+having in turn multiple changelog groups and also each group can have multiple changelog items. Therefore, this long pipeline became a serious 
+bottleneck for us once we reached a certain number of tickets because we had relations between all these tables, compared to Bolt which does not 
+link any key-value pair to another. Another major point when we decided to proceed with Bolt was that we did not need to query the data at all 
+as all our processing was too complex to convert the logic into an SQL query.
 
@@
 
-We firstly concatenated all comments into a single large string in order to be analysed for total number of words.
-We ran our comments analysis on 201,786 tickets among which 113,344 had comments and 88,442 did not have any comments.
+We concatenated all comments into a single large string in order to be analysed for total number of words. This step 
+was performed at the end of each ticket's lifecycle. We ran our comments analysis on 201,786 tickets among which 
+113,344 had comments and 88,442 did not have any comments.
 
@@
   \end{center}
-  \caption{\label{fields}Fields complexity analysis.}
+  \caption{\label{fields}Time-To-Close versus summary and description word count.}
 \end{figure}
@@
 as the Time-To-Close for the ticket. We have analysed a total number of 238,286 tickets, as they all have both 
-summaries and descriptions.
+summaries and descriptions. We concatenated the summary and description for every ticket at the end of the ticket 
+lifecycle.
 
@@
 \begin{itemize}
-  \item spelling errors - e.g. Hwo are you today? However, they go much further than a simple character mistyped - for example,
+  \item spelling errors; however, they go much further than a simple character mistyped - for example,
   if one would type Micrsft, it would automatically flag it as a grammar error because it also takes into account a large 
@@
 
-Another extension to the app could be adding the possibility of selecting what database provider to use 
-for storing tickets. As we previously mentioned, we currently provide only Bolt DB support, but adding others is 
-again straightforward, mainly because we already store tickets as arrays of bytes representing the JSON encoded 
-value. Thus, if we add a new database provider, if they allow us to store items as raw bytes (which most DBs already 
-do), then the necessary code changes would be minimal.
-
 One other improvement to the application could be adding more robust support for statistical analysis. At the moment, 

### 2018-04-21 paper/paper.tex
Add other future work candidate

@@
 
+We wish that our final deliverable would be either a \emph{goodness} metric, describing the quality of a ticket based 
+on the information inside, or a recommender tool that could automatically create high quality tickets. This requires 
+intensive work over a longer period of time, but we believe that with the findings presented in this study together 
+with other state-of-the-art research in the field, it is possible to implement it.
+
 \section{Conclusions}\label{conclusions}

### 2018-04-21 paper/paper.tex
Add section in related work related to merging duplicate bug reports

@@
 
-%TODO: ADD HERE PROPER PAPER
-However, the study conducted by Cavalcanti et. al \cite{cavalcanti2013bug} shows completely 
-different results. The authors investigated around 280,000 tickets from multiple open and 
-closed source repositories and found that having bug duplicates
-97,000 tickets from the Mozilla repository in order to infer the quality of merging duplicate
-bug reports. Their results are statistically significant and they show that merging bug report 
-duplicates improved the overall quality of the project (i.e. )
+Another study that investigates duplicate bug reports is the work conducted by Prifti et. al \cite{prifti2011detecting}. 
+The authors first collected 75,000 bug reports from Bugzilla for the Firefox project. Then, they created a tool 
+for detecting bug report duplicates with an accuracy of 53\%. However, due to prior 
+findings showing both that duplicate reports can improve the quality \cite{bettenburg2008duplicate}
+but also decrease it \cite{cavalcanti2013bug}, this study tries to achieve a middle ground - 
+before the reporter can file the bug in the system, the duplicate detection tool previously 
+described runs and checks whether there are any duplicates. If there are, the user is presented 
+with the possibility of simply adding extra information, if suitable, to one of the duplicates 
+found. This is indeed a novel approach that can bring great benefits to the software engineering 
+community and the authors state that they wish to pursue future work on this idea.
 
@@
   \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
-  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
+  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API to perform analysis on summary, 
   description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
@@
   (e.g. unknown token, misspell);
-  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
+  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API to retrieve the 
   sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
@@
 analyse even more possible correlations. As the Go community lacks native libraries to perform statistical tests, 
-the users of our tool might miss the simplicity of running such tests in R. A solution can be to integrate the 
+the users of our tool might miss the simplicity of running such tests in R. A solution can be to integrate Senseye's 
 Roger library \cite{r_stats} inside the stats package, which basically allows any Go application to communicate with 

### 2018-04-21 paper/paper.tex
Fix issue with quality changed with time-to-close

@@
 \begin{itemize}
-  \item the presence of steps to reproduce increases the quality of a ticket;
-  \item the presence of stack traces increases the quality of a ticket;
-  \item the presence of attachments increases the quality of a ticket - more specifically tickets with screenshots, 
-  config files or text files have lower times-to-complete than tickets without attachments;
-  \item higher numbers of grammar errors impply lower quality scores for a ticket;
-  \item higher sentiment scores imply higher quality scores for a ticket;
-  \item higher numbers of words in comments imply lower quality scores for a ticket;
-  \item higher number of words in description and summary imply lower quality scores for a ticket.
+  \item the presence of steps to reproduce reduces the time-to-close for a ticket;
+  \item the presence of stack traces reduces the time-to-close for a ticket;
+  \item the presence of attachments reduces the time-to-close for a ticket - more specifically tickets with screenshots, 
+  config files or text files help tickets get closed quicker than those without attachments;
+  \item higher numbers of grammar errors imply increased time-to-close values;
+  \item higher sentiment scores imply reduced time-to-close values for a ticket;
+  \item higher numbers of words in comments imply increased time-to-close values for a ticket;
+  \item higher number of words in description and summary increase the time-to-close values for tickets.
 \end{itemize}

### 2018-04-21 paper/paper.tex
Change all occurences of quality to time-to-close wherever needed

@@
   \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
-  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
+  of attachments (e.g. screenshots, archive, code snippets) influence time-to-close the most;
   \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
-  influence the quality of a ticket; the regular expression was adapted after the general guidelines elicited by 
+  influence the time-to-close of a ticket; the regular expression was adapted after the general guidelines elicited by 
   Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
@@
 \begin{itemize}
-  \item having attachments improves the quality of a ticket;
-  \item having steps to reproduce improves the quality of a ticket;
-  \item having stack traces improves the quality of a ticket;
-  \item more grammar errors imply lower ticket quality;
-  \item lower sentiment scores result in lower ticket quality;
-  \item verbose comments result in lower ticket quality;
-  \item verbose summary and description imply lower ticket quality.
+  \item having attachments reduces time-to-close of a ticket;
+  \item having steps to reproduce reduces time-to-close of a ticket;
+  \item having stack traces reduces time-to-close of a ticket;
+  \item more grammar errors imply increase time-to-close values;
+  \item lower sentiment scores result in increased time-to-close values;
+  \item verbose comments result in increased time-to-close values;
+  \item verbose summary and description imply increased time-to-close values.
 \end{itemize}
@@
 positive relationship with $r = 0.271$ and $p < 0.01$. This implies a statistically significant finding - 
-as the number of comments increases, the quality of the ticket decreases.
+as the number of comments increases, the time-to-close value of the ticket also increases.
 
@@
 grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
-tickets.
+tickets (i.e. increased time-to-close).
 
@@
 
-On the other side of the spectrum, having a more positive score leads to higher quality in tickets. Calefato et. al 
+On the other side of the spectrum, having a more positive score leads to reduced time-to-close values for tickets. Calefato et. al 
 \cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
@@
 We manager to answer all seven research questions and find factors that can posittively or 
-negatively affect the quality of a ticket. All of our results are statistically significant and we can summarise 
+negatively affect the time-to-close value of a ticket. All of our results are statistically significant and we can summarise 
 them as follows:

### 2018-04-21 paper/paper.tex
Complete paper with all suggestions

@@
   \begin{center}
-  \includegraphics[scale=0.23]{images/attachments.png}
+  \includegraphics[scale=0.25]{images/attachments.png}
   \end{center}
@@
   \begin{center}
-    \includegraphics[scale=0.23]{images/steps_to_reproduce.png}
+    \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
   \end{center}
@@
   \begin{center}
-    \includegraphics[scale=0.23]{images/stack_traces.png}
+    \includegraphics[scale=0.25]{images/stack_traces.png}
   \end{center}
@@
   \begin{center}
-    \includegraphics[scale=0.23]{images/comment_complexity.png}
+    \includegraphics[scale=0.25]{images/comment_complexity.png}
   \end{center}
@@
 was performed at the end of each ticket's lifecycle. We ran our comments analysis on 201,786 tickets among which 
-113,344 had comments and 88,442 did not have any comments.
+113,344 had comments and 88,442 did not have any comments. What we calculated as being total number of words inside comments 
+is all the words inside all comments corresponding to a ticket summed up.
 
@@
 From the figure we cannot clearly deduce whether increased number of words in comments influence 
-the Time-To-Close positively or negatively. However, a correlational analysis releaved a weak 
-positive relationship with $r = 0.271$ and $p < 0.01$. This implies a statistically significant finding - 
-as the number of comments increases, the time-to-close value of the ticket also increases.
+the Time-To-Close positively or negatively. Actually, we can assume at first sight that there is a descending trend implying more 
+words produce smaller Time-To-Close values. However, the bulk of values plotted are in the range of 
+1 to 1,600 total comment words per ticket (76,633 tickets) and in this slice of tickets, the trend is descending.
+We did not generate the plot containing only these values because there would still be 36,711 tickets left out.
+
+A correlational analysis ran on all 201,786 tickets, however, releaved a weak positive relationship with $r = 0.271$ and $p < 0.01$. 
+This implies a statistically significant finding - as the number of comments increases, the time-to-close value of the ticket also increases.
 
@@
   \begin{center}
-    \includegraphics[scale=0.23]{images/fields_complexity.png}
+    \includegraphics[scale=0.25]{images/fields_complexity.png}
   \end{center}
@@
 
-The Figure shows a very similar correlation to the one for comments complexity. A correlational analysis revealed 
-a weak positive relationship with $r = 0.178$ and $p < 0.01$. This implies both that our results are statistically 
-significant and also that as number of words in summary and description increase, the Time-To-Close increases, thus 
-the quality of the ticket decreases.
+The Figure shows a very similar correlation to the one for comments complexity - it seems that as the number of words 
+in summary and description increases, the Time-To-Close will decrease. This is true for the majority of the tickets 
+which are in the range of 2 to 290 words, but as in the case of comments complexity analysis, we did not generate 
+the plot only for those as we would have left 61,322 tickets out (out of a total of 201,786 tickets analysed).
+
+However, a correlational analysis ran on all 201,786 tickets revealed a weak positive relationship with $r = 0.178$ and $p < 0.01$. 
+This implies both that our results are statistically significant and also that as number of words in summary and description increase, 
+the Time-To-Close increases, thus the quality of the ticket decreases.
 
@@
   \begin{center}
-    \includegraphics[scale=0.23]{images/grammar_correctness.png}
+    \includegraphics[scale=0.25]{images/grammar_correctness.png}
   \end{center}
@@
   \begin{center}
-    \includegraphics[scale=0.23]{images/sentiment_analysis.png}
+    \includegraphics[scale=0.25]{images/sentiment_analysis.png}
   \end{center}

### 2018-04-22 paper/paper.tex
Add skips to correctly position all plots
Fix issues

@@
 \author{Andrei-Mihai Nicolae}
-\matricnum{21473292}
+\matricnum{2147392}
 
@@
 \begin{abstract}
-Issue trackins systems have become the defacto standard for tracking work items in 
+Issue tracking systems have become the defacto standard for tracking work items in 
 software projects - they guide engineers towards better planning and 
@@
 In this research paper, we present our findings after 
-investigating a large number of variables surrounding software tickets, 
+investigating a large number of variables surrounding software tickets.
 Our results show that the presence and type of attachments,
@@
 
-In the past decade software projects have inherently become more complex and require increasing number of developers in
+In the past decade software projects have inherently become more complex and they now require increasing number of developers in
 the team. Studies such as the one conducted by Herbsleb \cite{herbsleb2007global} show how software engineering teams have 
@@
 
+\vskip30pt
+
 \subsection{Attachments}
@@
 
+\vskip18pt
+
 \subsection{Steps to Reproduce}
@@
 when a ticket is created by reporters.
+
+\vskip12pt
 
@@
 unless they really have a very good reason to do so.
+
+\vskip10pt
 

### 2018-04-22 paper/paper.tex
Fix another issue
Fix typos

@@
 
-In the past decade software projects have inherently become more complex and they now require increasing number of developers in
-the team. Studies such as the one conducted by Herbsleb \cite{herbsleb2007global} show how software engineering teams have 
+In the past decade software projects have inherently become more complex and they now require an increasing number of developers 
+on the team. Studies such as the one conducted by Herbsleb \cite{herbsleb2007global} show how software engineering teams have 
 transitioned from small, collocated to globally distributed teams. One reason elicited in the paper is the increasing 
@@
 
-Even though tickets provide such comprehensive data regarding a specific task, studies have shown 
+Even though tickets provide such comprehensive data regarding a specific task, evidence shows 
 that fixing bugs is one of the most common and time consuming tasks performed by developers \cite{latoza2006maintaining}. One of
@@
 screenshot is unclear). Another main reason for this waste of effort on solving tickets, according to 
-Just et. al \cite{just2008towards} and Zimmermann et. al \cite{zimmermann2009improving}, is the generally poor design of issue 
+Just et al. \cite{just2008towards} and Zimmermann et al. \cite{zimmermann2009improving}, is the generally poor design of issue 
 tracking systems. This can lead to various issues, including increased costs for the company, wasted development effort, 
@@
 
-The study of Bettenburg et. al \cite{bettenburg2008makes} showed what 
+The study of Bettenburg et al. \cite{bettenburg2008makes} showed what 
 makes for a valuable bug report through qualitative analysis. 
-After conducting interviews with over 450 developers, Bettenburg et. al concluded that one of the main factors
+After conducting interviews with over 450 developers, Bettenburg et al. concluded that one of the main factors
 behind a quality ticket is grammar correctness in summary and description. Another
@@
 Another research paper that strenghtens the argument that readability is a quality 
-factor in software tickets is the one presented by Hooimeijer et. al \cite{hooimeijer2007modeling}.
+factor in software tickets is the one presented by Hooimeijer et al. \cite{hooimeijer2007modeling}.
 They conducted their analysis on over 25,000 bug reports from the Mozilla project, 
@@
 which might prove beneficial for developers and subsequently improve the ticket quality.
-One such type is stack traces and Schroter et. al \cite{schroter2010stack} analyse how 
+One such type is stack traces and Schroter et al. \cite{schroter2010stack} analyse how 
 quickly tickets are closed when they either have stack traces included in their fields 
 (e.g. description) or not. They collected their data from the Eclipse project using 
-the InfoZilla tool proposed by Bettenburg et. al \cite{bettenburg2008extracting}.
+the InfoZilla tool proposed by Bettenburg et al. \cite{bettenburg2008extracting}.
 Then, they linked the stack traces to changes in source code by mining the Eclipse version 
@@
 one might believe that they cannot bring any value to a software project, the work of 
-Bettenburg et. al \cite{bettenburg2008duplicate} shows the contrary.
+Bettenburg et al. \cite{bettenburg2008duplicate} shows the contrary.
 The authors collected large amounts of data from the Eclipse open source project and ran
@@
 
-Another study that investigates duplicate bug reports is the work conducted by Prifti et. al \cite{prifti2011detecting}. 
+Another study that investigates duplicate bug reports is the work conducted by Prifti et al. \cite{prifti2011detecting}. 
 The authors first collected 75,000 bug reports from Bugzilla for the Firefox project. Then, they created a tool 
@@
 
-Bettenburg et. al \cite{bettenburg2012using} present in their work an application
+Bettenburg et al. \cite{bettenburg2012using} present in their work an application
 called infoZilla. This tool can
@@
 is the summary field, which holds a small description, usually between 5 and 30 words, of 
-the request or bug being reported. In the study conducted by Rastkar et. al \cite{rastkar2010summarizing}, 
+the request or bug being reported. In the study conducted by Rastkar et al. \cite{rastkar2010summarizing}, 
 the authors investigated whether tickets could be summarized automatically and efficiently. What 
@@
 
-The work of Just et. al \cite{just2008towards} examines a rather different aspect
+The work of Just et al. \cite{just2008towards} examines a rather different aspect
 of quality in tickets - they are investigating the quality of the underlying issue 
@@
 poor design in issue tracking systems and how the ticket creation process could be improved. 
-The study conducted by Lamkanfi et. al \cite{lamkanfi2010predicting} looks at this aspect and
+The study conducted by Lamkanfi et al. \cite{lamkanfi2010predicting} looks at this aspect and
 shows how issue tracking systems could be extended in order to automatically generate the severity 
@@
 determining the quality factors for tickets is automatically assigning a bug report or a feature request 
-to the most suitable developer (or team of developers). Anvik et. al \cite{anvik2011reducing}
+to the most suitable developer (or team of developers). Anvik et al. \cite{anvik2011reducing}
 propose a Machine Learning technique that could automatically assign a bug report to the developer 
@@
   influence the time-to-close of a ticket; the regular expression was adapted after the general guidelines elicited by 
-  Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
+  Bettenburg et al. \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
   steps to reproduce are a subset);
@@
   \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
-  we applied the general guidelines described by Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured 
+  we applied the general guidelines described by Bettenburg et al. \cite{bettenburg2008extracting} on how to extract structured 
   data (including steps to reproduce) from tickets in order to create a regular expression for capturing them;
-  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
+  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et al. 
   \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
@@
 For this analysis, we only looked at tickets of high priority, closed and the project they correspond 
-is written in Java. In total, we investigated looked at We then ran a complex regular expression derived from the works of Bettenburg et. al 
-\cite{bettenburg2012using} and Moreno et. al \cite{moreno2014use} and collected all the tickets that have 
+is written in Java. In total, we investigated looked at We then ran a complex regular expression derived from the works of Bettenburg et al. 
+\cite{bettenburg2012using} and Moreno et al. \cite{moreno2014use} and collected all the tickets that have 
 stack traces. In the end, we got a total number of 256 tickets that had at least an exception stack trace 
@@
 implemented. Also, what if comments are a means of communication for developers in the team? There are studies, 
-such as the one conducted by Lotufo et. al \cite{lotufo2015modelling}, that show the importance of comments 
+such as the one conducted by Lotufo et al. \cite{lotufo2015modelling}, that show the importance of comments 
 in software tickets in relation to communication activities surrounding the project. Another possible explanation 
@@
 the essential reason of filing that ticket from triagers and developers working on the project. One of the findings 
-Zimmermann et. al \cite{zimmermann2010makes} present in their study is that a good, succint summary can significantly 
+Zimmermann et al. \cite{zimmermann2010makes} present in their study is that a good, succint summary can significantly 
 reduce the effort invested by the developers.
@@
 of 133,689 tickets. As shown in a number of studies, the number of spelling errors can influence the quality of a ticket. 
-However, in the work conducted by Schugerl et. al \cite{schugerl2008mining}, the authors found that spelling errors 
+However, in the work conducted by Schugerl et al. \cite{schugerl2008mining}, the authors found that spelling errors 
 can be found in both high and low quality tickets, thus should not be considered as a reliable factor for determining
@@
 
-On the other side of the spectrum, having a more positive score leads to reduced time-to-close values for tickets. Calefato et. al 
+On the other side of the spectrum, having a more positive score leads to reduced time-to-close values for tickets. Calefato et al. 
 \cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
@@
 open source ones. Most closed source projects have much more structured planning, tracking and management activities - as 
-Crowston et. al \cite{crowston2012free} present in their study, open source projects lack organized coordination which,
+Crowston et al. \cite{crowston2012free} present in their study, open source projects lack organized coordination which,
 in the context of our study, means that people do not invest much effort into properly creating tickets in issue tracking 
@@
 inside it. Unfortunately, at the moment, the research community has not come up with such an approach. 
-Vijayakumar et. al \cite{vijayakumar2014much} proposed a method of predicting how much effort is required for fixing 
+Vijayakumar et al. \cite{vijayakumar2014much} proposed a method of predicting how much effort is required for fixing 
 a bug, but after running it on our data, it did not prove successful. After such a technique becomes available, we could 

### 2018-04-22 paper/paper.tex
Fix issues

@@
 Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
-that would improve the overall performance of the development team and, inherently, the company. As there are many 
-fields in a ticket, there are numerous unanswered questions, such as whether stack traces have an influence on the quality
-of a ticket?
+that would improve the overall performance of the development team and, inherently, the company. Considering the many fields of 
+a ticket, there are numerous elements that could influence its quality, such as the presence of stack traces.
 
 In this research paper, we present and discuss our findings after running a quantitative data analysis 
-on over 3200,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
+on over 300,000 tickets taken from more than 38 open source projects. To this aim, we implemented a Go application 
 with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
@@
 
-During the analysis part, we investigate several variables in correlation with \emph{Time-To-Close}, 
-which we define as the \emph{metric of quality}. \emph{Time-To-Close} represents the period of time between the creation 
+For the analysis we investigate several variables in correlation with \emph{Time-To-Close}, 
+which we define as the \emph{indicator of quality}. More specifically, an inverse relationship was assigned between the 
+two: as \emph{Time-To-Close} increases, the quality decreases. \emph{Time-To-Close} represents the period of time between the creation 
 and the closing of a ticket; more specifically, the creation of the ticket is marked when the status of the ticket is set to 
@@
 such as \emph{Fixed}, \emph{Resolved}). \emph{Time-To-Close} is our dependent variable, and as independent variables 
-(i.e. variables controlled in order to test the effects on the dependent variable) we have set a number of ticket fields.
+(i.e. variables controlled in order to test the effects on the dependent variable) we set a number of ticket fields.
 
-In order to provide answers to what factors influence quality in a software ticket, we answer the following seven research 
+In order to provide answers to what factors influence quality in a software ticket, we investigated the following seven research 
 questions in this paper (Section \ref{correlations}):
@@
   a ticket?
-  \item does the presence of stack traces improve the ticket quality?
+  \item does the presence of stack traces reduce \emph{Time-To-Close}?
   \item does the presence of steps to reproduce reduce the \emph{Time-To-Close}?
@@
   \item does the total number of words in summary and description have an impact on \emph{Time-To-Close}?
-  \item does the number of grammar errors in summary, description and comments have an effect on the quality of a ticket?
+  \item does the number of grammar errors in summary, description and comments have an effect on \emph{Time-To-Close}?
   \item does a positive or negative ticket influence its \emph{Time-To-Close}?
@@
 
-In this section we will present what are the state-of-the art studies in the issue/ticket quality 
-field. More specifically, we will look at research papers that investigated what makes for a valuable ticket, 
-how can one extract structured/unstructured data from tickets (e.g. stack traces), ticket duplication and its 
+In this section we will present some of the state-of-the art studies in the issue/ticket quality 
+field. More specifically, we will look at research papers that investigated what makes for a high quality ticket, 
+how one can extract structured/unstructured data from tickets (e.g. stack traces), ticket duplication and its 
 positive and negative outcomes, quality of modern issue tracking systems as well as automating the process 
@@
 and severity. They conclude that not only readability in the textual fields of a ticket
-influence the \emph{Time-To-Close}, but also that the presence of attachments and 
-the number of comments have a clear effect on the duration of triaging. On the 
+influences the \emph{Time-To-Close}, but also that the presence of attachments and 
+the number of comments have a clear lowering effect on the duration of triaging. On the 
 other hand, the patch count and other similar fields did not provide significant 
@@
 
-However, there are other types on information typically included in software tickets 
+However, there are other types of information typically included in software tickets 
 which might prove beneficial for developers and subsequently improve the ticket quality.
-One such type is stack traces and Schroter et al. \cite{schroter2010stack} analyse how 
-quickly tickets are closed when they either have stack traces included in their fields 
+One such type is stack traces - Schroter et al. \cite{schroter2010stack} analyse how 
+quickly tickets are closed depending on whether they have stack traces included in their fields 
 (e.g. description) or not. They collected their data from the Eclipse project using 
@@
 The authors collected large amounts of data from the Eclipse open source project and ran
-various kind of textual and statistical analysis on the data to find answers.
+various kinds of textual and statistical analysis on the data to find answers.
 After the results were computed, they concluded that usually bug duplicates contain 
 information that is not present in the master report (i.e. the original report that was 
-filed). Also, developers also specified that they have often found value in these 
+filed). The developers also specified that they have often found value in these 
 duplicate bug reports and that they can even aid automated triaging techniques.
@@
 the authors investigated whether tickets could be summarized automatically and efficiently. What 
-that implies is that developers would not be required to look at complete tickets comprised 
-of a large number of fields, but rather at a simple summary of a couple of lines 
+that implies is that developers would no longer be required to look at tickets on the whole, comprising of 
+a large number of fields, but rather at a simple summary of a couple of lines 
 encapsulating the whole information. The authors selected the Mozilla, Eclipse, Gnome and KDE 

### 2018-04-22 paper/paper.tex
Finish second page

@@
 a large number of fields, but rather at a simple summary of a couple of lines 
-encapsulating the whole information. The authors selected the Mozilla, Eclipse, Gnome and KDE 
-open source projects and then they asked volunteering university students to annotate 
-the tickets in the issue tracking systems. More specifically, they had to write a summary 
+encapsulating the whole information. The authors selected the Mozilla, Eclipse, GNOME and KDE 
+open source projects and they asked volunteering university students to annotate 
+the tickets in the issue tracking systems. More specifically, they wrote a summary 
 of maximum 250 words using both technical and non-technical terms, depending on their expertise. 
-Then, the study presents Machine Learning algorithms employed to parse these summaries and 
-learn how to efficiently create automated summaries for new bug reports. Afterwards, they asked 
-software developers to rate these auto-generated summaries against the original ones and 
+In parallel, Machine Learning algorithms were also employed to parse these summaries and 
+learn how to efficiently create automated summaries for new bug reports. After both methods had been run, 
+software developers were asked to rate these auto-generated summaries against the original ones; 
 the conclusion was that existing conversation-based extractive summary generators used 
@@
 tracking systems instead. 
-The authors ran a survey on 175 developers from Eclipse, Apache and Mozilla
-Then, they applied a card sort in order to organize the comments into hierarchies to 
+After running a survey on 175 developers from Eclipse, Apache and Mozilla,
+the authors applied a card sort in order to organize the comments into hierarchies to 
 identify common patterns. Their findings can be summarized in the following top seven
@@
 \section{Building the Data Set}\label{building}
-The first step towards building the data set was to create a tool that was able to execute all the commands that we required:
+The first step towards building the data set was to create a tool that was able to execute all the necessary commands:
 fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
@@
     \item it is designed with simplicity in mind, thus making it easy for others who might join the project to read 
-    and understand the codebase; this would prove useful for us as developing the tool further is on our list of future 
-    work items;
+    and understand the codebase; this would prove useful for developing the tool further;
     \item it is a compiled, statically typed language that produces cross-platform executables when building the application;
@@
     running on them and collect even larger number of tickets than what we have collected so far;
-    \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
-    in our case, why it helps us is by allowing access to goroutines, very lightweight threads that can scale even up to 
-    millions; we use this powerful concept while fetching tickets from Jira or storing in the database - at one point, we had 
+    \item it is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
+    in our case, it helps by allowing access to goroutines, very lightweight threads that can scale even up to 
+    millions; we use this powerful concept while fetching tickets from Jira or storing in the database - at one point, there were 
     more than 30,000 goroutines running at the same time.
@@
 
-Throughout the entire application, we tried to apply the UNIX philosophy of creating small applications that do one thing, but 
-do it well. Therefore, we implemented clean and simple packages where we tried to use the standard library as much as possible
+Throughout the entire application, we applied the UNIX philosophy of creating small applications that do one thing, but 
+do it well. Therefore, we implemented clean and simple packages where we used the standard library as much as possible
 so that potential contributors coming to the project would find it easy to start working directly on the code. Also, we designed 

### 2018-04-22 paper/paper.tex
Fix issues and typos

@@
 
-We split our tool into four main commands: \emph{store}, \emph{analyse}, \emph{plot} and \emph{stats}. They all 
-follow the flow shown in figure \ref{fig-eg} and complete the whole application cycle, in the end producing a database 
-of analysed tickets, as well as plots and statistics for investigating correlations, saved on the filesystem.
+We split our tool into four main commands: \emph{store}, \emph{analyse}, \emph{plot} and \emph{stats}. By following the flow shown in 
+Figure \ref{fig-eg} and completing the whole application cycle, a database of analysed tickets is produced,
+as well as plots and statistics for investigating correlations, saved on the filesystem.
 
@@
 slicing the whole set of tickets into multiple smaller arrays to improve performance and reduce the load on the server. We also
-specified to Jira exactly what set of issue fields to return and, while responses were retrieved from the instance,
-we began storing them into our Bolt DB instance.
+specified to Jira exactly what set of issue fields to return and, as responses were retrieved from the instance,
+they were stored into our Bolt DB instance.
 
@@
 projects inside a Jira instance) as the key of the pair and the value is the JSON representation of the ticket. This storage method, in conjunction
-with how simple Bolt is designed, helped us reduce the size of the database significantly. For small databases, 
+with the simplicity of Bolt, helped us reduce the size of the database significantly. For small databases, 
 using RDBMSs (e.g. Postgres, MySQL, Oracle) is not performance critical, but when the data set is large such as in our study, bottlenecks might start affecting 
-the progress of the project. This is mainly due to the structure of how Jira returns the tickets; for example, all issues have comments as 
+the progress of the project. This is mainly due to the structure in which Jira returns the tickets; for example, all issues have comments as 
 a field, consisting of an array of structs with body, author, created time etc. Then, each comment has a changelog history attached to it, 
@@
 link any key-value pair to another. Another major point when we decided to proceed with Bolt was that we did not need to query the data at all 
-as all our processing was too complex to convert the logic into an SQL query.
+as processing was too complex to convert the logic into an SQL query.
 
@@
 \begin{itemize}
-  \item tickets are \emph{High Priority} - the ticket status was marked either Blocker, Critical, Major or High;
-  \item tickets were closed and had a maximum \emph{Time-To-Close} value of 27,000 hours (roughly 3 years) (we added the 
+  \item tickets are \emph{High Priority} - the ticket status marked as either Blocker, Critical, Major or High;
+  \item tickets are closed with a maximum \emph{Time-To-Close} value of 27,000 hours (roughly 3 years) (we added the 
   higher bound as well in order to eliminate outliers retrieved by Jira);
-  \item remove outliers for all categories - some fields for a small number of tickets that had extreme values (e.g. one ticket
+  \item remove outliers for all categories - some fields had extreme values for a small number of tickets (e.g. one ticket
   had over 270,000 comments) introduced by the team behind the project and we needed to exclude them so that the analysis 
-  produced correct results.
+  produced correct results (they were removed as they were skewing the results due to erroneous completion of fields).
 \end{itemize}
@@
 \begin{itemize}
-  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
-  of attachments (e.g. screenshots, archive, code snippets) influence time-to-close the most;
+  \item \emph{attachments} - checks whether attachments influence \emph{Time-To-Close} and also look at what types 
+  of attachments (e.g. screenshots, archive, code snippets) influence \emph{Time-To-Close} the most;
   \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
-  influence the time-to-close of a ticket; the regular expression was adapted after the general guidelines elicited by 
+  influence the \emph{Time-To-Close} of a ticket; the regular expression was adapted after the general guidelines elicited by 
   Bettenburg et al. \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
@@
 In this section we present our results to the research questions we set to answer. We have computed charts for all 
-independent variables using either scatter plots for continuous variables (e.g. number of comments/time-to-close) 
+independent variables using either scatter plots for continuous variables (e.g. number of comments/\emph{Time-To-Close}) 
 or bar charts for categorical variables (e.g. presence of attachments). We also computed statistical analysis for 
@@
 \begin{itemize}
-  \item having attachments reduces time-to-close of a ticket;
-  \item having steps to reproduce reduces time-to-close of a ticket;
-  \item having stack traces reduces time-to-close of a ticket;
-  \item more grammar errors imply increase time-to-close values;
-  \item lower sentiment scores result in increased time-to-close values;
-  \item verbose comments result in increased time-to-close values;
-  \item verbose summary and description imply increased time-to-close values.
+  \item having attachments reduces \emph{Time-To-Close} of a ticket;
+  \item having steps to reproduce reduces \emph{Time-To-Close} of a ticket;
+  \item having stack traces reduces \emph{Time-To-Close} of a ticket;
+  \item more grammar errors imply increase \emph{Time-To-Close} values;
+  \item lower sentiment scores result in increased \emph{Time-To-Close} values;
+  \item verbose comments result in increased \emph{Time-To-Close} values;
+  \item verbose summary and description imply increased \emph{Time-To-Close} values.
 \end{itemize}
@@
 As it can be seen, various types of attachments can produce completely different \emph{times-to-close}. For 
-tickets with archive we can see the longest time-to-close mean while tickets having text attachments are at 
+tickets with archive we can see the longest \emph{Time-To-Close} mean while tickets having text attachments are at 
 the other end of the spectrum. The smallest mean is for other attachments, which is represented by any file 
@@
 We assume that image attachments are screenshots attached to the ticket in order to help developers see and 
-subsequently reproduce the bug. Thus, we can clearly see that the difference between the means of time-to-close 
+subsequently reproduce the bug. Thus, we can clearly see that the difference between the means of \emph{Time-To-Close} 
 for tickets without attachments and tickets with screenshots is significantly in favor of the latter. This can 
@@
 Another insightful result is the fact that having text, config and spreadsheet attachments significantly 
-reduces the time-to-close for the ticket. This can imply that developers find value in various steps to reproduce, 
+reduces the \emph{Time-To-Close} for the ticket. This can imply that developers find value in various steps to reproduce, 
 config values used by users when the bug encountered or data in a spreadsheet format (e.g. csv) that can be 
-found in such files and helps them lower the time-to-close for the ticket.
+found in such files and helps them lower the \emph{Time-To-Close} for the ticket.
 
 On the other hand, having no attachments does not necessarily mean that the ticket will get closed after 
-a longer period of time. As it can be seen in the figure, the mean time-to-close value for tickets without 
+a longer period of time. As it can be seen in the figure, the mean \emph{Time-To-Close} value for tickets without 
 attachments is somewhat neutral in the entire data set.
@@
 provide the most value to the software project would be if issue tracking systems would make explicit to the reporters 
-that uploading a screenshot or a code snippet can help reduce the time-to-close for the ticket.
+that uploading a screenshot or a code snippet can help reduce the \emph{Time-To-Close} for the ticket.
 
@@
 
-As it can be shown in the figure, having steps to reproduce can significantly reduce the time-to-close 
+As it can be shown in the figure, having steps to reproduce can significantly reduce the \emph{Time-To-Close} 
 for the ticket. Even though the data collected does not have such many tickets with steps to reproduce 
@@
 Thus, the answer to our research question is that the presence of steps to reproduce in tickets 
-has a positive influence on the time-to-close. One solution that we propose for maximizing their benefit 
+has a positive influence on the \emph{Time-To-Close}. One solution that we propose for maximizing their benefit 
 is that issue tracking systems should include hints on the ticket creation form specifying that 
@@
 As shown in Figure \ref{stack_traces}, we can see that the presence of exception stack traces can 
-reduce the time-to-close of a ticket in orders of magnitude. This could imply that stack traces help 
+reduce the \emph{Time-To-Close} of a ticket in orders of magnitude. This could imply that stack traces help 
 developers working on the project localise the code that is running exceptions
@@
 A correlational analysis ran on all 201,786 tickets, however, releaved a weak positive relationship with $r = 0.271$ and $p < 0.01$. 
-This implies a statistically significant finding - as the number of comments increases, the time-to-close value of the ticket also increases.
+This implies a statistically significant finding - as the number of comments increases, the \emph{Time-To-Close} value of the ticket also increases.
 
@@
 grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
-tickets (i.e. increased time-to-close).
+tickets (i.e. increased \emph{Time-To-Close}).
 
@@
 
-On the other side of the spectrum, having a more positive score leads to reduced time-to-close values for tickets. Calefato et al. 
+On the other side of the spectrum, having a more positive score leads to reduced \emph{Time-To-Close} values for tickets. Calefato et al. 
 \cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
@@
 We manager to answer all seven research questions and find factors that can posittively or 
-negatively affect the time-to-close value of a ticket. All of our results are statistically significant and we can summarise 
+negatively affect the \emph{Time-To-Close} value of a ticket. All of our results are statistically significant and we can summarise 
 them as follows:
 \begin{itemize}
-  \item the presence of steps to reproduce reduces the time-to-close for a ticket;
-  \item the presence of stack traces reduces the time-to-close for a ticket;
-  \item the presence of attachments reduces the time-to-close for a ticket - more specifically tickets with screenshots, 
+  \item the presence of steps to reproduce reduces the \emph{Time-To-Close} for a ticket;
+  \item the presence of stack traces reduces the \emph{Time-To-Close} for a ticket;
+  \item the presence of attachments reduces the \emph{Time-To-Close} for a ticket - more specifically tickets with screenshots, 
   config files or text files help tickets get closed quicker than those without attachments;
-  \item higher numbers of grammar errors imply increased time-to-close values;
-  \item higher sentiment scores imply reduced time-to-close values for a ticket;
-  \item higher numbers of words in comments imply increased time-to-close values for a ticket;
-  \item higher number of words in description and summary increase the time-to-close values for tickets.
+  \item higher numbers of grammar errors imply increased \emph{Time-To-Close} values;
+  \item higher sentiment scores imply reduced \emph{Time-To-Close} values for a ticket;
+  \item higher numbers of words in comments imply increased \emph{Time-To-Close} values for a ticket;
+  \item higher number of words in description and summary increase the \emph{Time-To-Close} values for tickets.
 \end{itemize}

### 2018-04-22 paper/paper.tex
Fix issues

@@
 have a maximum rate of  100 requests per second, thus we needed to conform to their guidelines and restrict our 
-application to send more than allowed, otherwise our IP addresses could have been blacklisted. We also did not want 
-to exceed our free trial credits, therefore we calculated in advance how many requests we had available and computed 
+application not to send more than allowed, otherwise our IP addresses could have been blacklisted. The number of free trial 
+credits was limited, therefore we calculated in advance how many requests we had available and computed 
 scores only for those tickets.
@@
 already available there. Moreover, for analysis depending on third party services such as the Google Cloud Platform 
-Natural Processing Language API, we would incur costs, thus having everything saved in the database and running the 
-analysis only if the value has not been already computed allowed us to investigate the tickets without exceeding the 
+Natural Processing Language API, we would incur costs; thus having everything saved in the database and running the 
+analysis only if the value had not been already computed allowed us to investigate the tickets without exceeding the 
 free trial credits.
 
-\subsection{Plot and Statistical Tests}
+\subsection{Plots and Statistical Tests}
 
-Afterwards, we have created two extra commands for automatically generating plots (i.e. scatter plots and bar charts) and 
+Next, we created two extra commands for automatically generating plots (i.e. scatter plots and bar charts) and 
 running statistical tests on the collected data.
@@
 For plotting the data, we first connect again to the Bolt database instance and then filter out only the issues that have 
-the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance). 
+the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance; even though 
+we passed a filter for not fetching tickets still marked as Open, there was a small number erronously retrieved by Jira). 
 In order to compute correct results, we run the same checks on issues as the ones listed in the analyse command (e.g. plot 
-only tickets of high priority). Afterwards, we either save scatter plots or bar charts to disk presenting correlations 
+only tickets of high priority). Afterwards, we save either scatter plots or bar charts to disk presenting relationships 
 between all the variables we tested.
 
-In terms of technology used for plotting the data, we have used a library called go-chart \cite{go-chart} created by 
-Will Charczuk. It is an extensible library with a focus on extensability - it does not provide the end user a large number 
+In terms of technology used for plotting the data, we used a library called go-chart \cite{go-chart} created by 
+Will Charczuk. It is an extensible library with a focus on extensibility - it does not provide the end user a large number 
 of default options, but rather let him/her extend their graphs as much as it is needed (e.g. add specific labels for axes, 
@@
 tests: Welch's T Test \cite{welch1947generalization} for analysing categorical data (e.g. has/does not have attachments)
-and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. how do different 
-grammar correctness scores change \emph{Time-To-Close}). For computing Spearman R Tests we made use of a simple 
+and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. grammar correctness score 
+based on number of grammatical mistakes). For computing Spearman R Tests we made use of a simple 
 statistics library created by Damian Gryski called onlinestats \cite{onlinestats}, while for Welch T Tests we created our 
@@
 
-They have both been created with extensability in mind - we believe that in the future work we proposed to conduct on the 
-project, we might need to use other statistical tests as well, such as Mann-Whitney U tests \cite{mann1947test}. Also, before
+They have both been created with extensibility in mind. Also, before
 we ran both statistical tests and the plotting command, we tested them thoroughly and checked whether the libraries compute 

### 2018-04-22 paper/paper.tex
Finish 6th page

@@
 summary/description editing etc. What made them useful for our study was that we needed to see when tickets were marked closed and, 
-as Jira does not provide this in a separate field, we looped through all changelog history items and saved when the transition to 
+as Jira does not provide this in a separate field, we looped through the changelog history items and saved when the transition to 
 Closed or a similar status was made.
@@
 There are other fields that can be configured inside Jira, including custom fields, but we did not collect them as they would not 
-have been helpful in conducting the analysis. However, in addition to the fields we saved, we also stored grammar correctness scores, 
+have been relevant for the analysis. However, in addition to the fields we saved, we also stored grammar correctness scores, 
 sentiment scores, whether they have steps to reproduce, if stack traces are present and number of words in comments, summary and description. 
@@
 Go to Python and Ruby \cite{apache_projects}. Moreover, in terms of contributors, the projects we selected range from small teams of people
-such as Tika to large numbers of developers spread across the globe, such as the people working on Kafka. We came to this final number 
-and range of tickets and projects because of a couple of reasons: 
+such as Tika to large numbers of developers spread across the globe, such as Kafka. We came to this final number 
+and range of tickets and projects due to the following reasons: 
 \begin{itemize}
@@
 \begin{itemize}
-  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
+  \item out of the 303,138 tickets, 236,383 tickets were closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
   fetched them from the Jira instance;
@@
   data (including steps to reproduce) from tickets in order to create a regular expression for capturing them;
-  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et al. 
-  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
-  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
+  \item 1,942 tickets have Java stack traces - we applied the technique described by Bettenburg et al. 
+  \cite{bettenburg2008extracting} for extracting structured data from bug reports;
   \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
-  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
+  they were computed using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
   \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description

### 2018-04-22 paper/paper.tex
Finish 7th page

@@
   \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
-  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
+  and comments) - they were calculated using Google Cloud Platform Natural Language Processing APIs.
 \end{itemize}
@@
 All these numbers are also stored inside the database in a different bucket for easier access in the future. Moreover, the statistical 
-tests we ran on the tickets are saved as well in the database.
+tests that were run on the tickets are saved as well in the database.
 
@@
 
-In this section we present our results to the research questions we set to answer. We have computed charts for all 
+In this section we present our results to the research questions we set to answer. We computed charts for all 
 independent variables using either scatter plots for continuous variables (e.g. number of comments/\emph{Time-To-Close}) 
-or bar charts for categorical variables (e.g. presence of attachments). We also computed statistical analysis for 
+or bar charts for categorical variables (e.g. presence of attachments/\emph{Time-To-Close}). We also computed statistical analysis for 
 all variables to test their significance and rank correlation coefficient and we will present each of them in their 
@@
 
-The answers to our research questions are all statistically significant and they can summarised as follows:
+The answers to our research questions are all statistically significant and they can be summarised as follows:
 \begin{itemize}
@@
   \item having stack traces reduces \emph{Time-To-Close} of a ticket;
-  \item more grammar errors imply increase \emph{Time-To-Close} values;
+  \item more grammar errors increase \emph{Time-To-Close} values;
   \item lower sentiment scores result in increased \emph{Time-To-Close} values;
   \item verbose comments result in increased \emph{Time-To-Close} values;
-  \item verbose summary and description imply increased \emph{Time-To-Close} values.
+  \item verbose summary and description increase \emph{Time-To-Close} values.
 \end{itemize}
@@
 Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
-snippets written in Java to tar archives. We have analyzed all tickets that were both of high priority tickets and
-were marked as Closed by the time we collected the data. Then we split all these tickets into two main categories: 
+snippets written in Java to tar archives. We analysed all tickets that were both of high priority and
+were closed by the time we had collected the data. Then we split all these tickets into two main categories: 
 with attachments and without attachments. Furthermore, the tickets that were marked as having attachments were split 
@@
 Using the plot package in our Go tool, we automatically generated the bar chart shown in Figure \ref{attachments}. 
-As it can be seen, various types of attachments can produce completely different \emph{times-to-close}. For 
-tickets with archive we can see the longest \emph{Time-To-Close} mean while tickets having text attachments are at 
+As it can be seen, various types of attachments produce completely different \emph{times-to-close}. For 
+tickets with archive we can see the longest \emph{Time-To-Close} mean while tickets with text attachments are at 
 the other end of the spectrum. The smallest mean is for other attachments, which is represented by any file 
@@
 Another insightful result is the fact that having text, config and spreadsheet attachments significantly 
-reduces the \emph{Time-To-Close} for the ticket. This can imply that developers find value in various steps to reproduce, 
-config values used by users when the bug encountered or data in a spreadsheet format (e.g. csv) that can be 
-found in such files and helps them lower the \emph{Time-To-Close} for the ticket.
+reduces the \emph{Time-To-Close} for the ticket. For example, when a config file is present, it might contain 
+several environment variables that would help developers recreate the bug quicker. Similarly, a markdown file 
+might have logging output which potentially directs engineers towards fixing the issue faster.
 
@@
 
-However, we need to take into consideration tickets that have code attachments which are a \emph{thread to validity}. 
+However, we need to take into consideration tickets that have code attachments which are a \emph{threat to validity}. 
 When a snippet of code is attached, it might result in more complex tickets due to developers spending more time on 
@@
 A Welch T Test was computed to test the difference between tickets with attachments and those 
-without attachments. The analysis revealed significant difference with $p > 0.01$ with an
+without attachments. The analysis revealed significant difference with $p < 0.01$ with an
 average of $1380.551$ hours for tickets with attachments and an average of $3180.882$ hours
@@
 Thus, our analysis shows that having attachments in most formats, ranging from markdown files to PNG screenshots 
-and snippets of code, can help developers solve the tickets faster. We believe that the solution of making attachments
-provide the most value to the software project would be if issue tracking systems would make explicit to the reporters 
-that uploading a screenshot or a code snippet can help reduce the \emph{Time-To-Close} for the ticket.
+and snippets of code, can help developers solve the tickets faster. We believe that a solution to maximising the value 
+of a ticket through attachments lies in issue tracking systems making it explicit to the reporters that uploading a screenshot 
+or a code snippet could help reduce the \emph{Time-To-Close} for the ticket.
 

### 2018-04-23 paper/paper.tex
Finish 8th and 9th page

@@
 to reproduce in either the description field or in any of the comments. We looked in total at 201,786 tickets 
-among which 31,732 tickets had steps to reproduce and 170,054 did not have.
+among which 39,988 tickets had steps to reproduce and 161,798 did not.
 
-As it can be shown in the figure, having steps to reproduce can significantly reduce the \emph{Time-To-Close} 
-for the ticket. Even though the data collected does not have such many tickets with steps to reproduce 
-(39,988 compared to the total number of 238,286 closed tickets), it is still a valuable finding which shows 
+As it is shown in the figure, having steps to reproduce significantly reduces the \emph{Time-To-Close} 
+for the ticket. Even though the data collected does not have many tickets with steps to reproduce 
+(39,988 compared to the total number of 201,786 tickets), it is still a valuable finding which shows 
 that steps to reproduce are indeed a quality factor for software tickets.
@@
 bug occurs only on Linux and the developer is running MacOS, but the reporter did not specify his/her 
-operating system in the ticket), the developer might need to contact the reported either directly or 
-through commenting on the issue. What this implies is waiting time until the reporter comes back on the 
-issue tracking system or sees the notification that he/she received a new message, which subsequently makes 
-the ticket remain open for a longer period of time.
+operating system in the ticket), the developer might need to contact the reporter either directly or 
+through commenting on the issue. This consequently implies a waiting time until the reporter comes back on the 
+issue tracking system or sees the notification that he/she received a new message, which subsequently causes 
+the ticket to remain open for a longer period of time.
 
@@
 and those without steps to reproduce. The analysis revealed significant difference with 
-$p < 0.01$ with an average of $1596.714$ for tickets with steps to reproduce and an average of 
-$2609.142$ for tickets without steps to reproduce.
+$p < 0.01$ with an average of $1596.714$ hours for tickets with steps to reproduce and an average of 
+$2609.142$ hours for tickets without steps to reproduce.
 
 Thus, the answer to our research question is that the presence of steps to reproduce in tickets 
-has a positive influence on the \emph{Time-To-Close}. One solution that we propose for maximizing their benefit 
-is that issue tracking systems should include hints on the ticket creation form specifying that 
-steps to reproduce should be included as developers would be able to fix the bug faster. Moreover, 
+has a positive influence on the \emph{Time-To-Close}. One solution that we propose for maximising their benefit 
+is that issue tracking systems require steps to reproduce, or at least indicate on the ticket creation form, 
+that adding them would aid developers fix the bug faster. Moreover, 
 issue tracking systems could also automatically add a new system field (like summary or description) 
@@
 For this analysis, we only looked at tickets of high priority, closed and the project they correspond 
-is written in Java. In total, we investigated looked at We then ran a complex regular expression derived from the works of Bettenburg et al. 
+is written in Java. We then ran a complex regular expression derived from the works of Bettenburg et al. 
 \cite{bettenburg2012using} and Moreno et al. \cite{moreno2014use} and collected all the tickets that have 
-stack traces. In the end, we got a total number of 256 tickets that had at least an exception stack trace 
+stack traces. In the end, we got a total number of 1,942 tickets that had at least an exception stack trace 
 attached in either summary, description or any of the comments.
@@
 do not have stack traces. The analysis revealed significant difference with $p < 0.01$ with an
-average of $1475.074$ for tickets with stack traces and an average of $2441.877$
+average of $1475.074$ hours for tickets with stack traces and an average of $2441.877$ hours
 for tickets without them.
@@
 was performed at the end of each ticket's lifecycle. We ran our comments analysis on 201,786 tickets among which 
-113,344 had comments and 88,442 did not have any comments. What we calculated as being total number of words inside comments 
+113,344 had comments and 88,442 did not have any comments. What we calculated as number of words inside comments 
 is all the words inside all comments corresponding to a ticket summed up.
 
-In Figure \ref{comments} we present the correlations between the total number of words in comments per ticket and 
-the corresponding Time-To-Close for that ticket. We can observe in the scatter plot that most tickets tend to 
+In Figure \ref{comments} we illustrate the relationship between the total number of words in comments per ticket and 
+the corresponding \emph{Time-To-Close}. We can observe in the scatter plot that most tickets tend to 
 have up to around 3,200 words in total. However, there are tickets that have a total number of words as high as 
@@
 1 to 1,600 total comment words per ticket (76,633 tickets) and in this slice of tickets, the trend is descending.
-We did not generate the plot containing only these values because there would still be 36,711 tickets left out.
+We did not generate the plot containing solely these values because there would still be 36,711 tickets left out. 
+Therefore, the curve is skewed to the right, although the bulk of tickets that dictate the trend, are on the left side.
 
-A correlational analysis ran on all 201,786 tickets, however, releaved a weak positive relationship with $r = 0.271$ and $p < 0.01$. 
-This implies a statistically significant finding - as the number of comments increases, the \emph{Time-To-Close} value of the ticket also increases.
+A correlational analysis run on all 201,786 tickets, however, releaved a weak positive relationship with $r = 0.271$ and $p < 0.01$. 
+This implies a statistically significant finding - as the number of comments increases, the \emph{Time-To-Close} value of the ticket 
+also increases.
 
 Even though this might be surprising at first, we need to analyse the possible context where such large 
-number of words in comments occur. What if the bug was so hard to reproduce that the developers needed to 
+number of words in comments occur. What if the bug was so difficult to reproduce that the developers needed to 
 ask more than one user how they experienced the issue in the tool? Another case might be that even though 
@@
 in software tickets in relation to communication activities surrounding the project. Another possible explanation 
-for having increased number of comments increase the Time-To-Close value and, thus, decrease quality, is that 
-having many comments or very verbose comment can lead to more difficult information extraction. On the other 
-hand, if there would be a light discussion, the developers would be able to quickly analyse all the comments 
+for having increased number of comments increase the \emph{Time-To-Close} value and, thus, decrease quality, is that 
+having many comments or very verbose comments can lead to more difficult information extraction. On the other 
+hand, if there was a light discussion, the developers would be able to quickly analyse all the comments 
 and collect whatever is necessary to resolve the ticket.
 
-One possible solution that we propose to this correlation is to have the ability to limit the number of 
+One possible solution that we propose to this manifested trend is to have the ability to limit the number of 
 comments per ticket. As to our knowledge, one cannot do this in neither Jira nor Bugzilla. However, if it were 
 possible, we believe that this might help developers find the information they need quicker. But what happens 
-if the treshold is reached and there is still a need for clarifying certain aspects? We believe that having 
+if the threshold is reached and there is still a need for clarifying certain aspects? We believe that having 
 a button redirecting anyone still interesting in commenting on the ticket to a messaging tool, such as 
-Slack, would be beneficial for the project overall. Thus, if they were redirected to let's say Slack, a small 
-tool could automatically be run that creates a new channel specifically for that ticket with the name set 
+Slack, would be beneficial for the project overall. Thus, if they were redirected to Slack, a small 
+tool could automatically be run that created a new channel specifically for that ticket with the name set 
 to the unique ticket key (e.g. LUCENE-2901). We believe that such a solution could aid both developers in 
-completing tasks quicker but also end users for feeling more involved and valuable to the project.
+completing tasks quicker but also end users to feel more involved and valuable to the project.
 
@@
   \end{center}
-  \caption{\label{fields}Time-To-Close versus summary and description word count.}
+  \caption{\label{fields}Summary and Description Complexity Analysis.}
 \end{figure}
@@
 
-The Figure shows a very similar correlation to the one for comments complexity - it seems that as the number of words 
+The figure shows a very similar correlation to the one for comments complexity - graphically, it seems that as the number of words 
 in summary and description increases, the Time-To-Close will decrease. This is true for the majority of the tickets 
@@
 
-However, a correlational analysis ran on all 201,786 tickets revealed a weak positive relationship with $r = 0.178$ and $p < 0.01$. 
-This implies both that our results are statistically significant and also that as number of words in summary and description increase, 
+However, a correlational analysis run on all 201,786 tickets revealed a weak positive relationship with $r = 0.178$ and $p < 0.01$. 
+This implies both that our results are statistically significant and also that as the number of words in summary and description increases, 
 the Time-To-Close increases, thus the quality of the ticket decreases.

### 2018-04-23 paper/paper.tex
Finish 10th page

@@
 Description, on the other hand, even though it is made to be a more detailed summary of the report, it should still be
-in some reasonable parameters. During our analysis process, we identified more than 50 tickets having descriptions 
+within some reasonable parameters. During our analysis process, we identified more than 50 tickets having descriptions 
 with more than 4,000 words. Even though they included various types of information, including steps to reprodce, 
@@
   they might also be able to provide an estimate for the difficulty of the task; however, that should be stored in the 
-  Jira system field called \"Story Points\";
+  Jira system field called Story Points;
   \item the user might also want to provide excerpts of code or previous discussions with other end users/developers; 
@@
 
-A solution for this issue could be the freedom of easily selecting the total number of words allowed for summary and 
+A solution for this issue could be a setting to cap the total number of words allowed for summary and 
 description. Even though this is possible with Jira, the process of configuring it is not trivial, thus many 
@@
 
-Through calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
+By calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
 managed to calculate the total number of grammar errors in summary, description and comments for a total number 
@@
   \item it can detect the wrong usage of a verb tense in a specific context;
-  \item it can flag wrong conjugations of verbs;
+  \item it can flag wrong conjugations of verbs.
 \end{itemize}
@@
 
-However, we can not automatically change this through automation like the solutions we presented in the previous 
+However, we can not change this through automation like the solutions we presented in the previous 
 analysis types. We cannot call, for example, the Bing Spell Check API every couple of seconds on the text the user 
-is inputting in the ticket as the costs would become unbearable very soon. Thus, what can be done to fix this? It is, 
-after all, in the human nature to make mistakes, and typing is no exception. If we, for example, have some hint or a rule
-in the code of conduct for the project stating that everything should be 100\% gramatically correct, many reporters not 
-having English as their primary language would feel unwelcomed and they might not get involved in the project anymore.
+is inputting in the ticket as the costs would become unbearable very rapidly. Thus, what can be done to fix this? It is, 
+after all, in the human nature to make mistakes, and mistyping is no exception. If we, for example, have some hint or a rule
+in the code of conduct for the project stating that everything should be 100\% gramatically correct, many reporters with a 
+different language than English as their primary one would feel unwelcome and they might not get involved in the project anymore.
 

### 2018-04-23 paper/paper.tex
Finish analysis section

@@
 a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
-there are open source libraries that can help creating and employing the algorithms, such as TensorFlow, 
-we would still have needed tickets where we defined what do we mean by positive/negative tickets, as well as
+there are open source libraries that can help with creating and employing the algorithms, such as TensorFlow, 
+we would still have needed tickets where we defined what is meant by positive/negative tickets, as well as
 manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
@@
 
-After we concatenated summaries, descriptions and all the comments for every ticket, we started sending our 
+After we concatenated summaries, descriptions and all the comments for every ticket, we sent our 
 requests to Google and we plotted the data shown in Figure \ref{sentiment}. A correlational analysis revealed a 
@@
 
-We can see in the Figure that neutral scores (i.e. between -0.42 and 0.42) show rather neutral results, which 
-was expectable: this most probably implies that the discussions and descriptions for these tickets revolved 
-completely around the ticket and nothing else.
+We can see in Figure \ref{sentiment} that neutral scores (i.e. between -0.42 and 0.42) correspond to rather 
+average \emph{Times-To-Close}, as was expected.
 
-However, as the sentiment decreases, we can clearly observe that the sentiment scores increase significantly. 
-This might signify that once the discussion becomes \"heated\", the developers might lose interest in solving 
-the task anymore. Also, rude language might be a driver for increased Times-To-Close because when developers are 
-answering questions from the reporters (or vice versa), the other person might become rude or unpolite, which can 
-make them feel unwelcomed and start to lose interest in helping the project anymore.
+However, as the sentiment decreases, we can clearly observe that the \emph{Time-To-Close} increases significantly. 
+This might signify that once the discussion becomes "heated", the developers might lose interest in solving 
+the task anymore. Also, rude language might be a driver for increased \emph{Times-To-Close}: the engineer might become 
+rude or impolite, which can make the interlocutor feel unwelcome and start to lose interest in helping the project anymore.
 
@@
 sentiment analysis tool running in the background as the user is typing in any text box. If they reach a certain low 
-treshold and it is believed that they are becoming rude or unpolite, there could be a warning/pop-up on the screen advising 
-them to not do that as it wouldn't help any party, but rather try to be polite, engaging and friendly. One other solution
+threshold and it is believed that they are becoming rude or unpolite, there could be a warning/pop-up on the screen advising 
+them against submitting the comment and encouraging them to be polite, engaging and friendly. One other solution
 is a much more cost-effective one, but less efficient - the issue tracking system administrators could include a section 

### 2018-04-23 paper/paper.tex
Fix issues and typos

@@
 when we were first prototyping the application, but we decided to proceed exclusively with Jira mainly because 
-the APIs proved to be more reliable and also versatile in terms of what data you could collect. Another 
-reason was that we were time retricted, thus we wanted to have first a well tested and stable solution for Jira and 
+the APIs proved to be more reliable and also versatile in terms of what data could be collected. Another 
+reason was that we were time restricted, thus we wanted to have first a well tested and stable solution for Jira and 
 only after add support for other issue tracking systems. However, we already prepared for other potential systems by 
@@
 There is also room for future work in terms of the data collected. Even though the database we collected 
-is large, there is never enough tickets to analyse. Thus, the store command of the tool could be run against 
+is large, there are never too many tickets to analyse. Thus, the store command of the tool could be run against 
 other Jira instances apart from Apache's and collect tickets from other projects, thus improving the diversity 
@@
 
-Another aspect that could be improved is having access to funds in order to buy Google Cloud Platform credits. This 
-would be required to use the Natural Language Processing APIs on large amounts of data. We used the credits provided 
+Another aspect that could be improved is allocating a budget for Google Cloud Platform credits. This 
+would be required for running the Natural Language Processing APIs on large amounts of data. We used the credits provided 
 in the free trial but quickly ran out completely after only 160,000 tickets. Also, credits on Microsoft Azure would 
@@
 
-We manager to answer all seven research questions and find factors that can posittively or 
+We managed to answer all seven research questions and find factors that can positively or 
 negatively affect the \emph{Time-To-Close} value of a ticket. All of our results are statistically significant and we can summarise 
@@
 thank you, Tim, for all the support, kindness and advice you have given me throughout this academic year. I would 
-also like to thank you for being the lecturer who has taught me the most throughout all my years at the university
-and whose advice and ideas I have applied at all my work places and my personal projects.
+also like to thank you for being the lecturer who has taught me the most throughout all my years at university
+and whose advice and ideas I have applied in all my work places and my personal projects.
 
-The next huge thank you would have to go to my parents, the most amazing family in the world! Without them I would 
-not be here and I wouldn't have had anything of what I have now, both personally and professionally. 
-I will always treasure the unconditional support you have always offered me! Thank you for being my parents, Mom and Dad!
+The next huge thank you would have to go to my parents! Without them I would 
+not be here and I wouldn't have accomplished so much, both in my personal and professional lives. 
+I will always treasure the unconditional support you have offered me! Thank you for being the parents that you are!
 
-And last but not least, I want to thank my partner in \"crime\" and in life, Corina! Without her, I would not be who I 
+And last but not least, I want to thank my partner in "crime" and in life, Corina! Without her, I would not be who I 
 am today. You have been with me through thick and thin, in both bad moments (such as the endless nights working 
-on ticket statistics) and best moments in my life! Thank you for everything! I will always love you!
+on ticket statistics) and best moments in my life! Thank you for everything!
 

### 2018-04-23 paper/paper.tex
Fix valuable occurrences

@@
 managing their progress throughout complex projects. However, there
-are few studies that investigate what makes for a high quality,
-valuable ticket. This can lead to multiple issues in a company, such as 
-increased communication friction between developers and end users filing bug
+are few studies that investigate what makes for a high quality ticket. This can lead to 
+multiple issues in a company, such as increased communication friction between developers and end users filing bug
 reports, as well as increased overall costs due to waste of development effort. 
@@
 
-Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
+Therefore, there is a need in the community to find the answer to what makes for a high quality software ticket 
 that would improve the overall performance of the development team and, inherently, the company. Considering the many fields of 
@@
 The study of Bettenburg et al. \cite{bettenburg2008makes} showed what 
-makes for a valuable bug report through qualitative analysis. 
+makes for a high quality bug report through qualitative analysis. 
 After conducting interviews with over 450 developers, Bettenburg et al. concluded that one of the main factors
@@
 identify common patterns. Their findings can be summarized in the following top seven
-suggestions:
-  \begin{itemize}
-    \item create differentiation between bug report difficulty levels between 
-    novices and experiences reporters;
-    \item encourage users to input as much information as possible;
-    \item add ability to merge tickets when needed;
-    \item recognise and reward valuable bug reporters;
-    \item integrate reputation into user profiles to mark experienced reporters;
-    \item to be able to easily and expressively search through tickets.
-  \end{itemize}
+suggestions: create differentiation between bug report difficulty levels between 
+novices and experiences reporters, encourage users to input as much information as possible, 
+add ability to merge tickets when needed, recognise and reward valuable bug reporters, integrate 
+reputation into user profiles to mark experienced reporters and ensure the ability to expressively search through tickets.
 
@@
 The conclusions they drew from running the evaluation process were rather 
-interesting:
-  \begin{itemize}
-    \item terms such as segfault, deadlock, crash, hand or memory typically indicate
-      a severe bug;
-    \item when analyzing the textual description they found that using simple
+interesting: terms such as segfault, deadlock, crash, hand or memory typically indicate
+a severe bug, when analyzing the textual description they found that using simple
 one line summaries resulted in less false positives and increased precision
-      levels;
-    \item the classifier needs a large number of tickets in order to predict correctly;
-    \item depending on how well a software project is modularised, one can 
+levels, the classifier needs a large number of tickets in order to predict correctly, 
+depending on how well a software project is modularised and, lastly, one can 
 use a predictor per module rather than a universal one.
-  \end{itemize}
 
@@
 score from textual information. These algorithms need to be trained on very large data sets in order to 
-produce valuable results. Moreover, we would have also needed an already annotated data set, which means 
+produce valid results. Moreover, we would have also needed an already annotated data set, which means 
 a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
@@
 
-We strongly believe that having a positive sentiment score for tickets is valuable for absolutely everyone: the company
+We strongly believe that having a positive sentiment score for tickets is beneficial for everyone: the company
 behind the projects sees increased overall performance and productivity, developers feel better working in the team or

### 2018-04-23 paper/paper.tex
Add new image scales and fix issues
Finish whole paper completely

@@
 
+In this section, several state-of-the art research studies revolving around software tickets and their surrounding 
+environment were presented. The findings and techniques summarised proved useful for our own research, 
+helping us build the data set as we will elaborate in the following section.
+
 \begin{figure*}
 \begin{center}
-\includegraphics[width=\textwidth]{images/flow.pdf}
+\includegraphics[scale=0.80]{images/flow.pdf}
 \end{center}
@@
 
-\vskip30pt
-
 \subsection{Attachments}
@@
   \begin{center}
-  \includegraphics[scale=0.25]{images/attachments.png}
+  \includegraphics[scale=0.18]{images/attachments.png}
   \end{center}
@@
 
-\vskip18pt
-
 \subsection{Steps to Reproduce}
@@
   \begin{center}
-    \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
+    \includegraphics[scale=0.18]{images/steps_to_reproduce.png}
   \end{center}
@@
 
-\vskip12pt
-
 \subsection{Stack Traces}
@@
   \begin{center}
-    \includegraphics[scale=0.25]{images/stack_traces.png}
+    \includegraphics[scale=0.18]{images/stack_traces.png}
   \end{center}
@@
   \begin{center}
-    \includegraphics[scale=0.25]{images/comment_complexity.png}
+    \includegraphics[scale=0.18]{images/comment_complexity.png}
   \end{center}
@@
   \begin{center}
-    \includegraphics[scale=0.25]{images/fields_complexity.png}
+    \includegraphics[scale=0.18]{images/fields_complexity.png}
   \end{center}
@@
 
-\vskip10pt
-
 \subsection{Grammar Correctness}
@@
   \begin{center}
-    \includegraphics[scale=0.25]{images/grammar_correctness.png}
+    \includegraphics[scale=0.18]{images/grammar_correctness.png}
   \end{center}
@@
   \begin{center}
-    \includegraphics[scale=0.25]{images/sentiment_analysis.png}
+    \includegraphics[scale=0.18]{images/sentiment_analysis.png}
   \end{center}

### 2018-04-23 paper/paper.tex
Fix issue with text overflow
FINAL PAPEEER

@@
 on over 300,000 tickets taken from more than 38 open source projects. To this aim, we implemented a Go application 
-with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
-from a Jira instance, analyze them, generate plots and run statistical tests.
+with multiple commands (i.e. store, analyse, plot, statistics) that can automatically fetch any number of tickets 
+from a Jira instance, analyse them, generate plots and run statistical tests.
 
@@
 
-Another research paper that strenghtens the argument that readability is a quality 
+Another research paper that strengthens the argument that readability is a quality 
 factor in software tickets is the one presented by Hooimeijer et al. \cite{hooimeijer2007modeling}.
@@
 the request or bug being reported. In the study conducted by Rastkar et al. \cite{rastkar2010summarizing}, 
-the authors investigated whether tickets could be summarized automatically and efficiently. What 
+the authors investigated whether tickets could be summarised automatically and efficiently. What 
 that implies is that developers would no longer be required to look at tickets on the whole, comprising of 
@@
 After running a survey on 175 developers from Eclipse, Apache and Mozilla,
-the authors applied a card sort in order to organize the comments into hierarchies to 
-identify common patterns. Their findings can be summarized in the following top seven
+the authors applied a card sort in order to organise the comments into hierarchies to 
+identify common patterns. Their findings can be summarised in the following top seven
 suggestions: create differentiation between bug report difficulty levels between 
@@
 of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
-GNOME and Eclipse and projects and split their approach into four steps: extract and organize tickets, 
+GNOME and Eclipse and projects and split their approach into four steps: extract and organise tickets, 
 pre-process tickets (i.e. tokenization, stop word removal and stemming), train the classifier on two datasets 
@@
 The first step towards building the data set was to create a tool that was able to execute all the necessary commands:
-fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
+fetching the tickets from any Jira instance, storing them into some form of database, analyse the variables of interest, 
 automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
@@
 
-This is the first command implemented in our tool - it is desgined to fetch, from any valid Jira URL, any number of tickets 
+This is the first command implemented in our tool - it is designed to fetch, from any valid Jira URL, any number of tickets 
 and then store everything inside an instance of BoltDB \cite{bolt}, a key-value pair 
-database. The whole process is parallelized with the possibility of scaling even up to hundreds of goroutines
+database. The whole process is parallelised with the possibility of scaling even up to hundreds of goroutines
 (i.e. lightweight threads) running concurrently.
@@
 
-Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
+Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyse command first 
 fetches all the issues in the database. The next step is to filter out the tickets based on the following criteria:
@@
 Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
-outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
+outlined in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
 \begin{itemize}
@@
 the variable \emph{Time-To-Close} set (i.e. tickets marked as closed when they were fetched from the Jira instance; even though 
-we passed a filter for not fetching tickets still marked as Open, there was a small number erronously retrieved by Jira). 
+we passed a filter for not fetching tickets still marked as Open, there was a small number erroneously retrieved by Jira). 
 In order to compute correct results, we run the same checks on issues as the ones listed in the analyse command (e.g. plot 
@@
   \item created timestamp;
-  \item issue status - jira specific statuses, including Open, Closed, Awaiting Review, Patch Submitted;
+  \item issue status - Jira specific statuses, including Open, Closed, Awaiting Review, Patch Submitted;
   \item due date - optional deadline for when the ticket should get closed;
@@
 In this section we present our results to the research questions we set to answer. We computed charts for all 
-independent variables using either scatter plots for continuous variables (e.g. number of comments/\emph{Time-To-Close}) 
-or bar charts for categorical variables (e.g. presence of attachments/\emph{Time-To-Close}). We also computed statistical analysis for 
+independent variables using either scatter plots for continuous variables (e.g. number of comments / \emph{Time-To-Close}) 
+or bar charts for categorical variables (e.g. presence of attachments / \emph{Time-To-Close}). We also computed statistical analysis for 
 all variables to test their significance and rank correlation coefficient and we will present each of them in their 
@@
 
-For every type of analysis, we also discuss possible reasons why certain correlations occured. Furthermore, for all 
+For every type of analysis, we also discuss possible reasons why certain correlations occurred. Furthermore, for all 
 of them we give possible solutions that could be implemented in order to maximise the ticket quality as cost-effective 
@@
 or a code snippet could help reduce the \emph{Time-To-Close} for the ticket.
+
+\vskip20pt
 
@@
 the Apache Software Foundation projects (231 projects \cite{apache_projects}), many of the projects 
-we collected (22) are also written in Java, thus we had a considerable chunk of data to analyze.
+we collected (22) are also written in Java, thus we had a considerable chunk of data to analyse.
 
@@
 for tickets without them.
+
+\vskip35pt
 
@@
 words produce smaller Time-To-Close values. However, the bulk of values plotted are in the range of 
-1 to 1,600 total comment words per ticket (76,633 tickets) and in this slice of tickets, the trend is descending.
-We did not generate the plot containing solely these values because there would still be 36,711 tickets left out. 
+1 to 1,600 total comment words per ticket (76,633 tickets) and for this majority of tickets, the trend is ascending.
+We could not generate the plot based solely on these values as there would have been 36,711 tickets left out. 
 Therefore, the curve is skewed to the right, although the bulk of tickets that dictate the trend, are on the left side.
 
-A correlational analysis run on all 201,786 tickets, however, releaved a weak positive relationship with $r = 0.271$ and $p < 0.01$. 
+A correlational analysis run on all 201,786 tickets, however, revealed a weak positive relationship with $r = 0.271$ and $p < 0.01$. 
 This implies a statistically significant finding - as the number of comments increases, the \emph{Time-To-Close} value of the ticket 
@@
 The figure shows a very similar correlation to the one for comments complexity - graphically, it seems that as the number of words 
-in summary and description increases, the Time-To-Close will decrease. This is true for the majority of the tickets 
-which are in the range of 2 to 290 words, but as in the case of comments complexity analysis, we did not generate 
-the plot only for those as we would have left 61,322 tickets out (out of a total of 201,786 tickets analysed).
+in summary and description increases, the Time-To-Close will decrease. However, when numbers are run, the opposite trend 
+surfaces. The majority of the tickets are in the range of 2 to 290 words, but as in the case of comments complexity analysis, 
+we could not generate the plot only for those as we would have left 61,322 tickets out (out of a total of 201,786 tickets analysed). 
+Therefore, the curve is skewed to the right, although the bulk of tickets that dictate the trend, are on the left side.
 
@@
 the essential reason of filing that ticket from triagers and developers working on the project. One of the findings 
-Zimmermann et al. \cite{zimmermann2010makes} present in their study is that a good, succint summary can significantly 
+Zimmermann et al. \cite{zimmermann2010makes} present in their study is that a good, succinct summary can significantly 
 reduce the effort invested by the developers.
@@
 within some reasonable parameters. During our analysis process, we identified more than 50 tickets having descriptions 
-with more than 4,000 words. Even though they included various types of information, including steps to reprodce, 
+with more than 4,000 words. Even though they included various types of information, including steps to reproduce, 
 we believe that the reason why Jira and the other popular issue tracking systems created so many fields for bug reports 
@@
 Another simple and straightforward solution can be the simple addition of hints below or above the text boxes for summary 
-and description where administrators can write succint messages adivising reporters to not write verbose paragraphs 
+and description where administrators can write succinct messages advising reporters to not write verbose paragraphs 
 unless they really have a very good reason to do so.
@@
 after all, in the human nature to make mistakes, and mistyping is no exception. If we, for example, have some hint or a rule
-in the code of conduct for the project stating that everything should be 100\% gramatically correct, many reporters with a 
+in the code of conduct for the project stating that everything should be 100\% grammatically correct, many reporters with a 
 different language than English as their primary one would feel unwelcome and they might not get involved in the project anymore.
@@
 sentiment analysis tool running in the background as the user is typing in any text box. If they reach a certain low 
-threshold and it is believed that they are becoming rude or unpolite, there could be a warning/pop-up on the screen advising 
+threshold and it is believed that they are becoming rude or impolite, there could be a warning/pop-up on the screen advising 
 them against submitting the comment and encouraging them to be polite, engaging and friendly. One other solution
@@
 open source ones. Most closed source projects have much more structured planning, tracking and management activities - as 
-Crowston et al. \cite{crowston2012free} present in their study, open source projects lack organized coordination which,
+Crowston et al. \cite{crowston2012free} present in their study, open source projects lack organised coordination which,
 in the context of our study, means that people do not invest much effort into properly creating tickets in issue tracking 
